### 2021-09-03 docs/paper/paper.tex
Add paper scaffold

\input{template/acm}
\input{template/bibtex}
\input{template/hyphenation}
\input{template/packages}
\input{template/commands}

\begin{document}

	\input{title}

	\input{sections/0_abstract}
	\keywords{mining software repositories, ecosystem call graphs, API usage, type analyzer, npm}

	\maketitle

	\input{sections/1_introduction}
	\input{sections/2_related_work}
	\input{sections/3_approach}
	\input{sections/4_data_collection}
	\input{sections/5_usage_mining}
	\input{sections/6_presentation}
	\input{sections/7_evaluation}
	\input{sections/8_conclusion}

	\input{acknowledgements}

	\input{template/bibliography}

	%\appendix

\end{document}
\endinput

### 2021-09-03 docs/paper/sections/1_introduction.tex
Add paper scaffold

\section{Introduction}
\label{sec:introduction}

Foo.

### 2021-09-03 docs/paper/sections/2_related_work.tex
Add paper scaffold

\section{Related work}
\label{sec:related_work}

Foo.

### 2021-09-03 docs/paper/sections/5_usage_mining.tex
Add paper scaffold

\section{Usage mining}
\label{sec:usage_mining}

Foo!

### 2021-09-03 docs/paper/sections/7_evaluation.tex
Add paper scaffold

\section{Evaluation}
\label{sec:evaluation}

Foo!

### 2021-09-03 docs/paper/sections/8_conclusion.tex
Add paper scaffold

\section{Conclusion}
\label{sec:conclusion}

Foo!

### 2021-09-03 docs/paper/sections/0_abstract.tex
Add abstract

\begin{abstract}

	In the dependency graph of a software ecosystem, \emph{downstream dependencies} are the nodes that depend on a package.
	Other than for upstream dependencies, solutions that provide individual package developers with this kind of information do not yet exist.
	This paper makes two major contributions:
	\begin{enumerate*}[label=(\roman*)]
		\item We propose an approach for mining usage data about npm packages from their downstream dependencies by utilizing a static type analyzer.
		\item We introduce a tool that allows package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
			\footnote{
				All artifacts are available on GitHub under the following URL: \url{https://github.com/LinqLover/downstream-repository-mining}
				\TODO{Insert name and use link to VSCE}
			}
	\end{enumerate*}
	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that they can be useful to support package developers in improving or extending their APIs.

\end{abstract}

### 2021-09-03 docs/paper/sections/1_introduction.tex
Add introduction

@@
 
-Foo.
+Open Source software (OSS) solutions have become more and more and important during the last decades.
+Especially, this trend has been experiencing an additional updraft due to the ongoing spreading of OSS platforms such as GitHub or GitLab.
+Open-source development offers many advantages as opposed to traditional closed-source development, including large numbers of volunteer contributions from the open-source community, increased transparency effects in security-related domains, and a high potential for reusing solutions.
+These solutions are usually organized as \emph{packages} each of which attempts to solve an isolated problem and provide a generic interface.
+Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
+Other solutions or packages then can \emph{depend} on existing packages.
+These dependency relations form a large directed graph that connects major parts of the software world for each popular programming language ecosystem.
+
+Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
+While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
+This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
+Eventually, all these issues impair the capabilities of the global OSS community to build and support faultless products in an efficient process.
+In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.
+
+To tackle these concerns, in this paper, we propose an approach to gather API usages from downstream dependency repositories of npm packages, in order to support package developers in surveying usages of their solutions.
+We further make these data directly available to package developers by integrating them into an integrated development environment (IDE).
+
+The rest of this paper is organized as follows:
+In \cref{sec:related_work}, we give a summary of existing approaches in this field.
+In \cref{sec:approach}, we outline our approach for gathering and analyzing usage data from downstream dependencies.
+In \cref{sec:data_collection} and \cref{sec:usage_mining}, we describe our implementation for collecting downstream dependency repositories resp. mining usage data from these repositories.
+In \cref{sec:presentation}, we sketch our design for a display of the usage data inside an IDE.
+In \cref{sec:evaluation}, we examine the fitness of our data mining approach and the usability of the display solution.

### 2021-09-03 docs/paper/sections/2_related_work.tex
Add related work

@@
 
-Foo.
+To our knowledge, the design of proper tooling for improving package developers' knowledge about interface usages in dependencies has not yet attracted significant attention in the scientific community.
+Nevertheless, programmatic analysis of dependency graphs and API usage mining are already common techniques in the field of \emph{mining software repositories} (MSR).
+\citet{chaturvedi2013tools} provide a broad overview of existing achievements and ongoing research topics in this field.
+Besides source code repositories, they also describe various other data sources worthwhile to examine -- including version control systems, telemetry data from IDEs, issue trackers, and discussion platforms -- as well as different directions for evaluating the retrieved data -- such as classifying or ranking repositories, analyzing the evolution of projects, studying development communities, but also inspecting the relationships and dependencies between projects.
+In the following, we will consider the different problems that our research issue can be decomposed into.
+
+\subsection{Mining dependencies}
+
+A common purpose for \emph{analyzing dependency graphs} is to discover transitive (indirect) upstream dependencies of a project and assess their impact on the stability and vulnerability of the project.
+This is done by \citet{kikas2017structure} which apply their methodology to the JavaScript, Ruby, and Rust ecosystems and gain statistical insights into the centrality and evolution of these ecosystems.
+\citet{decan2018impact} pursue a similar approach in order to measure the spreading of security vulnerabilities along the chain of downstream dependencies.
+
+However, existing research about dependency graphs primarily takes a broad statistical perspective, and researchers often rely on a large corpus of downloaded software repositories \citep{abdalkareem2017developers,katz2020libraries,kikas2017structure}.
+% and researchers usually either access certain package registries such as the npm registry that already contain bidirectional dependency data, or they collect large amounts of software repositories from development platforms such as GitHub, extract dependency lists from each repository's metadata, and finally invert all adjacency lists to get the downstream dependencies.
+As opposed to this approach, these capacities will not be appropriate for scenarios that are occasionally performed by developers of a single package only.
+In this case, developers will often use a public \emph{code search} service such as GitHub code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or Sourcegraph\footnote{\url{https://sourcegraph.com/}} instead.
+\citet{liu2020opportunities} survey current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.
+
+\subsection{Mining usage information}
+
+Dependency graphs do not provide information about package usage on a finer granularity, so reference insights about single package members such as classes or methods remain unknown.
+The process of extracting fine-granular information about all references to individual elements of an interface is often referred to as \emph{API usage analysis}.
+A simple approach to this problem is to perform a string search for package names or members in the dependencies \citep{mileva2010mining}.
+\citet{qiu2016understanding} propose a more elaborated approach that operates on the AST of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
+A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data in order to analyze the historical importance of certain features supported by an API.
+
+However, the precision of ASTs is limited for dynamically typed languages such as JavaScript.
+For this reason, a common data structure that can be used to improve type information are \emph{call graphs} that are either \emph{static} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamic} (i.e., empirically recorded during program execution).
+While the latter type has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
+There are many solutions that analyze the structure of programs and extract the relevant information to build call graphs:
+
+\citet{collard2013srcml} propose an infrastructure called \caps{srcML} that is aimed to create a unified representation of multilingual source code snippets for arbitrary analysis purposes, including the construction of call graphs.
+Another solution is proposed by \citet{bogar2018lightweight} who focus on analyzing multilingual codebases and who utilize an island parser to build call graphs.
+Furthermore, \citet{antal2018static} compare several call graph generators for JavaScript.
+They also emphasize that for languages supporting dynamic typing or meta-programming mechanisms, static call graph generators have a limited precision by design.
+
+To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
+\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph.
+\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance; a very similar method is also sketched by \citet{boldi2020fine}.
+\citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
+With \caps{Pr\"azi}, \citet{hejderup2021präzi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
+For Java/Maven, \citet{keshani2021scalable} proposes another solution.
+
+After collecting these usage data, additional processing is possible to extract general usage information from the extensive raw data.
+Next to straightforward grouping and counting operations, such aggregations can be built by detecting popular \emph{usage patterns} of API features in the downstream dependencies.
+\citet{zhong2009mapo} propose a framework to do so that, for instance, finds sequences of API members that are invoked frequently and even uses these patterns for guiding API users by giving them recommendations.
+\citet{hanam2019aiding} pursue a different goal in their tool that helps package developers assess the impact of breaking API changes on the functionality of downstream dependencies.
+
+\subsection{Presentation of results}
+
+To establish an adequate developer experience, any collected usage data still need to be presented in a suitable manner.
+A common approach for this is a hierarchical and navigatable representation of the collected call tree.
+The first form of this representation has been invented as the ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
+Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
+With a focus on exploring references to API members, \citet{de2013multi} propose a set of additional views, including hierarchical lists and word clouds for highly referenced identifiers.
+Focusing on exploring APIs in a non-code-centric way, \citet{hora2015apiwave} propose a dashboard that allows developers to browse existing APIs and track possibly breaking changes in their interfaces.

### 2021-09-03 packages/core/test/npm-deps.test.ts
Try to fix timeouts for npm-deps tests

@@ -50,7 +50,7 @@ describe('getNpmDeps', () => {
             expect(github.stargazerCount).toBeGreaterThanOrEqual(10)
             expect(github.forkCount).toBeGreaterThanOrEqual(10)
         }
-    })
+    }, 60000)
 })
 
 describe('downloadDep', () => {

### 2021-09-13 docs/paper/sections/3_approach.tex
Add approach

\section{Approach}
\label{sec:approach}

Because of its superior popularity \TODO{prove}, in this work, we will confine ourselves to the JavaScript/npm ecosystem.
Our goal is thus to develop a tool for npm package developers that displays an overview of the downstream dependencies and their details for a chosen package.
Concretely, we pose the following key requirements to this tool:

\begin{enumerate}[label=R\arabic*]
	\item \label{req1} The tool allows package developers to survey and explore the usages of individual package members.
	\item The tool blends in well with the usual workflow of package developers.
	\item \label{req3} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
\end{enumerate}

In essence, our proposed approach to fulfill these requirements consists of three steps:
\begin{enumerate*}
	\item collect downstream dependency repositories,
	\item mine package usage samples from them,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}
In the following, we will describe each step.

\subsection{Downstream dependency collection}
\label{sec:approach/collection}

In the first step, a list of repositories that depend on the target package has to be assembled.
As mentioned in \cref{sec:related_work/usage_information}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.

As an alternative, we have decided to apply significantly stricter pre-filtering to the set of repositories before downloading it to the local machine.
For that, we have chosen two publicly available data sources:\footnote{
	Other data sources that we have rejected include GitHub code search which has limited precision results and is not freely accessible programatically as well as the \emph{libraries.io} service \citep{katz2020libraries} whose downstream dependency search was inoperative at the time of writing.%
}

\begin{enumerate}[label=(\roman*)]
	\item The npm registry which maintains a doubly-connected edge list of all npm packages that depend on each other.
	\item The code search engine \emph{Sourcegraph}\footnote{\url{https://sourcegraph.com/}} which is indexing repositories from most popular OSS platforms such as GitHub or GitLab.
		Using this search engine, we can query all repositories that declare a dependency on the target package in their package metadata file.
\end{enumerate}

Finally, we can download the source code for a small number of relevant repositories only.

\subsection{Usage sample mining}
\label{sec:approach/mining}

\begin{figure*}[htb!]
	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
	\newcommand\highlight[1]{\textcolor{red}{#1}}
	\centering
	\begin{subfigure}[t]{.32\linewidth}
		\include{sections/3_approach_assets/patterns/CallExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\include{sections/3_approach_assets/patterns/PropertyAccessExpression}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{.32\linewidth}
		\include{sections/3_approach_assets/patterns/JsxOpeningExpression}
	\end{subfigure}

	\caption{Example AST patterns for TypeScript programs.
		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
	}
	\label{fig:approach/mining/patterns}
\end{figure*}

Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.

To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.

% TODO: use term "binding"?
In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to, or between a function call and the definition of this function.

In the final step, we traverse the AST again and collect all nodes that are linked to a declaration in the target package.
To identify these links, we define a number of patterns for node structures and look up the declaration of every matched node (see \cref{fig:approach/mining/patterns}).

\subsection{Presentation of results}
\label{sec:approach/presentation}

After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
To satisfy \cref{req2} and make our tool avaiable in the usual working environment of users, we implement it as an extension to a popular IDE.
One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}.
As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.

For choosing appropriate views of the raw reference data, we have identified three common questions of package developers to answer each of which they require access to downstream dependencies and their usage samples:

\begin{enumerate}[label=Q\arabic*]
	\item Which dependencies do use the target package and what problems are they solving with it?
	\item By how many dependencies is a particular package member being used?
	\item In which contexts and constellations is a particular package member being used?
\end{enumerate}

To support developers in answering these questions and fulfill \cref{req1}, we have designed the following views for our extension:

\begin{enumerate}[label=(\roman*)]
	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
	\item The \emph{usage browser} displays all public package member and, grouped for each member, all dependencies and their references to this member.
	\item The \emph{CodeLens integration} provides quick access to a slice of the usage browser that is attached to the definition of each package member right in the source code editor.
\end{enumerate}

Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm felling lucky'' button for every view that redirects the user to a random dependency resp. reference to gain a faster, unbiased impression of usage samples.

### 2021-09-13 docs/paper/sections/2_related_work.tex
Add approach
Fix umlaut error with citation entry
Still strange that the bug did not occur locally ...

@@
 \subsection{Mining dependencies}
+\label{sec:related_work/dependencies}
 
@@
 \subsection{Mining usage information}
+\label{sec:related_work/usage_information}
 
@@
 \citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
-With \caps{Pr\"azi}, \citet{hejderup2021präzi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
+With \caps{Pr\"azi}, \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
 For Java/Maven, \citet{keshani2021scalable} proposes another solution.
@@
 \subsection{Presentation of results}
+\label{sec:related_work/presentation}
 

### 2021-09-17 docs/paper/sections/0_abstract.tex
Rework first sections (up to approach)

@@
 	In the dependency graph of a software ecosystem, \emph{downstream dependencies} are the nodes that depend on a package.
-	Other than for upstream dependencies, solutions that provide individual package developers with this kind of information do not yet exist.
+	Other than for upstream dependencies, solutions that provide individual package developers with this kind of information rarely exist to date.
 	This paper makes two major contributions:
 	\begin{enumerate*}[label=(\roman*)]
-		\item We propose an approach for mining usage data about npm packages from their downstream dependencies by utilizing a static type analyzer.
-		\item We introduce a tool that allows package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
+		\item We propose an approach for mining usage data about packages from their downstream dependencies by utilizing a static type analyzer.
+		\item We introduce a tool that allows npm package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
 			\footnote{

### 2021-09-17 docs/paper/sections/1_introduction.tex
Rework first sections (up to approach)

@@
 This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
-Eventually, all these issues impair the capabilities of the global OSS community to build and support faultless products in an efficient process.
+Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
 In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.

### 2021-09-17 docs/paper/sections/2_related_work.tex
Rework first sections (up to approach)

@@
 However, existing research about dependency graphs primarily takes a broad statistical perspective, and researchers often rely on a large corpus of downloaded software repositories \citep{abdalkareem2017developers,katz2020libraries,kikas2017structure}.
-% and researchers usually either access certain package registries such as the npm registry that already contain bidirectional dependency data, or they collect large amounts of software repositories from development platforms such as GitHub, extract dependency lists from each repository's metadata, and finally invert all adjacency lists to get the downstream dependencies.
 As opposed to this approach, these capacities will not be appropriate for scenarios that are occasionally performed by developers of a single package only.
@@
 A simple approach to this problem is to perform a string search for package names or members in the dependencies \citep{mileva2010mining}.
-\citet{qiu2016understanding} propose a more elaborated approach that operates on the AST of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
+\citet{qiu2016understanding} propose a more elaborated approach that operates on the \emph{abstract syntax tree} (AST) of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
 A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data in order to analyze the historical importance of certain features supported by an API.
@@
 To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
-\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph.
-\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance; a very similar method is also sketched by \citet{boldi2020fine}.
+\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph; a very similar method is described by \citet{boldi2020fine} to formulate the vision of new design for package management systems that provides options for finer-granular reuse of solutions.
+\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance.
 \citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
@@
 
-To establish an adequate developer experience, any collected usage data still need to be presented in a suitable manner.
+To establish an adequate developer experience, any collected usage data still need to be presented suitably.
 A common approach for this is a hierarchical and navigatable representation of the collected call tree.
-The first form of this representation has been invented as the ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
+The first form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
 Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.

### 2021-09-17 docs/paper/sections/2_related_work.tex
bibliography: add dois, emphasize preprints

@@
 In this case, developers will often use a public \emph{code search} service such as GitHub code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or Sourcegraph\footnote{\url{https://sourcegraph.com/}} instead.
-\citet{liu2020opportunities} survey current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.
+\citet{liu2020opportunities} provide a (not yet published) survey of current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.
 
@@
 \citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
-With \caps{Pr\"azi}, \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
+With \caps{Pr\"azi} (not yet peer-reviewed), \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
 For Java/Maven, \citet{keshani2021scalable} proposes another solution.

### 2021-09-17 docs/paper/sections/1_introduction.tex
Restructure paper: extract split up approach, merge implementation

@@
 Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
-Other solutions or packages then can \emph{depend} on existing packages.
+Other solutions or packages can then \emph{depend} on existing packages.
 These dependency relations form a large directed graph that connects major parts of the software world for each popular programming language ecosystem.
@@
 While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
-This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.\TODO{do we need to prove each of this?}
+This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.
+\TODO{do we need to prove each of this?}
 Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
@@
 
-To tackle these concerns, in this paper, we propose an approach to gather API usages from downstream dependency repositories of npm packages, in order to support package developers in surveying usages of their solutions.
+To tackle these concerns, in this paper, we propose an approach to extract API usage samples from downstream dependency repositories of individual packages in order to support package developers in surveying usages of their solutions.
 We further make these data directly available to package developers by integrating them into an integrated development environment (IDE).
@@
 In \cref{sec:related_work}, we give a summary of existing approaches in this field.
-In \cref{sec:approach}, we outline our approach for gathering and analyzing usage data from downstream dependencies.
-In \cref{sec:data_collection} and \cref{sec:usage_mining}, we describe our implementation for collecting downstream dependency repositories resp. mining usage data from these repositories.
-In \cref{sec:presentation}, we sketch our design for a display of the usage data inside an IDE.
+In \cref{sec:framework}, we outline the overall conditions and the general approach for our solution to mining downstream dependencies.
+In \cref{sec:dependency_collection} and \cref{sec:usage_mining}, we explain our approach for collecting downstream dependency repositories resp. mining usage data from these repositories in detail.
+In \cref{sec:implementation}, we describe an implementation of the proposed approach and our design decisions for displaying usage samples to the user.
 In \cref{sec:evaluation}, we examine the fitness of our data mining approach and the usability of the display solution.

### 2021-09-17 docs/paper/sections/3_framework.tex
Restructure paper: extract split up approach, merge implementation

\section{Framework}
\label{sec:framework}

To tackle the problems stated in \cref{sec:introduction}, our goal is to build a system that allows package developers to survey the API usage of downstream dependencies for a chosen target package.
Concretely, we have identified three common questions of package developers about the usage of their packages:

\begin{enumerate}[label=Q\arabic*]
	\item Which dependencies are using the target package, and what problems do they attempt to solve with it?
	\item By how many dependencies is a particular package member being used?
	\item In which contexts and constellations is a particular package member being used?
\end{enumerate}

Furthermore, we pose two organizational requirements to the tool solution to ensure its practical applicability for the target user group:

\begin{enumerate}[label=R\arabic*]
	\item \label[requirement]{req1} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
	\item \label[requirement]{req2} The tool blends in with the usual workflow of package developers at the best possible rate.
\end{enumerate}

In essence, our proposed approach to collect the required data while fulfilling these requirements consists of three steps:
\begin{enumerate*}
	\item collect downstream dependency repositories,
	\item mine package usage samples from them,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}
In the following sections, we will describe each step.

### 2021-09-17 docs/paper/sections/4_dependency_collection.tex
Restructure paper: extract split up approach, merge implementation

\section{Downstream dependency collection}
\label{sec:dependency_collection}

In the first step, a list of repositories that depend on the target package has to be assembled.
As mentioned in \cref{sec:related_work/usage_samples}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.

As an alternative, we have decided to apply significant pre-filtering to the set of repositories before downloading it to the local machine.
For that, we have identified two types of data sources that are available in public clouds:

\begin{enumerate}[label=(\roman*)]
	\item Package repositories that maintain a doubly-connected edge list of all packages in an ecosystem depending on each other.
	\item Code search engines that index the source code of many repositories from OSS platforms.
		Using these search engines, we can query all repositories that declare a dependency on the target package in their package metadata file.
\end{enumerate}

Finally, we can download the source code for a small number of relevant repositories only.

### 2021-09-17 docs/paper/sections/5_usage_mining.tex
Restructure paper: extract split up approach, merge implementation

@@
-\section{Usage mining}
+\section{Usage sample mining}
 \label{sec:usage_mining}
 
-Foo!
+\begin{figure*}
+	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
+	\newcommand\highlight[1]{\textcolor{red}{#1}}
+	\centering
+	\begin{subfigure}[t]{.32\linewidth}
+		\input{sections/5_usage_mining/patterns/CallExpression}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[t]{.32\linewidth}
+		\input{sections/5_usage_mining/patterns/PropertyAccessExpression}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[t]{.32\linewidth}
+		\input{sections/5_usage_mining/patterns/JsxOpeningElement}
+	\end{subfigure}
+
+	\caption{AST patterns for example JavaScript/TypeScript expressions.
+		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
+	}
+	\label{fig:usage_mining/patterns}
+\end{figure*}
+\input{sections/5_usage_mining/patterns/JsxOpeningElement.postfigure.tex}
+
+Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
+Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.
+
+To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.
+
+% TODO: use term "binding"?
+In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to or between a function call and the definition of this function.
+
+In the final step, the AST is traversed again and collect all nodes that are linked to a declaration in the target package.
+To identify these links, we define a set of language-specific patterns of AST subtrees that containing a declaration node (see \cref{fig:usage_mining/patterns}).

### 2021-09-17 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
Restructure paper: extract split up approach, merge implementation

\begin{tikzpicture}
	\node [red] {JsxOpeningExpression}
		child [gray] {node [gray] {tagName}}
		child [gray] {node [gray, yshift = -0.5cm] {typeArguments}}
		child [gray] {node [gray] {attributes}};
\end{tikzpicture}
\caption[LoF entry]{
	Node pattern for a JSX opening element (as supported in React\protect\footnotemark or TypeScript\protect\footnotemark), such as in:
	\code{\lowlight{elem = }\uline{<Button \lowlight{color}="\lowlight{blue}"> \lowlight{Google</Button>}}\lowlight{;}}
}

### 2021-09-17 docs/paper/sections/6_implementation.tex
Restructure paper: extract split up approach, merge implementation

--- 2021-09-13 docs/paper/sections/3_approach.tex
@@
-\section{Approach}
-\label{sec:approach}
+\section{Implementation}
+\label{sec:implementation}
 
-Because of its superior popularity \TODO{prove}, in this work, we will confine ourselves to the JavaScript/npm ecosystem.
-Our goal is thus to develop a tool for npm package developers that displays an overview of the downstream dependencies and their details for a chosen package.
-Concretely, we pose the following key requirements to this tool:
+\subsection{Data collection}
+\label{sec:implementation/data_collection}
 
-\begin{enumerate}[label=R\arabic*]
-	\item \label{req1} The tool allows package developers to survey and explore the usages of individual package members.
-	\item The tool blends in well with the usual workflow of package developers.
-	\item \label{req3} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
-\end{enumerate}
+Foo!
 
-In essence, our proposed approach to fulfill these requirements consists of three steps:
-\begin{enumerate*}
-	\item collect downstream dependency repositories,
-	\item mine package usage samples from them,
-	and \item aggregate and present these usage data to the user.
-\end{enumerate*}
-In the following, we will describe each step.
+\subsection{Usage mining}
+\label{sec:implementation/usage_mining}
 
-\subsection{Downstream dependency collection}
-\label{sec:approach/collection}
-
-In the first step, a list of repositories that depend on the target package has to be assembled.
-As mentioned in \cref{sec:related_work/usage_information}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
-However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
-This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.
-
-As an alternative, we have decided to apply significantly stricter pre-filtering to the set of repositories before downloading it to the local machine.
-For that, we have chosen two publicly available data sources:\footnote{
-	Other data sources that we have rejected include GitHub code search which has limited precision results and is not freely accessible programatically as well as the \emph{libraries.io} service \citep{katz2020libraries} whose downstream dependency search was inoperative at the time of writing.%
-}
-
-\begin{enumerate}[label=(\roman*)]
-	\item The npm registry which maintains a doubly-connected edge list of all npm packages that depend on each other.
-	\item The code search engine \emph{Sourcegraph}\footnote{\url{https://sourcegraph.com/}} which is indexing repositories from most popular OSS platforms such as GitHub or GitLab.
-		Using this search engine, we can query all repositories that declare a dependency on the target package in their package metadata file.
-\end{enumerate}
-
-Finally, we can download the source code for a small number of relevant repositories only.
-
-\subsection{Usage sample mining}
-\label{sec:approach/mining}
-
-\begin{figure*}[htb!]
-	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
-	\newcommand\highlight[1]{\textcolor{red}{#1}}
-	\centering
-	\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/CallExpression}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/PropertyAccessExpression}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/JsxOpeningExpression}
-	\end{subfigure}
-
-	\caption{Example AST patterns for TypeScript programs.
-		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
-	}
-	\label{fig:approach/mining/patterns}
-\end{figure*}
-
-Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
-Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.
-
-To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.
-
-% TODO: use term "binding"?
-In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to, or between a function call and the definition of this function.
-
-In the final step, we traverse the AST again and collect all nodes that are linked to a declaration in the target package.
-To identify these links, we define a number of patterns for node structures and look up the declaration of every matched node (see \cref{fig:approach/mining/patterns}).
+Foo!
 
 \subsection{Presentation of results}
-\label{sec:approach/presentation}
+\label{sec:implementation/presentation}
 
 After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
-To satisfy \cref{req2} and make our tool avaiable in the usual working environment of users, we implement it as an extension to a popular IDE.
-One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}.
+To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to a popular IDE.
+One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code.\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
 As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.
 
-For choosing appropriate views of the raw reference data, we have identified three common questions of package developers to answer each of which they require access to downstream dependencies and their usage samples:
-
-\begin{enumerate}[label=Q\arabic*]
-	\item Which dependencies do use the target package and what problems are they solving with it?
-	\item By how many dependencies is a particular package member being used?
-	\item In which contexts and constellations is a particular package member being used?
-\end{enumerate}
-
-To support developers in answering these questions and fulfill \cref{req1}, we have designed the following views for our extension:
+To support developers in answering the questions raised in \cref{sec:framework}, we have designed the following views for our extension:
 
@@
 reference to gain a faster, unbiased impression of usage samples.
+
+Foo!

### 2021-09-29 docs/paper/sections/5_usage_mining.tex
Paper: refine description of usage mining

@@
 
-To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.
+To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate abstract syntax forest (ASF, i.e., a set of ASTs).
 
-% TODO: use term "binding"?
-In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to or between a function call and the definition of this function.
+In a second step, a static type analysis is performed against each dependency ASF together with the target package's ASF.
+The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
+For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function.
+\TODO{Give example?}
+The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
+\TODO{Elaborate on the topics type analysis and static/dynamic typing in related work/introduction.}
 
-In the final step, the AST is traversed again and collect all nodes that are linked to a declaration in the target package.
-To identify these links, we define a set of language-specific patterns of AST subtrees that containing a declaration node (see \cref{fig:usage_mining/patterns}).
+In the final step, from each ASF all nodes are collected whose type is declared in the target package.
+To identify these links, we define a set of language-specific patterns for AST subtrees that constitute a usage expression.
+In particular, each of these patterns expects a node containing a link to an identifier declaration (see \cref{fig:usage_mining/patterns}).
+
+The complete procedure is displayed in \cref{alg:usage_mining}.
+
+\begin{algorithm}
+	\caption{Extraction of usage samples.}\label{alg:usage_mining}
+
+	\KwIn{\\\Indp
+		$\mli{pkg}$: target package \\
+		$\mli{dependencies}$: downstream dependencies}
+	\KwOut{usage samples (set of strings)}
+	\;
+	\For{$\mli{dep} \in \mli{dependencies}$}{
+		$\mli{asf} \gets \mtx{parse}(\mli{dep} \cup \mli{pkg})$\;
+	  	$\mtx{annotate\_types}(\mli{asf})$\;
+		\For{$\mli{ast} \in \mli{asf}$}{
+			\For{$\mli{node} \in \mli{dfs}(\mli{ast})$}{
+				\For{$\mli{pattern} \in \mli{patterns}$}{
+					\If{$\mli{pattern}.\mtx{matches}(\mli{node}) \wedge \mli{pkg}.\mtx{declares}(\mli{pattern}.\mtx{getType}(\mli{node}))$}{
+						\kwYield{$\mli{node}.\mtx{text}$}
+					}
+				}
+			}
+		}
+	}
+\end{algorithm}

### 2021-09-29 docs/paper/sections/6_implementation.tex
Complete implementation

@@
 
-\subsection{Data collection}
-\label{sec:implementation/data_collection}
+In our implementation, we are restraining ourselves to analyzing node.js projects written in JavaScript.
+This decision is based on the large prevalence of JavaScript\footnote{GitHut 2.0: A small place to discover languages in GitHub.
+\url{https://madnight.github.io/githut/\#/pushes}} as well as the first-rate extent of the npm ecosystem\footnote{Modulecounts: \url{http://www.modulecounts.com/}} which has been unsurpassed since 2015.
+In the following, we are describing how we apply the single steps of the approach presented above to this particular domain.
 
-Foo!
+\subsection{Downstream dependency collection}
+\label{sec:implementation/dependency_collection}
 
-\subsection{Usage mining}
+The de facto standard package repository for node.js packages is npm.\footnote{\url{https://www.npmjs.com/}}
+To fetch downstream dependency packages from the npm registry, we utilize the npm package npm-dependants\footnote{\url{https://www.npmjs.com/package/npm-dependants}} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
+To keep the footprint of our implementation small, we only scrape a part of the dependents list.
+We then request basic metadata for each found package from the npm registry, in particular including a URL to the source code archive of the latest package version (commonly referred to as \emph{tarball}), by using the package-metadata package.\footnote{\url{https://www.npmjs.com/package/package-metadata}}
+Finally, we download and extract each source code archive from the npm registry with the help of the download-package-tarball package.\footnote{\url{https://www.npmjs.com/package/download-package-tarball}}
+
+\begin{lstlisting}[language=json,
+	label=sec:implementation/package.json,
+	caption={An example \code{package.json} manifest file for the \code{ripple-lib} package specifying multiple dependencies (truncated).},
+	float=tpb,
+	floatplacement=tbp,
+	abovecaptionskip=-5pt
+]
+{
+	"name": "ripple-lib",
+	"version": "1.10.0",
+	"description": "A TypeScript/JavaScript API for interacting with the XRP Ledger",
+	"dependencies": {
+		"bignumber.js": "^9.0.0",
+		"https-proxy-agent": "^5.0.0",
+		"jsonschema": "1.2.2"
+	}
+}
+\end{lstlisting}
+
+For the second approach, using a code search engine, we have identified Sourcegraph\footnote{\url{https://sourcegraph.com/}} as a promising platform.
+npm packages specify their dependencies in a package.json metadata file (see \cref{sec:implementation/package.json}).
+To find all packages depending on a package \code{<pkg>}, we can search all available package.json files for the substring \code{"<pkg>":}.
+Refined with some additional constraints to filter out package copies from \code{node\_modules} folders that downstream developers have pushed accidentally, and to limit the number of results retrieved, our final Sourcegraph query has the following form:
+
+{
+	\lstset{frame=none,
+		aboveskip=3mm,
+		belowskip=3mm,
+		xleftmargin=3mm,
+		xrightmargin=3mm
+	}
+	\begin{lstlisting}[language=sourcegraph]
+"<pkg>":
+	file:package\.json
+	-file:node_modules/
+	select:file
+	count:<limit>
+	\end{lstlisting}
+}
+
+We submit this search query by sending it to the publicly available Sourcegraph GraphQL API.\footnote{\url{https://docs.sourcegraph.com/api/graphql}}
+For each hit, we request additional information from the API about the matched repository, including the name of the depending package and the URL to the original repository.
+We use the npm package graphql-request\footnote{\url{https://www.npmjs.com/package/graphql-request}} for accessing the GraphQL API.
+After retrieving a search result, we download a snapshot of the full repository by using the download-git-repo package\footnote{\url{https://www.npmjs.com/package/download-git-repo}} which combines access to the APIs of different code host providers such as GitHub or BitBucket.
+
+Additionally, we enrich the metadata of each package with a few metrics indicating its popularity from the associated GitHub repository if specified.
+The GitHub API is accessed via the official octokit library.\footnote{\url{https://octokit.github.io/}}
+
+\subsection{Usage sample mining}
 \label{sec:implementation/usage_mining}
 
-Foo!
+In our solution, we are focusing on mining usage samples from downstream dependencies that are written in JavaScript or TypeScript.
+\TODO{Is this the right place to introduce TypeScript?}
+TypeScript is an extension of JavaScript that adds strong typing to the former which is based on a combination of implicit type inference and explicit type declarations.
+As the type-checking capabilities of the TypeScript compiler are optional and can be turned off via configuration, we consider the JavaScript syntax a subset of TypeScript syntax.
+
+For parsing the dependencies, we utilize the public TypeScript Compiler API.\footnote{\url{https://github.com/Microsoft/TypeScript/wiki/Using-the-Compiler-API}}
+The TypeScript compiler's \emph{binder} component annotates every node of the parsed program with a type symbol if it can resolve one.
+After performing a type analysis of the dependency by instrumenting the binder, we collect all nodes from the type-annotated ASF that refer to the target package by traversing it with a visitor function.
+This visitor function matches each node against a list of defined patterns (similar to \cref{fig:usage_mining/patterns}) based on the \code{syntaxKind}s of the node and its ancestors and descendants and then looks up the declaration of the node's type symbol to compare it with the source directory of the target package.
+
+Normally, foreign types can only be resolved if they are declared in a dependency module that has been installed into the \code{node\_modules} folder of the repository.
+Because downloading and installing all dependency modules for every downstream repository of the target package would increase the computational resources of the usage mining drastically and eventually violate \cref{req1}, we skip this step but instead modify the module resolution strategy of the TypeScript compiler host.
+To do so, we extend the \code{paths} parameter from the default compiler options\footnote{\url{https://www.typescriptlang.org/tsconfig\#paths}} and insert a new entry that remaps accesses to the target package name to the separate source code directory of the target package.
 
@@
 
-To support developers in answering the questions raised in \cref{sec:framework}, we have designed the following views for our extension:
+\begin{figure*}[b]
+	\centering
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\textwidth]{sections/6_implementation/extension/dependencies.png}
+		\caption[LoF entry]{The dependency browser.}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\textwidth]{sections/6_implementation/extension/references.png}
+		\caption[LoF entry]{The usage browser.}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\textwidth]{sections/6_implementation/extension/codelens.png}
+		\caption[LoF entry]{The CodeLens integration for the class \code{GraphQLError}.}
+	\end{subfigure}
+
+	\caption{Screenshots of our Visual Studio Code extension used to explore downstream dependencies of the npm package graphql.}
+	\label{fig:implementation/presentation/screenshots}
+\end{figure*}
+
+To support developers in answering the questions raised in \cref{sec:framework}, we have designed three key views for our extension (see \cref{fig:implementation/presentation/screenshots}):
 
@@
 	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
-	\item The \emph{usage browser} displays all public package member and, grouped for each member, all dependencies and their references to this member.
+	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
 	\item The \emph{CodeLens integration} provides quick access to a slice of the usage browser that is attached to the definition of each package member right in the source code editor.
@@
 Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
-In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm felling lucky'' button for every view that redirects the user to a random dependency resp.
+In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm feeling lucky'' button for every view that redirects the user to a random dependency resp.
 reference to gain a faster, unbiased impression of usage samples.
 
-Foo!
+We implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the Tree View API and the CodeLens API.
+One challenge was to deliver fast results and not to block the user interface because even though the lightweight mining approaches we chose to satisfy \cref{req1} above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation/TODO}).
+To overcome this issue, we use pagination wherever possible and applied the observer pattern to push incremental UI updates.
+As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our data model using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting inside the data collection process.

### 2021-09-29 docs/paper/sections/0_abstract.tex
paper: minor phrasing and typesetting improvements

@@
 	\begin{enumerate*}[label=(\roman*)]
-		\item We propose an approach for mining usage data about packages from their downstream dependencies by utilizing a static type analyzer.
+		\item We propose an approach for gathering downstream dependencies of a single package and extracting usage samples from them by utilizing a static type analyzer.
 		\item We introduce a tool that allows npm package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
@@
 	\end{enumerate*}
-	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that they can be useful to support package developers in improving or extending their APIs.
+	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that our approach could support package developers in improving or extending their APIs.
 

### 2021-09-29 docs/paper/sections/4_dependency_collection.tex
paper: minor phrasing and typesetting improvements

@@
 However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
-This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.
+This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} because of its large footprint in terms of computational power and time.
 

### 2021-09-29 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
paper: minor phrasing and typesetting improvements

@@
 \caption[LoF entry]{
-	Node pattern for a JSX opening element (as supported in React\protect\footnotemark or TypeScript\protect\footnotemark), such as in:
+	Node pattern for a JSX opening element (as supported in React\protect\footnotemark{} or TypeScript\protect\footnotemark{}), such as in:
 	\code{\lowlight{elem = }\uline{<Button \lowlight{color}="\lowlight{blue}"> \lowlight{Google</Button>}}\lowlight{;}}

### 2021-09-29 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
Refactor and fix figure and footnote positioning

--- 2021-09-17 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
@@
 \caption[LoF entry]{
-	Node pattern for a JSX opening element (as supported in React\protect\footnotemark or TypeScript\protect\footnotemark), such as in:
+	Node pattern for a JSX opening element (as supported in React\footnote{\url{https://reactjs.org/docs/introducing-jsx.html}} or TypeScript\footnote{\url{https://www.typescriptlang.org/docs/handbook/jsx.html}}), such as in:
 	\code{\lowlight{elem = }\uline{<Button \lowlight{color}="\lowlight{blue}"> \lowlight{Google</Button>}}\lowlight{;}}

### 2021-09-29 docs/paper/sections/7_evaluation.tex
Try to fix paper template on CI

@@
 
+Rename into discussion?
+
 Foo!
+
+research questions:
+
+-(RQ0) (how useful are these data?)
+-(RQ1) what is the quality of collected dependencies?
+-(RQ2) what is the quality of mined usage samples?
+-(RQ3) how well is the tool applicable?
+
+\# actual evaluation
+
+\#\# rq1
+
+- numbers of dependencies found for example packages (table for small, medium, large packages) for all approaches
+
+<choose subset from excel>
+
+NEXT: beispiele für fehler sammeln. slides damit ergänzen, fazit ziehen.
+
+- resources: fetch metadata/download speed (zusammen 25 Pakete/min); disk space per dependency (ca. 703 KB/package); API restrictions (free, no limitations known)
+- correctness: superfluous dependency specifications (TODO: count false positives by comparing with references, manually check)
+limitations:
+- false positives:
+	* type defs
+- missing dependencies: repositories without proper package manifest file
+- ranking: small repositories will be underrepresented
+
+\#\# rq2
+
+- numbers of dependencies and references found for example packages (table for small, medium, large packages)
+- resources: speed per package (20 pkgs/min), RAM/ROM
+- precision/correctness: proof that there are no false positives (given correctness of tsc)
+- false negatives/recall - (real) examples:
+	* limited matches due to lack of type information for other frameworks used (but we could solve this); extreme metaprogramming (eval, Function.call(), .../limitations of typescript)
+	* additional build steps (code generation, transpilers, ...)
+
+\#\# rq3
+
+- expert interviews?
+- experience report (short case study looking at a certain package)
+- comparison to hora2015apiwave or de2013multi? (or does this rather belong to relwork?)
+
+\# discussion

### 2021-09-29 docs/paper/sections/8_conclusion.tex
Try to fix paper template on CI

@@
-\section{Conclusion}
+\section{Conclusion and future work}
 \label{sec:conclusion}
@@
 Foo!
+
+future work:
+
+* evaluation as future work:
+
+	- rq2 - false negatives durch annotation ermitteln
+	- rq3 - user study
+
+* pattern analysis -> sample classification, potential for reuse
+* dynamic analysis -> parameter/return value insights, coverage detection
+* dependency classification/clustering through metrics (number of references, coupling)
+
+minor:
+* support more AST pattern (e.g. import())
+
+STEHENGEBLIEBEN: Notizen hierfür, in slides übernehmen, dann weitere Notizen für Präsi anwenden. Heute nochmal durchsprehcne?

### 2021-10-02 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
Fix footnote positioning; use ACM colors

@@
 \begin{tikzpicture}
-	\node [red] {JsxOpeningExpression}
+	\node [accent1] {JsxOpeningExpression}
 		child [gray] {node [gray] {tagName}}
@@
 	Node pattern for a JSX opening element (as supported in React\footnote{\url{https://reactjs.org/docs/introducing-jsx.html}} or TypeScript\footnote{\url{https://www.typescriptlang.org/docs/handbook/jsx.html}}), such as in:
-	\code{\lowlight{elem = }\uline{<Button \lowlight{color}="\lowlight{blue}"> \lowlight{Google</Button>}}\lowlight{;}}
+	\code{\textlowlight{elem = }\uline{<Button \textlowlight{color}="\textlowlight{blue}"> \textlowlight{Submit</Button>}}\textlowlight{;}}
 }

### 2021-10-02 docs/paper/sections/7_evaluation.tex
Add evaluation

--- 2021-09-03 docs/paper/sections/7_evaluation.tex
@@
 
-Foo!
+To evaluate the efficacy of our approach, we formulate three research questions:
+
+\begin{enumerate}[label=RQ\arabic*]
+	\item \label[requirement]{resqu1} What is the quality and quantity of the proposed approaches for dependency collection?
+	\item \label[requirement]{resqu2} What is the quality and quantity of the proposed approach for mining usage samples?
+	\item \label[requirement]{resqu3} How well is the proposed tool applicable?
+\end{enumerate}
+
+In the following, we are going to investigate each of these questions.
+
+\subsection{\ref{resqu1}: Dependency collection}
+\label{sec:evaluation/resqu1}
+
+To assess the quality of dependency collection, we analyze it with respect to extent, precision, recall, and performance.
+\Cref{tab:evaluation/resqu1/quantities} shows the number of dependencies that were collected from each data source following the proposed approaches for a set of arbitrarily selected npm packages.
+For each package, we have annotated a subset of the collected dependencies (max. 20 dependencies per package) manually to identify and classify false positive hits.
+
+\begin{table}
+	\centering
+	\small
+	\input{sections/7_evaluation/resqu1/quantities}
+	\caption{Quantity and false-positive rates (FPR) of downstream dependencies found by both approaches for selected packages.}
+	\label{tab:evaluation/resqu1/quantities}
+\end{table}
+
+\subsubsection{Extent}
+\label{sec:evaluation/resqu1/extent}
+
+Regarding the total number of dependencies collected by each approach, no clear trend in favor of any approach can be ascertained for small or medium packages (having less than 10,000 stars on GitHub).
+For larger packages (having at least 10,000 stars), however, the number of dependencies collected from the npm registry stagnates near to 400 hits; beyond this limit, the npm registry will return internal server errors only.
+For Sourcegraph, on the other hand, we have not hit any limitations so far; currently, they do not provide any official documentation for the exact rate limits.
+
+As the disjunct proportion of results from both approaches is very small (on average about \SI{6}{\percent}), we consider a combination of both data sources useful for maximizing the extent and diversity of the gained dataset.
+
+\subsubsection{Precision}
+\label{sec:evaluation/resqu1/precision}
+
+The precision of collected dependencies is drastically lower for dependencies found on Sourcegraph than for such found on npm.
+\Cref{fig:evaluation/resqu1/fp_causes} collates the causes we have identified for these false positives; most frequently, repositories specify a dependency on the target package in their package manifest file but do not actually import this package at any place.
+
+\begin{figure}
+	\centering
+	\small
+	\input{sections/7_evaluation/resqu1/fp_causes}
+	\caption{Causes for false-positive dependency matches and their frequencies.}
+	\label{fig:evaluation/resqu1/fp_causes}
+\end{figure}
+
+In some situations, this may happen if the package is a plugin for another package or if it is invoked as a CLI from a build script (\TODO{C'mon, we could improve data classification for this}), but in the majority of repositories, developers trivially appear to have specified the upstream dependency by accident (e.g., while copying a \code{package.json} file over from another package), or to have forgotten to remove the upstream dependency after switching away from using the package.
+Rarer causes include repositories that only add type definitions for TypeScript to a package but do not actually import it, as well as, especially for repositories found on Sourcegraph, other packages required by a repository declaring a peer dependency on the target package which needs to be fulfilled by the depending repository.
+
+We explain the increased false-positive rate for Sourcegraph dependencies by our observation that packages found on npm typically stand out by their higher cohesion and professional maintenance, whereas GitHub projects are more likely run as imperfect hobby projects.
+
+We stress that a reduced precision does not impair the quality of results displayed to package developers as all dependencies not containing at least one
+usage sample can be easily filtered out, but downloading and analyzing any irrelevant packages lowers the performance of the approach.
+
+\subsubsection{Recall}
+\label{sec:evaluation/resqu1/recall}
+
+Besides the precision of collected dependencies, their recall is also of interest.
+As the dependencies are collected from two giant datasets in extracts only, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
+Nevertheless, there are some causes that will prevent a dependency from being found by our approaches:
+
+\begin{itemize}
+	\item Packages without a proper dependency manifest cannot be detected by our approaches which are based on exactly these metadata.
+	\item On npm, naturally packages only will be found, creating a bias towards rather generic and professional software.
+	\item On both platforms, results will be sorted based on intransparent criteria (which, as we however speculate, include the number of direct dependents on npm and the recent update frequency on Sourcegraph, resp.).
+		As we only fetch the first dependencies from both data sources, this sorting is a likely source of further biases.
+		These biases could be fought by always fetching all dependencies, but this would drastically reduce the overall performance.
+\end{itemize}
+
+\subsubsection{Performance}
+\label{sec:evaluation/resqu1/performance}
+
+\begin{table}
+	\centering
+	\small
+	\begin{threeparttable}
+		\input{sections/7_evaluation/resqu1/performance}
+		\begin{tablenotes}
+			\footnotesize
+			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \si{2.80}{GHz}, internet downspeed ~1.8 \si{Gbit}/\si{s}.
+			\item[\alphtnotetext{2}] Effective speed while downloading multiple packages in parallel.
+		\end{tablenotes}
+	\end{threeparttable}
+
+	\caption{Key performance metrics for both dependency collection methods.}
+	\label{tab:evaluation/resqu1/performance}
+\end{table}
+
+\Cref{tab:evaluation/resqu1/performance} gives some basic metrics comparing the performance of both data sources.
+While searching downstream dependencies is slower by average on npm as we use a web scraper instead of an API for this source, npm packages are usually smaller as opposed to many monorepos on OSS platforms that contain multiple node.js packages, and they are faster to download since the download-git-repo package that we use for repositories found on Sourcegraph, as of today, only uses zipballs instead of tarballs while the latter would offer a higher compression rate.
+
+\subsection{\ref{resqu2}: Usage mining}
+\label{sec:evaluation/resqu2}
+
+To assess the quality of usage mining, we examine the precision, recall, and performance of this processing step.
+Due to the complexity of a detailed annotation process, we only consider the existence of found usage samples on the dependency level.
+The absolute quantity of found usage samples varies largely for different packages and dependencies based on the semantic extent of the package and the coupling between package and dependency.
+
+\subsubsection{Precision}
+\label{sec:evaluation/resqu2/precision}
+
+Under laboratory conditions, false-positive usage samples cannot be emitted by our approach if we assume the correctness of the TypeScript compiler.
+There are only two exceptions to this invariant:
+\begin{enumerate*}[label=(\roman*)]
+	\item If there is a name collision between two packages, invalid or false positives usage samples may be emitted.
+		However, the npm infrastructure attempts to rule out these collisions by using the package name as a unique ID for every published package.
+	\item If dependency developers deliberately interfere with the TypeScript compiler (for instance, by suppressing type errors using a \verb|@ts-ignore| comment\footnote{\url{https://www.typescriptlang.org/docs/handbook/release-notes/typescript-2-6.html\#suppress-errors-in-ts-files-using--ts-ignore-comments}}), both false positive and false negative matches are possible.
+\end{enumerate*}
+
+\subsubsection{Recall}
+\label{sec:evaluation/resqu2/recall}
+
+To evaluate the recall of our approach, we have refined the experimental dataset collected in \cref{sec:evaluation/resqu1} and removed all false-positive dependencies.
+Within this cleansed dataset, the overall rate of dependencies for that our approach is unable to find at least one usage sample accounts for \SI{47.9}{\percent}.
+As a cause for these false negatives, we have identified a number of systematic causes:
+
+\begin{itemize}
+	\item Many projects on OSS platforms have complex build configurations that include additional transpilation or code generation steps before a final version of the source code is reached that is valid to the node.js interpreter or the TypeScript compiler.
+		Unless we add explicit support for such build configurations, type analysis and thus usage mining for these projects will fail.
+	\item In some situations, additional type definitions are required to perform a complete type inference of a dependency.
+		This is the case for every parametrized callback from a package for that type definitions are not available.
+		This limitation could be resolved by downloading or generating the type definitions for all upstream dependencies of every downstream dependency; this, on the other hand, would reduce the performance of the approach.
+	\item In general, the static type analyzer of TypeScript has its limitations.
+		For instance, the type analysis will have a limited recall for certain control flow patterns or metaprogramming constructs such as meta-circular evaluation using the the \code{eval()} function or dynamic function binding using \code{Function.bind()} and friends.
+\end{itemize}
+
+\subsubsection{Performance}
+\label{sec:evaluation/resqu2/performance}
+
+The total time spent for performing type analysis for a repository from the experimental dataset and mining usage samples averages ca. \num{3} seconds.
+The complete ASF of an average parsed repository consumes between \SI{10}{MB} and \SI{500}{MB} of RAM, depending on the size of the analyzed repository.
+
+\subsection{\ref{resqu3}: Tool}
+\label{sec:evaluation/resqu3}
+
+To assess the applicability of our proposed tool, we investigate the different options of users who would like to answer the questions raised in \cref{sec:framework}.
+We further analyze how far our tool meets the requirements posed above.
+
+\subsubsection{Answering user questions}
+
+In order to answer \cref{q1} without our tool, it would be possible to access the aforementioned data sources manually.
+Both npm and Sourcegraph provide suitable web interfaces for surveying dependent packages or search results, resp.
+To understand the intent of a dependency, users can read its documentation online, if any, or browse its implementation.
+The source code of repositories can be browsed on Sourcegraph, but on npm, this is not possible, and users need to either manually download and extract the package or follow the link to an open-source code repository if the package provides one.
+
+With our tool, the data collection process is condensed into a single button that displays all references from both data sources incrementally.
+Users can hover or click any dependency to view its documentation or implementation.
+
+In order to answer \cref{q2,q3} without our tool, users need to scan each dependency found in the previous step separately to count or read all usage samples, resp.
+If they are intending to analyze the usage of a member with an unambiguous name, they can perform an expeditious string search.
+For repositories found on Sourcegraph, this is either possible by starting a new search on the platform or by searching the source code in the original code host.
+If the source code is not available online, it needs to be downloaded first and searched locally.
+If the member of interest has a confusable name, a string search could not lead to the desired result.
+In this case, users need to download and install the project and view it in an IDE that supports reference search (for instance, there is a built-in feature for this in VS Code).
+Alternatively, they can try to use the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}).
+However, as of today, precise code intelligence is only available for a small number of repositories as both the dependent repository and the dependency repository are required to provide a special index file.
+
+Within our tool, all usage samples can be collected automatically and be merged into a single list.
+Once the collected dependencies have been processed, users can select a member of interest and view all its usage samples with a single click.
+For the usage analysis of Java APIs, there is also the tool \caps{Exapus}\citep{de2013multi} which differentiates between different kinds of member usages such as instantiation of vs.
+inheritance of a class.
+Such a classification mechanism could also improve the usability of our tool
+
+\subsubsection{Meeting requirements}
+
+We break down \cref{req1} into three acceptance criteria: application liveness, small resource footprint, and easy setup.
+
+As a result of the numbers mentioned in the evaluation of the previous research questions, our tool is able to process 5 up to 12 dependencies per minute while requiring about \SI{500}{MB} RAM in total and less than \SI{30}{MB} ROM per package.
+I.e., from the moment the tool is activated, the first results usually take less than 10 seconds to appear on the UI.
+This is an acceptable delay with regard to Shneiderman's definition of acceptable application response times, so the liveness criterion is fulfilled.\footnote{Ben Shneiderman and Catherine Plaisant.
+2010.
+Designing the user interface: Strategies for effective human-computer interaction.
+Pearson Education India.}
+Even if the tool is run for 10 minutes, it will occupy less than \SI{4}{GB} of ROM that can be released at any time, which we consider a small resource footprint at a time where modern operating systems require at least \SI{64}{GB} ROM; thus, also the second acceptance criterion is fulfilled.
+As our extension can be installed with two clicks from the Visual Studio Code Extension Marketplace, it is also easy to set up and thus fulfills the first requirement.
+
+\Cref{req2} effectively calls for a minimum number of context switches that are required to use the tool, i.e., for minimizing the temporal, spatial, and semantic distance\footnote{David Ungar, Henry Lieberman, and Christopher Fry.
+1997.
+Debugging and the experience of immediacy.
+Commun.
+ACM 40, 4 (1997), 38–43.} between the downstream dependency UI and the IDE used by package developers.
+
+Once the data are available in the UI, interaction with them is possible with the same speed as with local source files in the package.
+This is compatible with Shneiderman's requirement to frequent tasks and indicates a low temporal distance.
+
+The spatial distance varies for the different views of the tool:
+For the dependency browser and the usage browser, a separate toolbar has to be opened, which indicates a higher spatial distance; still, the artifacts are available in the same IDE.
+On the other hand, the dependency artifacts were not displayed in the IDE without our tool and have no strong relationship to the already existing artifacts, so any closer integration into an existing view would increase unintended coupling between independent domains.
+The code annotations are very close to the original source code and thus have a small spatial distance.
+
+The semantic distance can be described as the perceived similarity of artifacts displayed both in the tool's UI and in the existing IDE.
+Such artifacts are the package and dependency members displayed in the usage browser of our tool.
+Most items in the usage browser bear the same label as the corresponding identifier in the source code, which reduces the semantic distance.
+However, some nodes in the path of dependency members correspond to anonymous expressions in the source code that do not bear a label themselves and thus are labeled using a generic fallback token in our tool (see \cref{fig:implementation/presentation/screenshot/dependency_browser}).
+This does not match the labeling convention in VS Code (as displayed in the outline view of the explorer activity bar), where a target identifier is determined from the context of the expression.
+For such nodes, the current semantic distance of our tool is still higher than necessary.
+
+With a low temporal distance, a low-to-medium spatial distance, and a mainly low semantic distance, our tool also fulfills \cref{req2}.

### 2021-10-02 docs/paper/sections/8_conclusion.tex
Remove notes committed by accident 😬
Add conclusion

--- 2021-09-03 docs/paper/sections/8_conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion and future work}
 \label{sec:conclusion}
 
-Foo!
+Downstream dependencies provide a promising perspective for package developers that are interested in understanding how their interfaces are being used in the wild by other software developers.
+In this paper, we have proposed a novel approach to making this sort of information accessible to package developers by automating the dependency collection and mining of usage samples from every dependency.
+We have identified two kinds of rich data sources for collecting downstream dependencies efficiently: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
+We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis beforehand.
+We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the Visual Studio Code IDE.
+
+Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent, and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
+However, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
+Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our usage samples mining approach as well as the efficacy of our tool.
+To answer the first question, source code repositories will need to be annotated manually with all usage samples to compare these annotations to the outputs of our implementation.
+To answer the second question, the best strategy would be to run a user study that compares the efficiency of package developers asked to solve a set of downstream dependency-related tasks with or without the help of our tool.
+
+We believe that our tool has further potential to support package developers in surveying downstream dependencies and thus have assembled a shortlist of open to-dos for the project:
+
+\begin{description}
+	\item[Expand applicability of the tool:]
+		Add support for further ecosystems and programming languages (e.g., JavaScript packages distributed over content delivery networks and imported from HTML; the Python/pip environment; the .NET ecosystem).
+		Our implementation already provides key abstractions that will facilitate the integration of other data sources.
+	\item[Optimize the dataflow:]
+		Store mined usage samples in a file system cache to reuse them in a later IDE session.
+		Reduce the number of UI updates to improve the performance and operability of the tool.
+	\item[Increase liveness of displayed data:]
+		Automatically reflect source code changes in the displayed package structure.
+		In JavaScript projects with separate typings, mirror the code annotations from the type definition files into the implementation files.
+	\item[Improve the integration of the extension:]
+		Convert the extension into a web extension to support browser environments such as github.dev.\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}}
+		Integrate the GitHub Remote Repositories extension for VS Code\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}} to make browsing dependencies more convenient.
+\end{description}
+
+In a wider perspective, we envision many other purposes for analyzing the collected downstream dependency data.
+By deriving usage patterns from the samples using an approach such as MAPO \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
+The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
+There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (for instance, according to their coupling to the target package (LCOM)), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.
+
+By replacing the static usage analysis with a dynamic approach, the detect usage samples could be enriched with valuable runtime data describing involved parameters, the fine-grained code coverage of package members, or the invocation context of members.
+Returning to the abstract problem that we have formulated in the introduction -- how can we improve developer knowledge about their packages' usage?
+--, further data sources next to source code files emerge that could be mined for package references, too.
+For instance, we are looking forward to mining the change history of projects for package-related changes (potentially indicating breaking changes), searching conversation platforms such as public issue trackers or Q\&A forums for mentions of package members and analyzing their sentiments (potentially indicating confusing behavior or bad documentation), or even scanning continuous integration logs for failure stack traces (potentially revealing bugs in the package of interest).

### 2021-10-02 docs/paper/sections/2_related_work.tex
Restructure paper: extract split up approach, merge implementation
Mention type analyis in related work

@@
 
-\subsection{Mining dependencies}
+\subsection{Searching dependency graphs}
 \label{sec:related_work/dependencies}
@@
 
-\subsection{Mining usage information}
-\label{sec:related_work/usage_information}
+\subsection{Extracting usage samples}
+\label{sec:related_work/usage_samples}
 
@@
 
-However, the precision of ASTs is limited for dynamically typed languages such as JavaScript.
-For this reason, a common data structure that can be used to improve type information are \emph{call graphs} that are either \emph{static} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamic} (i.e., empirically recorded during program execution).
-While the latter type has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
-There are many solutions that analyze the structure of programs and extract the relevant information to build call graphs:
+However, the precision of ASTs is limited for \emph{dynamically typed} languages such as JavaScript or Python.
+As opposed to static typing, the value type of an expression in a dynamically typed language may be unknown at the compile time of the program.
+For this reason, a \emph{type analysis} can be performed to predict the runtime types of all expressions in the AST \citep{jensen2009type}.
+Usually, this is accomplished by analyzing the control flow of a program and inferring the possible types of every variable or function.
+Another useful data structure for enhancing type information are \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
+While the latter method has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
+Many solutions exist that analyze the structure of programs and extract relevant information to build call graphs:
 

### 2021-10-02 docs/paper/sections/5_usage_mining.tex
Refactor and fix figure and footnote positioning
Fix footnote positioning; use ACM colors
Mention type analyis in related work

@@
 \begin{figure*}
-	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
-	\newcommand\highlight[1]{\textcolor{red}{#1}}
-	\centering
+	\begin{minipage}{\linewidth}
+		\newcommand\textlowlight[1]{\textcolor{gray}{#1}}
+		\newcommand\texthighlight[1]{\textcolor{accent1}{#1}}
+		\begin{center}
 			\begin{subfigure}[t]{.32\linewidth}
@@
 			\caption{AST patterns for example JavaScript/TypeScript expressions.
-		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
+				The \texthighlight{highlighted} node contains the link to the declaration of the referenced identifier.
 			}
 			\label{fig:usage_mining/patterns}
+		\end{center}
+	\end{minipage}
 \end{figure*}
-\input{sections/5_usage_mining/patterns/JsxOpeningElement.postfigure.tex}
 
@@
 The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
-\TODO{Elaborate on the topics type analysis and static/dynamic typing in related work/introduction.}
 

### 2021-10-02 docs/paper/sections/1_introduction.tex
Prove bad consequences of knowledge deficits in introduction

@@
 While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} -- is often neglected by package developers when they extend, restructure, or refactor their solutions.
-This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces, unidentified defects, and compatibility problems \citep[see][]{bogart2015breaks}.
-\TODO{do we need to prove each of this?}
+This knowledge deficit can cause a wide range of alignment issues, including poorly suited interfaces \citep{piccioni2013empirical}, unidentified defects \citep{wong2017more}, and compatibility problems \citep{bogart2015breaks}.
 Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.

### 2021-10-02 docs/paper/sections/3_framework.tex
paper: minor phrasing and typesetting improvements
Complements c8b4220099ad8ca7bed862217d56dbd39dc2f602

@@
 \begin{enumerate}[label=Q\arabic*]
-	\item Which dependencies are using the target package, and what problems do they attempt to solve with it?
-	\item By how many dependencies is a particular package member being used?
-	\item In which contexts and constellations is a particular package member being used?
+	\item \label[question]{q1} Which dependencies are using the target package, and what problems do they attempt to solve with it?
+	\item \label[question]{q2} By how many dependencies is a particular package member being used?
+	\item \label[question]{q3} In which contexts and constellations is a particular package member being used?
 \end{enumerate}
@@
 In essence, our proposed approach to collect the required data while fulfilling these requirements consists of three steps:
-\begin{enumerate*}
+\begin{enumerate*}[label=(\roman*)]
 	\item collect downstream dependency repositories,

### 2021-10-02 docs/paper/sections/1_introduction.tex
Minor improvements to phrasing and layout

@@
 Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
-Other solutions or packages can then \emph{depend} on existing packages.
+Other solutions or packages can then \emph{depend} on existing packages by declaring them in their manifest, i.e., the \code{package.json} file of an npm package, or the \code{requirements.txt} file of a Python project.
 These dependency relations form a large directed graph that connects major parts of the software world for each popular programming language ecosystem.
@@
 Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
-In the following, downstream dependencies will also be referred to shortly as \emph{dependencies}.
+In the following, we also refer to downstream dependencies will shortly as \emph{dependencies}.
 
@@
 In \cref{sec:framework}, we outline the overall conditions and the general approach for our solution to mining downstream dependencies.
-In \cref{sec:dependency_collection} and \cref{sec:usage_mining}, we explain our approach for collecting downstream dependency repositories resp. mining usage data from these repositories in detail.
+In \cref{sec:dependency_collection} and \cref{sec:usage_mining}, we explain our approach for collecting downstream dependency repositories and mining usage data from these repositories in detail, resp.
 In \cref{sec:implementation}, we describe an implementation of the proposed approach and our design decisions for displaying usage samples to the user.

### 2021-10-02 docs/paper/sections/2_related_work.tex
Minor improvements to phrasing and layout

@@
 This is done by \citet{kikas2017structure} which apply their methodology to the JavaScript, Ruby, and Rust ecosystems and gain statistical insights into the centrality and evolution of these ecosystems.
-\citet{decan2018impact} pursue a similar approach in order to measure the spreading of security vulnerabilities along the chain of downstream dependencies.
+\citet{decan2018impact} pursue a similar approach to measure the spreading of security vulnerabilities along the chain of downstream dependencies.
 
@@
 Dependency graphs do not provide information about package usage on a finer granularity, so reference insights about single package members such as classes or methods remain unknown.
-The process of extracting fine-granular information about all references to individual elements of an interface is often referred to as \emph{API usage analysis}.
+The process of extracting fine-grained information about all references to individual elements of an interface is often referred to as \emph{API usage analysis}.
 A simple approach to this problem is to perform a string search for package names or members in the dependencies \citep{mileva2010mining}.
-\citet{qiu2016understanding} propose a more elaborated approach that operates on the \emph{abstract syntax tree} (AST) of each parsed dependency to avoid false positive matches that can be caused by ambivalent identifier names.
-A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data in order to analyze the historical importance of certain features supported by an API.
+\citet{qiu2016understanding} propose a more elaborated approach that operates on the \emph{abstract syntax tree} (AST) of each parsed dependency to avoid false positive matches caused by ambivalent identifier names.
+A very similar approach is also chosen by \citet{sawant2017fine} who evaluate the collected usage data to analyze the historical importance of certain features supported by an API.
 
@@
 
-\citet{collard2013srcml} propose an infrastructure called \caps{srcML} that is aimed to create a unified representation of multilingual source code snippets for arbitrary analysis purposes, including the construction of call graphs.
+\citet{collard2013srcml} propose an infrastructure called \caps{srcML} that aims to create a unified representation of multilingual source code snippets for arbitrary analysis purposes, including the construction of call graphs.
 Another solution is proposed by \citet{bogar2018lightweight} who focus on analyzing multilingual codebases and who utilize an island parser to build call graphs.
@@
 To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
-\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and perform an impact analysis for vulnerabilities based on their graph; a very similar method is described by \citet{boldi2020fine} to formulate the vision of new design for package management systems that provides options for finer-granular reuse of solutions.
+\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and conduct an impact analysis for vulnerabilities based on their graph; a very similar method is described by \citet{boldi2020fine} to formulate the vision of a new design for package management systems that provides options for finer-grained reuse of solutions.
 \citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance.
@@
 For Java/Maven, \citet{keshani2021scalable} proposes another solution.
+Another approach is implemented in the \emph{precise code intelligence} feature of the Sourcegraph code search engine that makes code references explorable across repository boundaries for repositories that provide a metadata file in the \emph{Language Server Index Format}.\footnote{\url{https://docs.sourcegraph.com/code_intelligence/explanations/precise_code_intelligence}}
 
 After collecting these usage data, additional processing is possible to extract general usage information from the extensive raw data.
-Next to straightforward grouping and counting operations, such aggregations can be built by detecting popular \emph{usage patterns} of API features in the downstream dependencies.
+Next to trivial grouping and counting operations, such aggregations can be built by detecting popular \emph{usage patterns} of API features in the downstream dependencies.
 \citet{zhong2009mapo} propose a framework to do so that, for instance, finds sequences of API members that are invoked frequently and even uses these patterns for guiding API users by giving them recommendations.
@@
 A common approach for this is a hierarchical and navigatable representation of the collected call tree.
-The first form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
+An early form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
 Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.

### 2021-10-02 docs/paper/sections/3_framework.tex
Minor improvements to phrasing and layout

@@
 
-Furthermore, we pose two organizational requirements to the tool solution to ensure its practical applicability for the target user group:
+Furthermore, we pose two organizational requirements to the eventual tool solution to ensure its practical applicability for the target user group:
 
 \begin{enumerate}[label=R\arabic*]
-	\item \label[requirement]{req1} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
+	\item \label[requirement]{req1} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources.
 	\item \label[requirement]{req2} The tool blends in with the usual workflow of package developers at the best possible rate.

### 2021-10-02 docs/paper/sections/4_dependency_collection.tex
Minor improvements to phrasing and layout

--- 2021-09-17 docs/paper/sections/4_dependency_collection.tex
@@
 In the first step, a list of repositories that depend on the target package has to be assembled.
-As mentioned in \cref{sec:related_work/usage_samples}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
+As mentioned in \cref{sec:related_work/usage_samples}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem, which they then iterate over to filter the relevant repositories.
 However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
-This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.
+This approach is suited for analyzing repositories on a large scale but is not conform to \cref{req1} because of its large footprint in terms of computational power and time.
 
@@
 \begin{enumerate}[label=(\roman*)]
-	\item Package repositories that maintain a doubly-connected edge list of all packages in an ecosystem depending on each other.
+	\item Package repositories that maintain a doubly-connected edge list of all interdependent packages in an ecosystem.
 	\item Code search engines that index the source code of many repositories from OSS platforms.
-		Using these search engines, we can query all repositories that declare a dependency on the target package in their package metadata file.
+		Using these search engines, we can query all repositories that declare a dependency on the target package in their package manifest file.
 \end{enumerate}

### 2021-10-02 docs/paper/sections/5_usage_mining.tex
Minor improvements to phrasing and layout

@@
 Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
-Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.
+Our goal is to collect fine-grained source code excerpts that reference single identifiers exposed by the target package.
 
-To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate abstract syntax forest (ASF, i.e., a set of ASTs).
-
-In a second step, a static type analysis is performed against each dependency ASF together with the target package's ASF.
-The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
-For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function.
-\TODO{Give example?}
-The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
-
-In the final step, from each ASF all nodes are collected whose type is declared in the target package.
-To identify these links, we define a set of language-specific patterns for AST subtrees that constitute a usage expression.
-In particular, each of these patterns expects a node containing a link to an identifier declaration (see \cref{fig:usage_mining/patterns}).
-
-The complete procedure is displayed in \cref{alg:usage_mining}.
-
-\begin{algorithm}
+\begin{algorithm}[b]
 	\caption{Extraction of usage samples.}\label{alg:usage_mining}
@@
 \end{algorithm}
+
+To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate abstract syntax forest (ASF, i.e., a set of ASTs).
+
+In a second step, we perform a static type analysis against each dependency ASF together with the target package's ASF.
+The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
+For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function.
+The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
+
+In the final step, from each ASF, we collect all nodes whose type is declared in the target package.
+To identify these links, we define a set of language-specific patterns for AST subtrees that constitute a usage expression.
+In particular, each of these patterns expects a node containing a link to an identifier declaration (see \cref{fig:usage_mining/patterns}).
+
+The complete procedure is displayed in \cref{alg:usage_mining}.

### 2021-10-02 docs/paper/sections/6_implementation.tex
Minor improvements to phrasing and layout

@@
 
-In our implementation, we are restraining ourselves to analyzing node.js projects written in JavaScript.
+In our implementation, we confine ourselves to analyzing node.js projects written in JavaScript.
 This decision is based on the large prevalence of JavaScript\footnote{GitHut 2.0: A small place to discover languages in GitHub.
 \url{https://madnight.github.io/githut/\#/pushes}} as well as the first-rate extent of the npm ecosystem\footnote{Modulecounts: \url{http://www.modulecounts.com/}} which has been unsurpassed since 2015.
-In the following, we are describing how we apply the single steps of the approach presented above to this particular domain.
+In the following, we describe how we apply the single steps of the approach presented above to this particular domain.
 
@@
 
-The de facto standard package repository for node.js packages is npm.\footnote{\url{https://www.npmjs.com/}}
-To fetch downstream dependency packages from the npm registry, we utilize the npm package npm-dependants\footnote{\url{https://www.npmjs.com/package/npm-dependants}} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
+The de facto standard package repository for node.js is npm.\footnote{\url{https://www.npmjs.com/}}
+To fetch downstream dependency packages from the npm registry, we use the npm package npm-dependants\footnote{\url{https://www.npmjs.com/package/npm-dependants}} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
 To keep the footprint of our implementation small, we only scrape a part of the dependents list.
@@
 	"version": "1.10.0",
-	"description": "A TypeScript/JavaScript API for interacting with the XRP Ledger",
+	"description": "An API for the XRP Ledger",
 	"dependencies": {
@@
 npm packages specify their dependencies in a package.json metadata file (see \cref{sec:implementation/package.json}).
-To find all packages depending on a package \code{<pkg>}, we can search all available package.json files for the substring \code{"<pkg>":}.
+To find all packages depending on a package with the name \code{<pkg>}, we can search all available package.json files for the substring \code{"<pkg>":}.
 Refined with some additional constraints to filter out package copies from \code{node\_modules} folders that downstream developers have pushed accidentally, and to limit the number of results retrieved, our final Sourcegraph query has the following form:
@@
 
-We submit this search query by sending it to the publicly available Sourcegraph GraphQL API.\footnote{\url{https://docs.sourcegraph.com/api/graphql}}
+We submit this search query by sending it to the publicly available Sourcegraph GraphQL API\footnote{\url{https://docs.sourcegraph.com/api/graphql}} by using the npm package graphql-request\footnote{\url{https://www.npmjs.com/package/graphql-request}}.
 For each hit, we request additional information from the API about the matched repository, including the name of the depending package and the URL to the original repository.
-We use the npm package graphql-request\footnote{\url{https://www.npmjs.com/package/graphql-request}} for accessing the GraphQL API.
-After retrieving a search result, we download a snapshot of the full repository by using the download-git-repo package\footnote{\url{https://www.npmjs.com/package/download-git-repo}} which combines access to the APIs of different code host providers such as GitHub or BitBucket.
+After retrieving a search result, we download a snapshot of the full repository by using the download-git-repo package\footnote{\url{https://www.npmjs.com/package/download-git-repo}} which unifies access to the APIs of different code host providers such as GitHub or BitBucket.
 
@@
 
-In our solution, we are focusing on mining usage samples from downstream dependencies that are written in JavaScript or TypeScript.
-\TODO{Is this the right place to introduce TypeScript?}
-TypeScript is an extension of JavaScript that adds strong typing to the former which is based on a combination of implicit type inference and explicit type declarations.
+For parsing the dependencies, we utilize the public TypeScript Compiler API.\footnote{\url{https://github.com/Microsoft/TypeScript/wiki/Using-the-Compiler-API}}
+TypeScript is an extension of JavaScript that adds strong typing to the former; typing is based on a combination of implicit type inference and explicit type declarations.
 As the type-checking capabilities of the TypeScript compiler are optional and can be turned off via configuration, we consider the JavaScript syntax a subset of TypeScript syntax.
+As a side benefit, our implementation is also able to analyze packages implemented in true TypeScript.
 
-For parsing the dependencies, we utilize the public TypeScript Compiler API.\footnote{\url{https://github.com/Microsoft/TypeScript/wiki/Using-the-Compiler-API}}
 The TypeScript compiler's \emph{binder} component annotates every node of the parsed program with a type symbol if it can resolve one.
 After performing a type analysis of the dependency by instrumenting the binder, we collect all nodes from the type-annotated ASF that refer to the target package by traversing it with a visitor function.
-This visitor function matches each node against a list of defined patterns (similar to \cref{fig:usage_mining/patterns}) based on the \code{syntaxKind}s of the node and its ancestors and descendants and then looks up the declaration of the node's type symbol to compare it with the source directory of the target package.
+This visitor function matches each node against a list of defined patterns (similar to \cref{fig:usage_mining/patterns}) based on the syntax kinds of the node, its ancestors, and its descendants, and then looks up the declaration of the node's type symbol to compare it with the source directory of the target package.
 
@@
 To do so, we extend the \code{paths} parameter from the default compiler options\footnote{\url{https://www.typescriptlang.org/tsconfig\#paths}} and insert a new entry that remaps accesses to the target package name to the separate source code directory of the target package.
+
+\begin{figure*}[b]
+	\centering
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/6_implementation/extension/dependencies.png}
+		\caption[LoF entry]{The dependency browser.}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/6_implementation/extension/references.png}
+		\caption[LoF entry]{The usage browser.}
+		\label{fig:implementation/presentation/screenshot/usage_browser}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/6_implementation/extension/codelens.png}
+		\caption[LoF entry]{The CodeLens integration for the class \code{GraphQLError}.}
+	\end{subfigure}
+
+	\caption{Screenshots of our Visual Studio Code extension used to explore downstream dependencies of the npm package graphql.}
+	\label{fig:implementation/presentation/screenshots}
+\end{figure*}
 
@@
 One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code.\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
-As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.
-
-\begin{figure*}[b]
-	\centering
-	\begin{subfigure}{.32\linewidth}
-		\includegraphics[width=\textwidth]{sections/6_implementation/extension/dependencies.png}
-		\caption[LoF entry]{The dependency browser.}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{.32\linewidth}
-		\includegraphics[width=\textwidth]{sections/6_implementation/extension/references.png}
-		\caption[LoF entry]{The usage browser.}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{.32\linewidth}
-		\includegraphics[width=\textwidth]{sections/6_implementation/extension/codelens.png}
-		\caption[LoF entry]{The CodeLens integration for the class \code{GraphQLError}.}
-	\end{subfigure}
-
-	\caption{Screenshots of our Visual Studio Code extension used to explore downstream dependencies of the npm package graphql.}
-	\label{fig:implementation/presentation/screenshots}
-\end{figure*}
+As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.\footnote{To support other researchers in reusing our solution, we also provide a CLI for our implementation.}
 
@@
 Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
-In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm feeling lucky'' button for every view that redirects the user to a random dependency resp.
-reference to gain a faster, unbiased impression of usage samples.
+In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm feeling lucky'' button for every view that redirects the user to a random dependency or reference, resp., to gain a faster, unbiased impression of usage samples.
 
 We implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the Tree View API and the CodeLens API.
-One challenge was to deliver fast results and not to block the user interface because even though the lightweight mining approaches we chose to satisfy \cref{req1} above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation/TODO}).
-To overcome this issue, we use pagination wherever possible and applied the observer pattern to push incremental UI updates.
-As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our data model using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting inside the data collection process.
+One challenge has been to deliver fast results and not to block the user interface because even inspite of the lightweight mining approaches we chose to satisfy \cref{req1} above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation}).
+To overcome this issue, we use pagination wherever possible and apply the observer pattern to push incremental UI updates.
+As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our object model by using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting inside the data collection process.

### 2021-10-02 packages/core/src/dowdep.ts
Correct limit calculation for multiple depency searchers

@@ -41,7 +41,7 @@ export class Dowdep {
             : this.dependencySearchStrategies
         
         return strategies.map(strategy => createDependencySearcher(strategy, $package, {
-            limit: this.dependencyLimit
+            limit: this.dependencyLimit ? this.dependencyLimit / strategies.length : this.dependencyLimit
         }))
     }
 

### 2021-10-02 packages/core/src/dependencies/sourcegraph.ts
Escape sourcegraph query arguments
Includes module import workaround for https://github.com/microsoft/vscode/issues/130367 and https://github.com/microsoft/TypeScript/issues/43329 🤯

@@ -1,6 +1,6 @@
 import { strict as assert } from 'assert'
-import _ from 'lodash'
 import { gql, GraphQLClient } from 'graphql-request'
+import _ from 'lodash'
 import normalizePackageData from 'normalize-package-data'
 
 import { Dependency, DependencySearcher } from './base'
@@ -133,15 +133,16 @@ class SourcegraphClient {
 
         const queryArgs: Record<string, string> = {
             'select': 'file',
-            'file': 'package.json',
+            'file': 'package\\.json',
             '-file': 'node_modules/',
             'count': `${limit || this.maximumLimit}`
         }
+        // Workaround for https://github.com/microsoft/vscode/issues/130367 and https://github.com/microsoft/TypeScript/issues/43329 🤯
+        const dynamicImport = new Function('moduleName', 'return import(moduleName)')
+        const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
+        const query = `"${escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
         const response = this.documentSpecifier.protoResponse
-        console.log("query", `"${packageName}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' '))
-        Object.assign(response, await graphql.request(this.documentSpecifier.document, {
-            query: `"${packageName}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
-        }))
+        Object.assign(response, await graphql.request(this.documentSpecifier.document, { query }))
 
         const results = response.search.results
         if (results.timedout.length) {

### 2021-10-02 packages/core/src/dowdep.ts
Fix: Unless specified, use all datasources for dependency search

@@ -37,9 +37,9 @@ export class Dowdep {
 
     createDependencySearchers($package: Package): readonly DependencySearcher[] {
         const strategies = this.dependencySearchStrategies == '*'
-            ? <['sourcegraph']>['sourcegraph']
+            ? <['npm', 'sourcegraph']>['npm', 'sourcegraph']
             : this.dependencySearchStrategies
-        
+
         return strategies.map(strategy => createDependencySearcher(strategy, $package, {
             limit: this.dependencyLimit ? this.dependencyLimit / strategies.length : this.dependencyLimit
         }))

### 2021-10-02 packages/core/src/dependencies/base.ts
Exclude too large repositories from reference search

@@ -24,6 +24,8 @@ export class Dependency {
     rootDir = '/'
     pluggableUrls = new Map<string | null, string>()
     _references: Reference[] = []
+    /** In kilobyte (kB). */
+    static maximumRepositorySize = 500_000
     get githubUrl() {
         return [...this.urls.entries()].find(([key, ]) => key.toLowerCase() === 'github')?.[1]
     }
@@ -94,17 +96,23 @@ export class Dependency {
         } else {
             repo = this.urls.values().next().value
         }
+
+        if (this.githubRepository?.diskUsage ?? 0 > Dependency.maximumRepositorySize) {
+            console.warn("Repository is too large, skipping download", this.githubUrl)
+            return false
+        }
+
         // TODO: Use dowdep.fileSystem!
         await promisify(downloadGitRepo)(repo, basicSourceDirectory)
         return true
     }
 
     private *collectUpdateJobs(dowdep: Dowdep, options: Partial<DependencyUpdateOptions> = {}) {
-        if (options.downloadMetadata ?? true) {
-            yield () => this.updateFromGithub(dowdep)
-        }
-        if (options.downloadSource ?? false) {
-            yield () => this.updateSource(dowdep)
+        yield async () => {
+            await this.updateFromGithub(dowdep, options.downloadMetadata ?? true)
+            if (options.downloadSource ?? false) {
+                await this.updateSource(dowdep)
+            }
         }
     }
 
@@ -126,7 +134,7 @@ export class Dependency {
         }
     }
 
-    async updateFromGithub(dowdep: Dowdep) {
+    async updateFromGithub(dowdep: Dowdep, richMetadata: boolean) {
         const match = this.githubUrl?.match(/github\.com[/:](?<owner>[^/]+)\/(?<name>[\w-_.]+?)(?:.git)?$/)
         if (!match?.groups) {
             this.githubRepository = null
@@ -134,7 +142,7 @@ export class Dependency {
         }
 
         this.githubRepository = new GithubRepository(match.groups.owner, match.groups.name)
-        await this.githubRepository.updateMetadata(dowdep)
+        await this.githubRepository.updateMetadata(dowdep, richMetadata)
         return true
     }
 }
@@ -166,18 +174,20 @@ export class GithubRepository {
     ) { }
 
     public url?: string
+    public diskUsage?: number
     public stargazerCount?: number
     public forkCount?: number
 
-    async updateMetadata(dowdep: Dowdep) {
+    async updateMetadata(dowdep: Dowdep, richMetadata: boolean) {
[…]

### 2021-10-08 docs/paper/sections/0_abstract.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

--- 2021-09-17 docs/paper/sections/0_abstract.tex
@@
 	\begin{enumerate*}[label=(\roman*)]
-		\item We propose an approach for mining usage data about packages from their downstream dependencies by utilizing a static type analyzer.
-		\item We introduce a tool that allows npm package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an integrated development environment.%
+		\item We propose an approach for gathering downstream dependencies of a single package efficiently and extracting usage samples from them by utilizing a static type analyzer.
+		\item We introduce a tool that allows npm package developers to survey usage samples of their APIs by incorporating the aggregated usage data into an IDE.%
 			\footnote{
@@
 	\end{enumerate*}
-	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that they can be useful to support package developers in improving or extending their APIs.
+
+	Our two methods yield over \num{8000} dependencies for popular packages at an average precision of \SI{98.7}{\percent} or \SI{68.4}{\percent}, resp., but tend to exclude unpopular dependencies.
+	The extracted usage samples have a high precision but are unavailable for repositories with complex build configurations or metaprogramming patterns.
+	Our tool is able to process up to 12 dependencies per minute while requiring about \SI{500}{\mega\byte} RAM in total and less than \SI{30}{\mega\byte} ROM per package.
+	We find that usage data from downstream dependency repositories are a promising source of information for mining software repositories and that our approach could support package developers in improving or extending their APIs.
 

### 2021-10-08 docs/paper/sections/1_introduction.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

@@
 Especially, this trend has been experiencing an additional updraft due to the ongoing spreading of OSS platforms such as GitHub or GitLab.
-Open-source development offers many advantages as opposed to traditional closed-source development, including large numbers of volunteer contributions from the open-source community, increased transparency effects in security-related domains, and a high potential for reusing solutions.
-These solutions are usually organized as \emph{packages} each of which attempts to solve an isolated problem and provide a generic interface.
-Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript/TypeScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for languages from the .NET ecosystem).
+Open-source development offers many advantages as opposed to traditional closed-source development, including volunteer contributions from the open-source community, increased transparency effects in security-related domains, and a high potential for reusing solutions.
+These solutions are usually organized as \emph{packages} each of which attempts to solve an isolated problem and provide a generalized interface.
+Most commonly, packages are developed in a \emph{code repository} that is managed using a \emph{development platform} (such a \emph{GitHub}\footnote{\url{https://github.com/}}, \emph{GitLab}\footnote{\url{https://gitlab.com/}}, or \emph{Bitbucket}\footnote{\url{https://bitbucket.com/}}) and deployed to a \emph{package repository} using a \emph{package manager} (such as \emph{PyPI}\footnote{\url{https://pypi.org/}} using \emph{pip}\footnote{\url{https://pip.pypa.io/}} for the Python programming language, the \emph{npm registry}\footnote{\url{https://www.npmjs.com/}} for JavaScript, or the \emph{NuGet Gallery}\footnote{\url{https://www.nuget.org/}} for .NET languages).
 Other solutions or packages can then \emph{depend} on existing packages by declaring them in their manifest, i.e., the \code{package.json} file of an npm package, or the \code{requirements.txt} file of a Python project.
@@
 Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality products.
-In the following, we also refer to downstream dependencies will shortly as \emph{dependencies}.
+In the following, we also refer to downstream dependencies shortly as \emph{dependencies}.
 
@@
 
+In essence, our proposed approach consists of three steps:
+\begin{enumerate*}[label=(\roman*)]
+	\item collect downstream dependency repositories from public clouds,
+	\item mine package usage samples from these dependencies by using a type analyzer,
+	and \item aggregate and present these usage data to the user.
+\end{enumerate*}
+
 The rest of this paper is organized as follows:
 In \cref{sec:related_work}, we give a summary of existing approaches in this field.
-In \cref{sec:framework}, we outline the overall conditions and the general approach for our solution to mining downstream dependencies.
-In \cref{sec:dependency_collection} and \cref{sec:usage_mining}, we explain our approach for collecting downstream dependency repositories and mining usage data from these repositories in detail, resp.
+In \cref{sec:approach}, we outline the overall conditions for our solution and explain our approach for collecting downstream dependency repositories and mining usage data from these repositories.
 In \cref{sec:implementation}, we describe an implementation of the proposed approach and our design decisions for displaying usage samples to the user.

### 2021-10-08 docs/paper/sections/2_related_work.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

@@
-\section{Related work}
+\section{Related Work}
 \label{sec:related_work}
@@
 
-\subsection{Searching dependency graphs}
+\paragraph{Searching dependency graphs}
 \label{sec:related_work/dependencies}
@@
 However, existing research about dependency graphs primarily takes a broad statistical perspective, and researchers often rely on a large corpus of downloaded software repositories \citep{abdalkareem2017developers,katz2020libraries,kikas2017structure}.
-As opposed to this approach, these capacities will not be appropriate for scenarios that are occasionally performed by developers of a single package only.
-In this case, developers will often use a public \emph{code search} service such as GitHub code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or Sourcegraph\footnote{\url{https://sourcegraph.com/}} instead.
-\citet{liu2020opportunities} provide a (not yet published) survey of current methods and trends in code search tools that include, besides simple full-text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.
+As opposed to this approach, these capacities will not be appropriate for scenarios occasionally performed by developers of a single package only.
+In this case, developers will often use a public \emph{code search} service such as \emph{GitHub} code search\footnote{\url{https://docs.github.com/en/github/searching-for-information-on-github}} or \emph{Sourcegraph}\footnote{\url{https://sourcegraph.com/}} instead.
+\citet{liu2020opportunities} provide a pre-printed survey of current methods and trends in code search tools that include, besides simple text search, newer approaches such as structural or semantic search queries, code similarity metrics, or Machine Learning methods.
 
-\subsection{Extracting usage samples}
+\paragraph{Extracting usage samples}
 \label{sec:related_work/usage_samples}
@@
 \citet{collard2013srcml} propose an infrastructure called \caps{srcML} that aims to create a unified representation of multilingual source code snippets for arbitrary analysis purposes, including the construction of call graphs.
-Another solution is proposed by \citet{bogar2018lightweight} who focus on analyzing multilingual codebases and who utilize an island parser to build call graphs.
+Another solution is proposed by \citet{bogar2018lightweight} who utilize an island parser to build polyglot call graphs.
 Furthermore, \citet{antal2018static} compare several call graph generators for JavaScript.
@@
 To bring together dependency graphs and call graphs, \emph{ecosystem call graphs} can be constructed by applying call graphs to entire ecosystems, crossing repository boundaries.
-\citet{hejderup2018software} propose an approach to do so for the JavaScript/npm ecosystem in which they also model the semantic version numbers of packages and conduct an impact analysis for vulnerabilities based on their graph; a very similar method is described by \citet{boldi2020fine} to formulate the vision of a new design for package management systems that provides options for finer-grained reuse of solutions.
-\citet{nielsen2021modular} elaborate on this work by developing a call graph generator tailored to this problem that comes with significant improvements in terms of recall and performance.
-\citet{wang2020empirical} describe a similar approach for the same ecosystem and apply it to the domain of locating security issues in a project's upstream dependencies.
-With \caps{Pr\"azi} (not yet peer-reviewed), \citet{hejderup2021praezi} also describe their implementation of a dependency-scale call graph for the Rust/Cratesio ecosystem in-depth.
-For Java/Maven, \citet{keshani2021scalable} proposes another solution.
+Many approaches apply this concept to different ecosystems, often aiming to conduct a fine-grained impact analysis for security vulnerabilities \citep{boldi2020fine,hejderup2018software,hejderup2021praezi,keshani2021scalable,nielsen2021modular,wang2020empirical}.
 Another approach is implemented in the \emph{precise code intelligence} feature of the Sourcegraph code search engine that makes code references explorable across repository boundaries for repositories that provide a metadata file in the \emph{Language Server Index Format}.\footnote{\url{https://docs.sourcegraph.com/code_intelligence/explanations/precise_code_intelligence}}
@@
 
-\subsection{Presentation of results}
+\paragraph{Presentation of results}
 \label{sec:related_work/presentation}
@@
 A common approach for this is a hierarchical and navigatable representation of the collected call tree.
-An early form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep[section~10.1f.]{goldberg1984smalltalk}.
-Modern alternatives include the \caps{Stacksplorer} \citep{karrer2011stacksplorer} or \caps{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
+An early form of this representation has been invented as the interactive ``message set'' tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \citep{goldberg1984smalltalk}.
+Modern alternatives include the \emph{Stacksplorer} \citep{karrer2011stacksplorer} or \emph{Blaze} \citep{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
 With a focus on exploring references to API members, \citet{de2013multi} propose a set of additional views, including hierarchical lists and word clouds for highly referenced identifiers.

### 2021-10-08 docs/paper/sections/3_approach.tex
Rework first sections (up to approach)
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

@@
-\section{Approach}
+\section{Downstream Dependency Mining}
 \label{sec:approach}
 
-Because of its superior popularity \TODO{prove}, in this work, we will confine ourselves to the JavaScript/npm ecosystem.
-Our goal is thus to develop a tool for npm package developers that displays an overview of the downstream dependencies and their details for a chosen package.
-Concretely, we pose the following key requirements to this tool:
+To improve the developers' knowledge about the usages of their packages, our goal is to build a system that allows package developers to survey the API usage of downstream dependencies for a chosen target package.
+Concretely, we have identified three common questions of package developers about the usage of their packages:
+
+\begin{enumerate}[label=Q\arabic*]
+	\item \label[question]{q1} Which dependencies are using the target package, and what problems do they attempt to solve with it?
+	\item \label[question]{q2} By how many dependencies is a particular package member being used?
+	\item \label[question]{q3} In which contexts and constellations is a particular package member being used?
+\end{enumerate}
+
+Furthermore, we pose two organizational requirements to the eventual tool solution to ensure its practical applicability for the target user group:
 
 \begin{enumerate}[label=R\arabic*]
-	\item \label{req1} The tool allows package developers to survey and explore the usages of individual package members.
-	\item The tool blends in well with the usual workflow of package developers.
-	\item \label{req3} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources for it to work.
+	\item \label[requirement]{req1} The tool runs out-of-the-box with a small footprint, without the user needing to perform any sophisticated setup steps or providing additional system resources.
+	\item \label[requirement]{req2} The tool blends in with the usual workflow of package developers at the best possible rate.
 \end{enumerate}
 
-In essence, our proposed approach to fulfill these requirements consists of three steps:
-\begin{enumerate*}
-	\item collect downstream dependency repositories,
-	\item mine package usage samples from them,
-	and \item aggregate and present these usage data to the user.
-\end{enumerate*}
-In the following, we will describe each step.
+In the following, we will describe both steps of our approach to collect the desired data.
 
-\subsection{Downstream dependency collection}
-\label{sec:approach/collection}
+\subsection{Downstream Dependency Collection}
+\label{sec:approach/dependency_collection}
 
 In the first step, a list of repositories that depend on the target package has to be assembled.
-As mentioned in \cref{sec:related_work/usage_information}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem which they then iterate over to filter the relevant repositories.
+As mentioned in \cref{sec:related_work/usage_samples}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem, which they then iterate over to filter the relevant repositories.
 However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
-This approach is suited for analyzing repositories in large scale but is not conform to \cref{req1} due to the large footprint in terms of computational power and time.
+This approach is suited for analyzing repositories on a large scale but is not conform to \cref{req1} because of its large footprint in terms of computational power and time.
 
-As an alternative, we have decided to apply significantly stricter pre-filtering to the set of repositories before downloading it to the local machine.
-For that, we have chosen two publicly available data sources:\footnote{
-	Other data sources that we have rejected include GitHub code search which has limited precision results and is not freely accessible programatically as well as the \emph{libraries.io} service \citep{katz2020libraries} whose downstream dependency search was inoperative at the time of writing.%
-}
+As an alternative, we have decided to apply significant pre-filtering to the set of repositories before downloading a subset of it to the local machine.
+For that, we have identified two types of data sources that are available in public clouds:
 
 \begin{enumerate}[label=(\roman*)]
-	\item The npm registry which maintains a doubly-connected edge list of all npm packages that depend on each other.
-	\item The code search engine \emph{Sourcegraph}\footnote{\url{https://sourcegraph.com/}} which is indexing repositories from most popular OSS platforms such as GitHub or GitLab.
-		Using this search engine, we can query all repositories that declare a dependency on the target package in their package metadata file.
+	\item Package repositories that maintain a doubly-connected edge list of interdependent packages in an ecosystem.
+	\item Code search engines that index the source code of many repositories from OSS platforms.
+		Using these search engines, we can query all repositories that declare a dependency on the target package in their package manifest file.
 \end{enumerate}
 
-Finally, we can download the source code for a small number of relevant repositories only.
+\subsection{Usage Sample Mining}
+\label{sec:approach/usage_mining}
 
-\subsection{Usage sample mining}
-\label{sec:approach/mining}
-
-\begin{figure*}[htb!]
-	\newcommand\lowlight[1]{\textcolor{gray}{#1}}
-	\newcommand\highlight[1]{\textcolor{red}{#1}}
-	\centering
+\begin{figure*}
+	\begin{minipage}{\linewidth}
+		\newcommand\textlowlight[1]{\textcolor{gray}{#1}}
+		\newcommand\texthighlight[1]{\textcolor{accent1}{#1}}
+		\begin{center}
 			\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/CallExpression}
+				\input{sections/3_approach/usage_mining/patterns/CallExpression}
 			\end{subfigure}
@@
 			\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/PropertyAccessExpression}
+				\input{sections/3_approach/usage_mining/patterns/PropertyAccessExpression}
 			\end{subfigure}
@@
 			\begin{subfigure}[t]{.32\linewidth}
-		\include{sections/3_approach_assets/patterns/JsxOpeningExpression}
+				\input{sections/3_approach/usage_mining/patterns/JsxOpeningElement}
 			\end{subfigure}
 
-	\caption{Example AST patterns for TypeScript programs.
-		The \highlight{highlighted} node contains the link to the declaration of the referenced identifier.
+			\caption{AST patterns for example JavaScript/TypeScript expressions.
+				The \texthighlight{highlighted} node contains the link to the declaration of the referenced identifier.
 			}
-	\label{fig:approach/mining/patterns}
+			\label{fig:approach/usage_mining/patterns}
+		\end{center}
+	\end{minipage}
 \end{figure*}
@@
 Having downloaded the selected downstream dependency repositories, we can proceed to extract usage samples for the target package from each dependency repository.
-Our goal is to identify these usage samples on a fine-granular level so that we can trace them down to the single identifiers that were exposed by the target package.
+Our goal is to collect fine-grained source code excerpts that reference single identifiers exposed by the target package.
+The complete procedure is displayed in \cref{alg:usage_mining}.
 
-To do so, we start by parsing the source code of every dependency repository as well as the source of the target package each into a separate AST.
+\begin{algorithm}[b]
+	\caption{Extraction of usage samples.}\label{alg:usage_mining}
 
-% TODO: use term "binding"?
-In a second step, every dependency AST is traversed together with the target package AST in order to create links between semantically related nodes, e.g., between an expression and the variable it is assigned to, or between a function call and the definition of this function.
+	\KwIn{\\\Indp
+		$\mli{pkg}$: target package \\
+		$\mli{dependencies}$: downstream dependencies}
+	\KwOut{usage samples (set of strings)}
+	\;
+	\For{$\mli{dep} \in \mli{dependencies}$}{
+		$\mli{asf} \gets \mtx{parse}(\mli{dep} \cup \mli{pkg})$\;
+	  	$\mtx{annotate\_types}(\mli{asf})$\;
+		\For{$\mli{ast} \in \mli{asf}$}{
+			\For{$\mli{node} \in \mli{dfs}(\mli{ast})$}{
+				\For{$\mli{pattern} \in \mli{patterns}$}{
+					\If{$\mli{pattern}.\mtx{matches}(\mli{node}) \wedge \mli{pkg}.\mtx{declares}(\mli{pattern}.\mtx{getType}(\mli{node}))$}{
+						\kwYield{$\mli{node}.\mtx{text}$}
+					}
+				}
+			}
+		}
+	}
+\end{algorithm}
 
-In the final step, we traverse the AST again and collect all nodes that are linked to a declaration in the target package.
-To identify these links, we define a number of patterns for node structures and look up the declaration of every matched node (see \cref{fig:approach/mining/patterns}).
+To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate abstract syntax forest (ASF, i.e., a set of ASTs).
 
-\subsection{Presentation of results}
-\label{sec:approach/presentation}
+In a second step, we perform a static type analysis against each dependency ASF together with the target package's ASF.
+The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
+For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function.
+The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
 
-After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
-To satisfy \cref{req2} and make our tool avaiable in the usual working environment of users, we implement it as an extension to a popular IDE.
-One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}.
-As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.
-
-For choosing appropriate views of the raw reference data, we have identified three common questions of package developers to answer each of which they require access to downstream dependencies and their usage samples:
-
-\begin{enumerate}[label=Q\arabic*]
-	\item Which dependencies do use the target package and what problems are they solving with it?
-	\item By how many dependencies is a particular package member being used?
-	\item In which contexts and constellations is a particular package member being used?
-\end{enumerate}
-
-To support developers in answering these questions and fulfill \cref{req1}, we have designed the following views for our extension:
-
-\begin{enumerate}[label=(\roman*)]
-	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
-	\item The \emph{usage browser} displays all public package member and, grouped for each member, all dependencies and their references to this member.
-	\item The \emph{CodeLens integration} provides quick access to a slice of the usage browser that is attached to the definition of each package member right in the source code editor.
-\end{enumerate}
-
-Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
-In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm felling lucky'' button for every view that redirects the user to a random dependency resp.
-reference to gain a faster, unbiased impression of usage samples.
+In the final step, from each ASF, we collect all nodes whose type is declared in the target package.
+To identify these links, we define a set of language-specific patterns for AST subtrees that constitute a usage expression.
+In particular, each of these patterns expects a node containing a link to an identifier declaration (see \cref{fig:approach/usage_mining/patterns}).

### 2021-10-08 docs/paper/sections/4_implementation.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

--- 2021-09-17 docs/paper/sections/6_implementation.tex
@@
 
-\subsection{Data collection}
-\label{sec:implementation/data_collection}
+In our implementation, we confine ourselves to analyzing JavaScript projects for node.js.
+This decision is based on the large prevalence of JavaScript\footnote{GitHut 2.0: A small place to discover languages in GitHub.
+\url{https://madnight.github.io/githut/\#/pushes}} as well as the first-rate extent of the npm ecosystem which has been unsurpassed since 2015\footnote{Modulecounts: \url{http://www.modulecounts.com/}}.
+In the following, we describe how we apply the single steps of the approach presented above to this domain.
 
-Foo!
+\subsection{Downstream Dependency Collection}
+\label{sec:implementation/dependency_collection}
 
-\subsection{Usage mining}
+The de facto standard package repository for node.js is npm.
+To fetch downstream dependency packages from the npm registry, we use the npm package \code{npm-dependants}\footnote{All packages can be retrieved from \url{npmjs.com}} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
+To keep the footprint of our implementation small, we only scrape a part of the dependents list.
+We then request basic metadata for each found package from the npm registry, including the \emph{tarball} URL of the latest package version, using the package \code{package-metadata}.
+Finally, we download and extract each tarball using the package \code{download-package-tarball}.
+
+\begin{lstlisting}[language=json,
+	label=sec:implementation/package.json,
+	caption={An example \code{package.json} file for the \code{ripple-lib} package specifying multiple dependencies (truncated).},
+	float=tpb,
+	floatplacement=tbp,
+	abovecaptionskip=-5pt
+]
+{
+	"name": "ripple-lib",
+	"version": "1.10.0",
+	"description": "An API for the XRP Ledger",
+	"dependencies": {
+		"bignumber.js": "^9.0.0",
+		"https-proxy-agent": "^5.0.0",
+		"jsonschema": "1.2.2"
+	}
+}
+\end{lstlisting}
+
+For the second approach based on a code search engine, we have identified Sourcegraph\footnote{\url{https://sourcegraph.com/}} as a promising platform.
+npm packages specify their dependencies in a package.json metadata file (see \cref{sec:implementation/package.json}).
+To find all packages depending on a certain package, we can search all available \code{package.json} files for a reference to this package identifier.
+We refine our search query with some additional constraints to filter out package copies from \code{node_modules} folders that downstream developers have pushed accidentally, and to limit the number of results retrieved.
+We submit this search query to the publicly available GraphQL\footnote{\url{https://graphql.com/}} API of Sourcegraph\footnote{\url{https://docs.sourcegraph.com/api/graphql}} by using the npm package \code{graphql-request}.
+After retrieving a search result, we download a snapshot of the full repository by using the package \code{download-git-repo}.
+
+Additionally, we enrich the metadata of each package with a few metrics indicating its popularity from the associated GitHub repository if specified.
+The GitHub API is accessed via the official \emph{octokit} library\footnote{\url{https://octokit.github.io/}}.
+
+\subsection{Usage Sample Mining}
 \label{sec:implementation/usage_mining}
 
-Foo!
+For parsing the dependencies, we utilize the \emph{TypeScript Compiler API}\footnote{\url{https://github.com/Microsoft/TypeScript/wiki/Using-the-Compiler-API}}.
+TypeScript is an extension of JavaScript that adds strong typing to the former; typing is based on a combination of implicit type inference and explicit type declarations.
+As the type-checking capabilities of the TypeScript compiler are optional and can be turned off via configuration, we consider the JavaScript syntax a subset of TypeScript syntax.
+As a side benefit, our implementation is also able to analyze packages implemented in true TypeScript.
 
-\subsection{Presentation of results}
+The TypeScript compiler's \emph{binder} component annotates every node of the parsed program with a type symbol if it can resolve one.
+After performing a type analysis of the dependency by instrumenting the binder, we collect all nodes from the type-annotated ASF that refer to the target package by traversing it with a visitor function.
+This visitor function matches each node against a list of defined patterns (similar to \cref{fig:approach/usage_mining/patterns}) based on the syntax kinds of the node, its ancestors, and its descendants, and then performs a lookup of the node's type symbol's declaration to compare it with the source directory of the target package.
+
+Normally, foreign types can only be resolved if they are declared in a dependency module that has been installed into the \code{node_modules} folder of the repository.
+Because downloading and installing all dependency modules for every downstream repository of the target package would increase the computational resources of the usage mining drastically and eventually violate \cref{req1}, we skip this step but instead modify the module resolution strategy of the TypeScript compiler host.
+To do so, we extend the \code{paths} parameter from the default compiler options\footnote{\url{https://www.typescriptlang.org/tsconfig\#paths}} and insert a new entry that remaps accesses to the target package name to the separate source code directory of the target package.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/4_implementation/extension/dependencies.png}
+		\caption[LoF entry]{The dependency browser.}
+		\label{fig:implementation/presentation/screenshot/dependency_browser}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/4_implementation/extension/references.png}
+		\caption[LoF entry]{The usage browser.}
+		\label{fig:implementation/presentation/screenshot/usage_browser}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{.32\linewidth}
+		\includegraphics[width=\linewidth]{sections/4_implementation/extension/codelens.png}
+		\caption[LoF entry]{The CodeLens integration for the class \code{GraphQLError}.}
+		\label{fig:implementation/presentation/screenshot/codelens}
+	\end{subfigure}
+
+	\caption{Screenshots of our VS Code extension used to explore downstream dependencies of the npm package graphql.}
+	\label{fig:implementation/presentation/screenshots}
+\end{figure*}
+
+\subsection{Presentation of Results}
 \label{sec:implementation/presentation}
@@
 After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
-To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to a popular IDE.
-One of the most popular IDEs that support JavaScript, and the one with the highest annual growth, is Visual Studio Code.\footnote{\url{https://code.visualstudio.com/}}\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
-As it also provides a comprehensive set of APIs for extension developers, we have decided to roll our tool out as a VS Code extension.
+To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to the \emph{Visual Studio Code} IDE\footnote{\url{https://code.visualstudio.com/}}.
+VS Code is one of the most popular IDEs that support JavaScript, and the one with the highest annual growth.\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
+It also provides a comprehensive set of APIs for extension developers.
+To support other researchers in reusing our solution, we also provide a CLI.
 
-To support developers in answering the questions raised in \cref{sec:framework}, we have designed the following views for our extension:
+To support developers in answering the questions raised in \cref{sec:approach}, we have designed three key views for our extension (see \cref{fig:implementation/presentation/screenshots}):
 
@@
 	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
-	\item The \emph{usage browser} displays all public package member and, grouped for each member, all dependencies and their references to this member.
-	\item The \emph{CodeLens integration} provides quick access to a slice of the usage browser that is attached to the definition of each package member right in the source code editor.
+	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
+	\item The \emph{CodeLens integration} provides quick access to a slice usage samples and is attached to the definition of each package member in the source code editor.
 \end{enumerate}
@@
 Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
-In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm felling lucky'' button for every view that redirects the user to a random dependency resp.
-reference to gain a faster, unbiased impression of usage samples.
+In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm feeling lucky'' button for every view that redirects the user to a random dependency or reference, resp., to gain a faster, unbiased impression of usage samples.
 
-Foo!
+We implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the \emph{Tree View API} and the \emph{CodeLens API}.
+One challenge has been to deliver fast results and not to block the user interface because even in spite of the lightweight mining approaches we chose to satisfy \cref{req1} above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation}).
+To overcome this issue, we use pagination wherever possible and apply the observer pattern to push incremental UI updates.
+As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our object model by using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting inside the data collection process.

### 2021-10-08 docs/paper/sections/5_evaluation.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

--- 2021-09-03 docs/paper/sections/7_evaluation.tex
@@
 
-Foo!
+To evaluate the efficacy of our approach, we formulate three research questions:
+
+\begin{enumerate}[label=RQ\arabic*]
+	\item \label[requirement]{resqu1} What is the quality and quantity of the proposed approaches for dependency collection?
+	\item \label[requirement]{resqu2} What is the quality and quantity of the proposed approach for mining usage samples?
+	\item \label[requirement]{resqu3} How well is the proposed tool applicable?
+\end{enumerate}
+
+In the following, we will investigate each question.
+
+\subsection{\ref{resqu1}: Dependency collection}
+\label{sec:evaluation/resqu1}
+
+To assess the quality of dependency collection, we analyze it with respect to extent, precision, recall, and performance.
+\Cref{tab:evaluation/resqu1/quantities} shows the number of dependencies that we collected to build an experimental dataset from each data source following the proposed approaches for a set of arbitrarily selected npm packages.
+For each package, we have annotated a subset of the collected dependencies (max. 20 dependencies per package) to identify and classify false positive hits.
+
+\begin{table}
+	\caption{Quantity and false-positive rates (FPR) of downstream dependencies found by both approaches for selected packages.}
+	\label{tab:evaluation/resqu1/quantities}
+
+	\centering
+	\small
+	\input{sections/5_evaluation/resqu1/quantities}
+\end{table}
+
+\paragraph{Extent}
+\label{sec:evaluation/resqu1/extent}
+
+Regarding the total number of dependencies collected by each approach, no clear trend in favor of any approach can be ascertained for small or medium packages (having less than \num{10,000} stars on GitHub).
+For larger packages (having at least \num{10,000} stars), however, the number of dependencies collected from the npm registry stagnates near to 400 hits; beyond this limit, the npm registry will return internal server errors only.
+For Sourcegraph, we have not hit any limitations so far; currently, they do not provide any official documentation for the exact rate limits.
+
+As the disjunct proportion of results from both approaches is very small (on average about \SI{6}{\percent}), we consider a combination of both data sources useful for maximizing the extent and diversity of the gained dataset.
+
+\paragraph{Precision}
+\label{sec:evaluation/resqu1/precision}
+
+The precision of collected dependencies is drastically lower for dependencies found on Sourcegraph than for such found on npm.
+\Cref{fig:evaluation/resqu1/fp_causes} collates the causes we have identified for false positives; most frequently, repositories specify a dependency on a target package in their package manifest file but do not import this package at any place.
+
+\begin{figure}
+	\centering
+	\small
+	% Fix font size of \thead
+	\renewcommand\theadfont{\small}
+	\input{sections/5_evaluation/resqu1/fp_causes}
+
+	\caption{Causes for false-positive dependency matches and their frequencies.}
+	\label{fig:evaluation/resqu1/fp_causes}
+\end{figure}
+
+In some situations, this may happen if the package is a plugin for another package or if it is invoked as a CLI from a build script, but in the majority of repositories, developers trivially appear to have specified the upstream dependency by accident (e.g., while copying a \code{package.json} file over from another package), or to have forgotten to remove the upstream dependency after switching away from using the package.
+Rarer causes include repositories that only add type definitions for TypeScript to a package but do not actually import it, as well as, especially for repositories found on Sourcegraph, other packages required by a repository declaring a peer dependency on the target package which needs to be fulfilled by the depending repository.
+
+We explain the increased false-positive rate for Sourcegraph dependencies by our observation that packages found on npm typically stand out by their higher cohesion and professional maintenance, whereas GitHub projects are more likely run as imperfect hobby projects.
+
+We stress that a reduced precision does not impair the quality of results displayed to package developers as all dependencies not containing at least one
+usage sample can be easily filtered out, but downloading and analyzing any irrelevant packages lowers the performance of the approach.
+
+\paragraph{Recall}
+\label{sec:evaluation/resqu1/recall}
+
+Besides the precision of collected dependencies, their recall is also of interest.
+As the dependencies are collected from two giant datasets in excerpts only, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
+Nevertheless, there are some causes that will prevent a dependency from being found by our approaches:
+
+\begin{itemize}
+	\item Packages without a proper dependency manifest cannot be detected by our approaches which are based on exactly these metadata.
+	\item On npm, only published packages will be found, creating a bias towards generic and professional software.
+	\item On both platforms, results will be sorted based on intransparent criteria (which, as we speculate, include the number of direct dependents on npm and the recent update frequency on Sourcegraph, resp.).
+		As we only fetch the first dependencies from both data sources, this is a likely source of further biases.
+		These could be fought by always fetching all dependencies, but this would drastically reduce the overall performance.
+\end{itemize}
+
+\paragraph{Performance}
+\label{sec:evaluation/resqu1/performance}
+
+\begin{table}
+	\caption{Key performance metrics for both dependency collection methods.}
+	\label{tab:evaluation/resqu1/performance}
+
+	\centering
+	\begin{threeparttable}
+		% Fix font size of \thead
+		\renewcommand\theadfont{\normalsize}
+		\input{sections/5_evaluation/resqu1/performance}
+		\begin{tablenotes}
+			\footnotesize
+			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \SI{2.80}{\giga\hertz}, internet downspeed ~\SI{1.8}{\giga\bit/\second}.
+			\item[\alphtnotetext{2}] Effective speed while downloading multiple packages in parallel.
+		\end{tablenotes}
+	\end{threeparttable}
+\end{table}
+
+\Cref{tab:evaluation/resqu1/performance} gives some basic metrics comparing the performance of both data sources.
+While searching downstream dependencies is slower by average on npm as we use a web scraper instead of an API for this source, npm packages are usually smaller as opposed to many monorepos on OSS platforms that contain multiple node.js packages, and they are faster to download since the download-git-repo package that we use for repositories found on Sourcegraph, as of today, only uses zipballs instead of tarballs while the latter would offer a higher compression rate.
+
+\subsection{\ref{resqu2}: Usage mining}
+\label{sec:evaluation/resqu2}
+
+To assess the quality of usage mining, we examine the precision, recall, and performance of this processing step.
+Due to the complexity of a detailed annotation process, we only consider the existence of found usage samples on the dependency level.
+The absolute quantity of found usage samples varies largely for different packages and dependencies based on the semantic extent of the package and the coupling between package and dependency.
+
+\paragraph{Precision}
+\label{sec:evaluation/resqu2/precision}
+
+Under laboratory conditions, false-positive usage samples cannot be emitted by our approach if we assume the correctness of the TypeScript compiler.
+There are only two exceptions to this invariant:
+\begin{enumerate*}[label=(\roman*)]
+	\item In case of a name collision between two packages, invalid or false positives usage samples may be emitted.
+		However, the npm infrastructure attempts to rule out these collisions by using the package name as a unique ID for every published package.
+	\item If dependency developers deliberately interfere with the TypeScript compiler (for instance, by suppressing type errors using a \verb|@ts-ignore| comment\footnote{\url{https://www.typescriptlang.org/docs/handbook/release-notes/typescript-2-6.html\#suppress-errors-in-ts-files-using--ts-ignore-comments}}), both false positive and false negative matches are possible.
+\end{enumerate*}
+
+Additionally, some npm packages contain minified sources only that are still searchable valid code but can provide a significantly reduced readability.
+
+\paragraph{Recall}
+\label{sec:evaluation/resqu2/recall}
+
+To evaluate the recall of our approach, we have refined the experimental dataset collected in \cref{sec:evaluation/resqu1} and removed all false-positive dependencies.
+Within this cleansed dataset, the overall rate of dependencies for that our approach is unable to find at least one usage sample accounts for \SI{47.9}{\percent}.
+As a cause for these false negatives, we have identified a number of systematic causes:
+
+\begin{itemize}
+	\item Many projects on OSS platforms have complex build configurations that include additional transpilation or code generation steps before a final version of the source code is reached that is valid to the node.js interpreter or the TypeScript compiler.
+		Unless we add explicit support for such build configurations, type analysis and usage mining for these projects will fail.
+	\item In some situations, additional type definitions are required to perform a complete type inference of a dependency.
+		This applies to every parametrized callback from a package for that type definitions are not available.
+		This limitation could be resolved by downloading or generating type definitions for all upstream dependencies of every downstream dependency; this, however, would reduce the performance of the approach.
+	\item In general, the static type analyzer of TypeScript has its limitations.
+		For instance, the type analysis will have a limited recall for certain control flow patterns or metaprogramming constructs such as meta-circular evaluation using the the \code{eval()} function or dynamic function binding using \code{Function.bind()} etc.
+\end{itemize}
+
+\paragraph{Performance}
+\label{sec:evaluation/resqu2/performance}
+
+The total time spent performing type analysis for a repository from the experimental dataset and mining usage samples averages ca. \num{3} seconds.
+The complete ASF of an average parsed repository consumes between \SI{10}{\mega\byte} and \SI{500}{\mega\byte} RAM, depending on the size of the repository.
+
+\subsection{\ref{resqu3}: Tool}
+\label{sec:evaluation/resqu3}
+
+To assess the applicability of our proposed tool, we investigate the different options of users who would like to answer the questions raised in \cref{sec:approach}.
+We further analyze how far our tool meets the requirements posed above.
+
+\paragraph{Answering User Questions}
+
+To answer \cref{q1} without our tool, users could access the aforementioned data sources manually to search for and view downstream dependencies.
+The source code of repositories can be browsed on Sourcegraph, but if an npm package is not available on an OSS platform, users will need to download and extract it.
+
+With our tool, the data collection process is condensed into a single button that displays all references from both data sources incrementally.
+Users can hover or click any dependency to view its documentation or implementation.
+
+To answer \cref{q2,q3} without our tool, users need to scan each found dependency separately to count or read all usage samples.
+If they are intending to analyze the usage of a member with an unambiguous name, they can perform an expeditious string search.
+This is possible using Sourcegraph if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
+If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
+Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for a small number of repositories only.
+
+Within our tool, all usage samples can be collected automatically and be merged into a single list.
+Once the collected dependencies have been processed, users can select a member of interest and view all its usage samples with a single click.
+For the usage analysis of Java APIs, the tool \emph{Exapus} \citep{de2013multi} also considers different kinds of member usages such as instantiation vs.
+inheritance of a class; a similar classification could also improve the usability of our tool.
+
+\paragraph{Meeting Requirements}
+
+We break down \cref{req1} into three acceptance criteria: application liveness, a small resource footprint, and an easy setup.
+
+As learned from the previous research questions, our tool is able to process 5 up to 12 dependencies per minute while requiring about \SI{500}{\mega\byte} RAM in total and less than \SI{30}{\mega\byte} ROM per package.
+After the tool is activated, the first results usually take less than 10 seconds to appear on the UI.
+This is an acceptable delay regarding Shneiderman's definition of acceptable application response times \citep{shneiderman2010designing}, so the liveness criterion is fulfilled.
+Even if the tool downloads a few hundred dependencies, it will occupy less than \SI{10}{\giga\byte} ROM that can be released at any time, which we consider a small resource footprint at a time where modern operating systems require \SI{64}{\giga\byte} ROM; thus, also the second acceptance criterion is fulfilled.
+As our extension can be installed with two clicks from the Visual Studio Code Extension Marketplace, it also fulfills the setup criterion and thus the first requirement.
+
+\Cref{req2} effectively calls for a minimum number of context switches that are required to use the tool, i.e., for minimizing the temporal, spatial, and semantic distance \citep{ungar1997debugging} between the downstream dependency UI and the IDE used by package developers.
+
+Once the data are available in the UI, interaction with them is possible with the same speed as with local source files in the package.
+This meets Shneiderman's requirement to frequent tasks and indicates a low temporal distance.
+
+The spatial distance varies for the different views of the tool:
+For the dependency browser and the usage browser, a separate toolbar has to be opened, which indicates a higher spatial distance; still, the artifacts are available in the same IDE.
+Also, the dependency artifacts have no strong relationship to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
+The code annotations are disaplyed close to the original source code with a small spatial distance.
+
+The semantic distance can be described as the perceived similarity of artifacts displayed both in the tool's UI and in the existing IDE, i.e., the package and dependency members.
+Most items in the usage browser bear the same label as the corresponding identifier in the source code, which reduces the semantic distance.
+However, dependency member path nodes that refer to anonymous source code expressions are displayed differently than in the outline view of VS Code (see \cref{fig:implementation/presentation/screenshot/dependency_browser}), increasing the semantic distance a bit.
+
+With a low temporal distance, a low-to-medium spatial distance, and a mainly low semantic distance, our tool also fulfills \cref{req2}.

### 2021-10-08 docs/paper/sections/6_conclusion.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting

--- 2021-09-03 docs/paper/sections/8_conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \label{sec:conclusion}
 
-Foo!
+Downstream dependencies provide a promising perspective for package developers that are interested in understanding how their interfaces are being used in practice by other software developers.
+In this paper, we have proposed a novel approach to making this sort of information accessible to package developers by automating the dependency collection and mining of usage samples from every dependency.
+We have identified two kinds of rich data sources for collecting downstream dependencies efficiently: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
+We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis beforehand.
+We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the Visual Studio Code IDE.
+
+Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent, and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
+However, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
+Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our approach for mining usage samples as well as the efficacy of our tool.
+As for the first question, manual annotation of source code repositories with usage samples will be required to compare them to the outputs of our implementation.
+Close insights for the second question could be gained from a user study that compares the efficiency of package developers asked to solve a set of downstream dependency-related tasks with or without the help of our tool.
+
+We believe that our tool has further potential to support package developers in surveying downstream dependencies and thus have assembled a shortlist of open to-dos for the project.
+Among others, we want to expand the applicability of the tool by adding support for further ecosystems and programming languages.
+The user experience of the tool could be improved by increasing the liveness of displayed data, for instance, by automatically reflecting source code changes.
+For better performance, usage samples could be cached, and finer-grained UI updates could be implemented.
+Last but not least, we want to improve the integration of the extension by adding support for browser environments such as github.dev\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}} and by connecting it to the GitHub Remote Repositories extension\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}}.
+
+In a wider perspective, we envision many other purposes for analyzing the collected downstream dependency data.
+By deriving usage patterns from the samples using an approach such \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
+The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
+There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package, LCOM), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.
+
+By replacing the static usage analysis with a dynamic approach, the detect usage samples could be enriched with valuable runtime data describing involved parameters, the fine-grained code coverage of package members, or the invocation context of members.
+Returning to the abstract problem that we have formulated in the introduction -- how can we improve developer knowledge about their packages' usage?
+--, further data sources next to source code files emerge that could be mined for package references, too.
+For instance, we are looking forward to mining the change history of projects for package-related changes (potentially indicating breaking changes), searching conversation platforms such as public issue trackers or Q\&A forums for mentions of package members and analyzing their sentiments (potentially indicating confusing behavior or bad documentation), or even scanning continuous integration logs for failure stack traces (potentially revealing bugs in the package of interest).

### 2021-10-08 packages/cli/src/DowdepCommand.ts
Document, restructure, and refactor core

@@ -1,7 +1,7 @@
 import filterAsync from 'node-filter-async'
 import { Command } from '@oclif/command'
 
-import { Dependency, DependencyUpdateOptions, Dowdep, getCacheDirectory, Package } from 'dowdep'
+import { Dependency, DependencyUpdateOptions, Dowdep, Package } from 'dowdep'
 
 export default abstract class DowdepCommand extends Command {
     async *updateDependencies(
@@ -16,7 +16,7 @@ export default abstract class DowdepCommand extends Command {
             dependencyLimit: limit,
             githubAccessToken: process.env.GITHUB_OAUTH_TOKEN,
             sourcegraphToken: process.env.SOURCEGRAPH_TOKEN,
-            sourceCacheDirectory: getCacheDirectory()
+            sourceCacheDirectory: this.cacheDirectory
         })
         const $package = new Package(packageName)
 
@@ -52,5 +52,9 @@ export default abstract class DowdepCommand extends Command {
             }
             yieldPromise = new Promise(resolve => yieldResolve = resolve)
         }
+    }
+
+    get cacheDirectory() {
+        return process.env.NPM_CACHE || 'cache'
     }
 }

### 2021-10-08 packages/cli/src/commands/download.ts

@@ -1,5 +1,5 @@
 import { flags } from '@oclif/command'
-import asyncIteratorToArray from 'it-all'
+import itAll from 'it-all'
 
 import DowdepCommand from '../DowdepCommand'
 import tqdm2 from '../utils/tqdm2'
@@ -35,7 +35,7 @@ export default class Download extends DowdepCommand {
             : <['npm', 'sourcegraph']>['npm', 'sourcegraph']
 
         // Processing
-        const dependencies = await asyncIteratorToArray(
+        const dependencies = await itAll(
             tqdm2(
                 this.updateDependencies(
                     packageName,

### 2021-10-08 packages/cli/src/commands/search.ts

@@ -1,13 +1,14 @@
 import * as _ from 'lodash'
-import { Command, flags } from '@oclif/command'
+import { flags } from '@oclif/command'
 import * as path from 'path'
 import * as util from 'util'
 
-import { getCacheDirectory, Package, Reference, ReferenceSearcher, ReferenceKind } from 'dowdep'
+import DowdepCommand from '../DowdepCommand'
+import { Package, Reference, ReferenceCollector, ReferenceKind, ReferenceSearchStrategy } from 'dowdep'
 import tqdm2 from '../utils/tqdm2'
 
 
-export default class Search extends Command {
+export default class Search extends DowdepCommand {
     static description = 'search downstream dependencies for package references'
 
     static flags = {
@@ -49,7 +50,10 @@ export default class Search extends Command {
         const packageName: string = args.packageName
         if (!packageName) throw new Error("dowdep-cli: Package not specified")
         const packageDirectory = flags.source || undefined
-        const strategy = flags.strategy
+        const strategy = <ReferenceSearchStrategy>flags.strategy
+        if (!['heuristic', 'types'].includes(strategy)) {
+            throw new Error("Invalid strategy")
+        }
         const includeImports = flags.includeImports
         const includeOccurences = flags.includeOccurences
         const aggregate = flags.aggregate
@@ -57,9 +61,9 @@ export default class Search extends Command {
 
         const $package = new Package(
             packageName,
-            packageDirectory ?? path.join(getCacheDirectory(), packageName)
+            packageDirectory ?? path.join(this.cacheDirectory, packageName)
         )
-        const searcher = new ReferenceSearcher($package, getCacheDirectory(), strategy)
+        const searcher = new ReferenceCollector($package, this.cacheDirectory, strategy)
         const includeKinds: ReferenceKind[] = ['usage']
         if (includeImports) {
             includeKinds.push('import')

### 2021-10-08 packages/core/src/dependencies/base.ts

@@ -13,6 +13,7 @@ import isDefined from '../utils/isDefined'
 import { OnlyData } from '../utils/OnlyData'
 
 
+/** A downstream dependency of a {@link Package}. */
 export class Dependency {
     constructor(
         public name: string,
@@ -28,7 +29,9 @@ export class Dependency {
     /** In kilobyte (kB). */
     static maximumRepositorySize = 100_000
     get githubUrl() {
-        return [...this.urls.entries()].find(([key, ]) => key.toLowerCase() === 'github')?.[1]
+        return [...this.urls.entries()].find((
+            [key, ]) => key.toLowerCase() === 'github'
+        )?.[1]
     }
     get isGitHubRepositoryReady() {
         if (_.isUndefined(this.githubRepository)) {
@@ -42,15 +45,20 @@ export class Dependency {
 
     get references() { return this._references }
     get urls() {
+        // Pretty-print URL labels
         const map = new Map<string, string>([...this.pluggableUrls.entries()].map(
             ([key, value]) => [key && ({"github": "GitHub"}[key] ?? key) || '?', value]
         ))
+
+        // Prefer official GitHub URL if available
         if (this.githubRepository?.url) {
             map.set("GitHub", this.githubRepository.url)
         }
+
         return map
     }
 
+    /** Update this dependency from multiple data sources as specified in the `options`. After each step, evauate `updateCallback`. */
     async update(dowdep: Dowdep, options: Partial<DependencyUpdateOptions> = {}, updateCallback?: DependencyUpdateCallback) {
         const jobs = [...this.collectUpdateJobs(dowdep, options)]
         await Promise.allSettled(jobs.map(async (job, index) => {
@@ -72,12 +80,13 @@ export class Dependency {
         return isDefined(this.sourceDirectory) && await dowdep.fileSystem.exists(this.sourceDirectory)
     }
 
+    /** Download the source code for this dependency from GitHub unless already cached. */
     async updateSource(dowdep: Dowdep): Promise<boolean> {
         if (!this.urls.size) {
             return false
         }
         if (await this.isSourceCodeReady(dowdep)) {
-            return true // TODO: What to return here?
+            return true
         }
 
         const cacheDirectory = dowdep.sourceCacheDirectory
@@ -91,7 +100,8 @@ export class Dependency {
         if (this.githubUrl) {
             const url = parseGitHubRepoUrl(this.githubUrl)
             if (!url) {
-                return false // TODO: Raise?
[…]

### 2021-10-08 packages/core/src/dependencies/index.ts

@@ -26,6 +26,10 @@ function dependencySearcher(strategy: DependencySearchStrategy) {
     }[strategy]
 }
 
-export function createDependencySearcher(strategy: DependencySearchStrategy, $package: Package, init: Partial<OnlyData<DependencySearcher>>) {
+export function createDependencySearcher(
+    $package: Package,
+    strategy: DependencySearchStrategy,
+    init: Partial<OnlyData<DependencySearcher>>
+) {
     return new (dependencySearcher(strategy))($package, init)
 }

### 2021-10-08 packages/core/src/dependencies/npm.ts

@@ -11,6 +11,7 @@ import { OnlyData } from '../utils/OnlyData'
 import { URL } from 'url'
 
 
+/** A downstream dependency of a {@link Package} that was retrieved from npm. */
 export class NpmDependency extends Dependency {
     tarballUrl?: string
 
@@ -32,6 +33,7 @@ export class NpmDependency extends Dependency {
         await super.update(dowdep, options, updateCallback)
     }
 
+    /** Download the source code of this dependency from the npm registry. */
     async updateSource(dowdep: Dowdep) {
         if (!this.tarballUrl) {
             return false
@@ -52,6 +54,7 @@ export class NpmDependency extends Dependency {
         return true
     }
 
+    /** Fetch metadata about this dependency from the npm registry. */
     async updateFromRegistry() {
         const metadata = await RegistryClient.getMetadata(this.name, { fullMetadata: true })
         const latestVersion = metadata.versions?.latest
@@ -82,6 +85,7 @@ export class NpmDependency extends Dependency {
     }
 }
 
+/** Finds downstream dependencies for a package in the npm ecosystem. */
 export class NpmDependencySearcher extends DependencySearcher {
     constructor($package: Package, init: Partial<OnlyData<NpmDependencySearcher>>) {
         super($package, init)

### 2021-10-08 packages/core/src/dependencies/sourcegraph.ts

@@ -9,6 +9,7 @@ import { Package } from '../packages'
 import { OnlyData } from '../utils/OnlyData'
 
 
+/** Finds downstream dependencies for a package on [Sourcegraph](sourcegraph.com). */
 export class SourcegraphDependencySearcher extends DependencySearcher {
     constructor($package: Package, init: Partial<OnlyData<SourcegraphDependencySearcher>>) {
         super($package, init)
@@ -145,9 +146,11 @@ class SourcegraphClient {
             '-file': 'node_modules/',
             'count': `${limit || this.maximumLimit}`
         }
+
         // Workaround for https://github.com/microsoft/vscode/issues/130367 and https://github.com/microsoft/TypeScript/issues/43329 🤯
         const dynamicImport = new Function('moduleName', 'return import(moduleName)')
         const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
+
         const query = `"${escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
         const response = this.documentSpecifier.protoResponse
         Object.assign(response, await graphql.request(this.documentSpecifier.document, { query }))

### 2021-10-08 packages/core/src/dowdep.ts

@@ -1,18 +1,15 @@
-import pathExists from 'path-exists'
 import path from 'path'
+import pathExists from 'path-exists'
 
 import { createDependencySearcher, Dependency, DependencySearcher, DependencySearchStrategy } from './dependencies'
 import { Package } from './packages'
-import { PackageReferenceSearcher, ReferenceSearchStrategy } from './references'
+import { createReferenceSearcher, ReferenceSearchStrategy } from './references'
 import { OnlyData } from './utils/OnlyData'
 
 
-export function getCacheDirectory() {
-    return process.env.NPM_CACHE || 'cache'
-}
-
+/** This is the starting point and configuration place for the downstream repository miner. */
 export class Dowdep {
-    constructor(init: Partial<OnlyData<Dowdep>>) {
+    constructor(init: Partial<OnlyData<Dowdep>> = {}) {
         Object.assign(this, init)
     }
 
@@ -40,17 +37,18 @@ export class Dowdep {
             ? <['npm', 'sourcegraph']>['npm', 'sourcegraph']
             : this.dependencySearchStrategies
 
-        return strategies.map(strategy => createDependencySearcher(strategy, $package, {
+        return strategies.map(strategy => createDependencySearcher($package, strategy, {
             limit: this.dependencyLimit ? Math.ceil(this.dependencyLimit / strategies.length) : this.dependencyLimit
         }))
     }
 
     createReferenceSearcher(dependency: Dependency, $package: Package) {
         // TODO: Do we still need $package param?
-        return PackageReferenceSearcher.create($package, dependency, this.referenceSearchStrategy)
+        return createReferenceSearcher($package, dependency, this.referenceSearchStrategy)
     }
 }
 
+/** Wraps an existing physical or virtual filesystem. In preparation for supporting VS Code's virtual filesystem for github.dev. */
 export interface FileSystem {
     exists(path: string): Promise<boolean>
     join(...parts: string[]): string

### 2021-10-08 packages/core/src/index.ts

@@ -1,22 +1,18 @@
-import { Dependency, DependencySearchStrategy, DependencyUpdateOptions } from './dependencies'
-import { Dowdep, getCacheDirectory } from './dowdep'
-import { Package } from './packages'
-import { DeclarationLocation, FilePosition, FilePositionPrimitive, Location, Reference, ReferenceKind, ReferenceSearcher, ReferenceSearchStrategy } from './references'
-
-
 export {
-    Location,
-    DeclarationLocation,
     Dependency,
     DependencySearchStrategy,
-    DependencyUpdateOptions,
-    Dowdep,
+    DependencyUpdateOptions
+} from './dependencies'
+export { Dowdep } from './dowdep'
+export { Package } from './packages'
+export {
+    DeclarationLocation,
     FilePosition,
     FilePositionPrimitive,
-    getCacheDirectory,
-    Package,
+    Location,
     Reference,
+    ReferenceCollector,
     ReferenceKind,
     ReferenceSearcher,
     ReferenceSearchStrategy
-}
+} from './references'

### 2021-10-08 packages/core/src/packages.ts

@@ -3,10 +3,11 @@ import mapManyAsync from '@async-generators/map-many'
 
 import { Dowdep } from './dowdep'
 import { Dependency, DependencyUpdateCallback, DependencyUpdateOptions } from './dependencies'
-import { Reference } from '.'
+import { Reference } from './references'
 import mapUnorderedAsync from './utils/mapUnorderedAsync'
 
 
+/** A package whose downstream dependencies will be analyzed. */
 export class Package {
     constructor(
         public name: string,
@@ -25,6 +26,7 @@ export class Package {
         return this.dependencies.flatMap(depedendency => depedendency.references)
     }
 
+    /** Fetch and update dependencies for the package asynchronously. After every update step, `updateCallback` is invoked. */
     async updateDependencies(dowdep: Dowdep, options: Partial<DependencyUpdateOptions> = {}, updateCallback?: DependencyUpdateCallback) {
         const searchers = dowdep.createDependencySearchers(this)
 

### 2021-10-08 packages/core/src/references/base.ts

@@ -1,0 +1,184 @@
+import { strict as assert } from 'assert'
+import glob from 'glob-promise'
+
+import { Dependency } from '../dependencies'
+import { Package } from '../packages'
+import { OnlyData } from '../utils/OnlyData'
+
+
+/** The 2D position of a code snippet in an (extrinsic) file. */
+export class FilePosition {
+    constructor(init: OnlyData<FilePosition>) {
+        Object.assign(this, init)
+    }
+
+    row!: number
+    column?: number
+
+    /** Convert this instance into a primitive data type that is comparable and hashable by standard ES6 collections such as {@link Map} and {@link Set}. */
+    toPrimitive() {
+        return this.toString()
+    }
+
+    /** Convert this instance into a human-readable string. */
+    toString() {
+        return this.column ? `${this.row}:${this.column}` : `${this.row}`
+    }
+}
+
+export type FilePositionPrimitive = ReturnType<typeof FilePosition.prototype.toPrimitive>
+
+/** The address of a code snippet in a file. */
+export interface Location {
+    file: string
+    position: FilePosition,
+    memberPath?: string[] | null | undefined
+
+    toString(): string
+}
+
+/** The address of a code snippet for a reference with a definite member path. */
+export class ReferenceLocation implements Location {
+    constructor(init: OnlyData<ReferenceLocation>) {
+        Object.assign(this, init)
+    }
+
+    file!: string
+    position!: FilePosition
+    memberPath?: string[]
+
+    keyEquals(location: Location) {
+        return this.file === location.file
+        && this.position.toPrimitive() === location.position.toPrimitive()
+    }
+
+    toString() {
+        return `${this.file}:${this.position}`
+    }
+}
+
+type DeclarationPath = string[] | null | undefined
+
+/** The address of a code snippet for a declaration with a definite member path and member name. */
+export class DeclarationLocation implements Location {
+    constructor(init: OnlyData<DeclarationLocation>) {
+        Object.assign(this, init)
+    }
+
+    file!: string
+    position!: FilePosition
+    /**
+     * - `undefined`: is default import
+     * - `null`: imports root
+     */
+    memberPath!: DeclarationPath
+    memberName!: string
+
+    /**
+     * The ES6 syntax for a default import is:
+     *
+     *     import foo from 'bar'
+     */
+    isDefaultImport() {
+        return this.memberPath === undefined
+    }
+
+    /**
+     * The ES6 syntax for a namespace import is:
+     *
[…]

### 2021-10-08 packages/core/src/references/heuristic.ts

@@ -1,0 +1,279 @@
+import fs from 'fs'
+import { promises as fsPromises } from 'fs'
+import itAll from 'it-all'
+import LinesAndColumns from 'lines-and-columns'
+import _ from 'lodash'
+import type { Import, Options } from 'parse-imports'
+import path from 'path'
+import pkgDir from 'pkg-dir'
+
+import { DeclarationImport, FilePosition, ReferenceSearcher, Reference, ReferenceLocation } from './base'
+import rex from '../utils/rex'
+
+
+type ModuleBinding = {
+    moduleName: string
+    /**
+     * - `undefined`: is default import
+     * - `null`: imports root
+     */
+    memberName: string | null | undefined
+    alias: string
+    index: number
+}
+
+/** A reference searcher that performs simple string searches for the names of imported modules. Just a baseline. */
+export class HeuristicReferenceSearcher extends ReferenceSearcher {
+    static readonly maximumFileSize = 100_000  // 100 MB
+    protected commonJsPatterns!: readonly RegExp[]
+
+    async initialize() {
+        await super.initialize()
+        await this.initializeCommonJsPatterns()
+    }
+
+    private async initializeCommonJsPatterns() {
+        // Let's build a regex family!
+        // `foo = require('bar')`
+        // `foo = require('bar/baz')`
+        // See collectRequireBindings().
+
+        const identifierPattern = /[\p{L}\p{Nl}$_][\p{L}\p{Nl}$\p{Mn}\p{Mc}\p{Nd}\p{Pc}]*/u
+
+        /**
+         * Workaround for https://github.com/microsoft/TypeScript/issues/43329. // TODO: Check if this is a regression
+         *
+         * TypeScript will always try to replace dynamic imports with `requires` which doesn't work for importing ESM from CJS.
+         * We work around by "hiding" our dynamic import in a Function constructor (terrible...).
+         *
+         * In particular, we must not extract this call into a separate module.
+         * This would result in sporadic unresolved promises in the jest environment.
+         * See #65.
+         */
+        const dynamicImport = new Function('moduleName', 'return import(moduleName)')
+        const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
+
+        const requirePattern = rex`
+            (?<alias> ${identifierPattern} ) \s*
+            = \s*
+            require \s* \( \s*
+                (?<quote>['"])
+                (?<packageName> ${escapeRegexp(this.$package.name)} )
[…]

### 2021-10-08 packages/core/src/references/index.ts

@@ -1,0 +1,93 @@
+import { promises as fsPromises, Dirent } from 'fs'
+import { Dependency } from '../dependencies'
+import { Package } from '../packages'
+import path from 'path'
+
+import { ALL_REFERENCE_KINDS, Reference, ReferenceKind } from './base'
+import { HeuristicReferenceSearcher } from './heuristic'
+import { TypeReferenceSearcher } from './types'
+import fsExists from '../utils/fs.exists'
+
+export {
+    DeclarationLocation,
+    FilePosition,
+    FilePositionPrimitive,
+    Location,
+    Reference,
+    ReferenceKind,
+    ReferenceSearcher
+} from './base'
+
+
+const ALL_REFERENCE_SEARCH_STRATEGIES = [
+    'heuristic',
+    'types'
+] as const
+export type ReferenceSearchStrategy = (typeof ALL_REFERENCE_SEARCH_STRATEGIES)[number]
+
+function referenceSearcher(strategy: ReferenceSearchStrategy) {
+    switch (strategy) {
+        case 'heuristic':
+            return HeuristicReferenceSearcher
+        case 'types':
+            return TypeReferenceSearcher
+    }
+}
+
+export function createReferenceSearcher($package: Package, dependency: Dependency, strategy: ReferenceSearchStrategy) {
+    return new (referenceSearcher(strategy))($package, dependency)
+}
+
+/** Collects all packages from a `node_modules`-like folder structure and searches references in each package. */
+export class ReferenceCollector {
+    package: Package
+    rootDirectory: string
+    searchStrategy: ReferenceSearchStrategy
+
+    constructor($package: Package, rootDirectory: string, searchStrategy: ReferenceSearchStrategy) {
+        this.package = $package
+        this.rootDirectory = rootDirectory
+        this.searchStrategy = searchStrategy
+    }
+
+    async* searchReferences(limit?: number, includeKinds: readonly ReferenceKind[] | '*' = ['usage']): AsyncIterable<Reference> {
+        yield* this.basicSearchReferences(this.rootDirectory, limit, includeKinds == '*' ? ALL_REFERENCE_KINDS : includeKinds, 0)
+    }
+
+    protected async* basicSearchReferences(rootDirectory: string, limit: number | undefined, includeKinds: readonly ReferenceKind[] | '*', depth: number): AsyncIterable<Reference> {
+        if (!await fsExists(path.join(rootDirectory, 'package.json'))) {
+            // Search recursively
[…]

### 2021-10-08 packages/core/src/references/types.ts

@@ -1,0 +1,402 @@
+import { strict as assert } from 'assert'
+import { promises as fsPromises } from 'fs'
+import _ from 'lodash'
+import path from 'path'
+import pathIsInside from 'path-is-inside'
+import tryCatch from 'try-catch'
+import ts from 'typescript'
+
+import { DeclarationLocation, FilePosition, ReferenceSearcher, Reference, ReferenceKind, ReferenceLocation } from './base'
+
+
+/** A reference searcher that uses the TypeScript Compiler API to identify AST nodes that invoke a type from the target package. */
+export class TypeReferenceSearcher extends ReferenceSearcher {
+    protected typeChecker!: ts.TypeChecker
+    protected references!: Reference[]
+    protected dependencyDirectory!: string
+
+    /** In bytes (B). */
+    protected static maximumFileSize = 10_000_000
+
+    protected get packageDirectory() {
+        const directory = this.$package.directory
+        assert(directory, `No package directory was specified for package ${this.$package.name}`)
+        return directory
+    }
+
+    async* basicSearchReferences(rootDirectory: string) {
+        this.dependencyDirectory = rootDirectory
+        try {
+            const options = this.loadOptions()
+
+            const allFileNames = (
+                await this.findAllSourceFiles(this.dependencyDirectory)
+            ).map(file => path.join(this.dependencyDirectory, file))
+            if (!options.fileNames.length) {
+                if (!allFileNames.length) {
+                    console.warn("No files names passed or found, skipping repository", { dependencyName: this.dependency.name })
+                } else if (allFileNames.length > 1000) {
+                    console.warn("No files names passed and too many hypothetical source files, skipping repository", { dependencyName: this.dependency.name })
+                } else {
+                    console.warn("No file names passed, searching whole repository", { dependencyName: this.dependency.name })
+                    options.fileNames = allFileNames
+                }
+            }
+
+            const totalFileSize = _.sumBy(await Promise.all(options.fileNames.map(name => fsPromises.stat(name))), x => x.size)
+            if (totalFileSize > TypeReferenceSearcher.maximumFileSize) {
+                console.warn("Too large source files, skipping repository", { dependencyName: this.dependency.name })
+                return
+            }
+
+            const host = this.createCompilerHost(options.options)
+            const program = ts.createProgram(options.fileNames, options.options, host)
+            this.typeChecker = program.getTypeChecker()
+
[…]

### 2021-10-08 packages/core/src/utils/lodash-classify.ts

@@ -2,6 +2,8 @@ import _ from 'lodash'
 
 type Grouping<TItem> = { [key: string]: TItem[] }
 
+
+/** Classify the grouped input values into a map of buckets indicated by the values' keys and the passed function. See tests. */
 export function lodashClassify<TItem, TGrouping extends Grouping<TItem>, TClassKey>(
     input: TGrouping,
     fn: (item: TItem, key: string) => TClassKey
@@ -35,8 +37,7 @@ export function lodashClassify<TItem, TGrouping extends Grouping<TItem>, TClassK
 export function lodashClassifyNested<TItem extends object, TGrouping extends { [key: string]: TItem }, TClassKey>(
     input: TGrouping,
     fn: (key: string) => TClassKey
-    // eslint-disable-next-line @typescript-eslint/no-explicit-any
-): { [P in keyof TGrouping]: Map<TClassKey, { [P in keyof TGrouping[keyof TGrouping]]: _.Dictionary<any> }> } {
+): { [P in keyof TGrouping]: Map<TClassKey, { [P in keyof TGrouping[keyof TGrouping]]: _.Dictionary<unknown> }> } {
     return _.mapValues(
         input,
         item => new Map(Array.from(

### 2021-10-08 packages/core/test/npm-dependencies.test.ts

@@ -7,13 +7,12 @@ import { promisify } from 'util'
 import { Package } from '../src'
 import { NpmDependency } from '../src/dependencies/npm'
 
-import { Dowdep, getCacheDirectory } from '../src'
+import { Dowdep } from '../src'
 
 const readPackageJson = <(file: string) => Promise<PackageJson>><unknown>  // BUG in type definitions: https://github.com/DefinitelyTyped/DefinitelyTyped/issues/33340
     promisify(readPackageJsonCallback)
 
 
-// TODO: Extract all fixtures into separate files?
 describe('updateDependencies', () => {
     it.each`
         packageName     | limit  | downloadGitHubData  | timeoutSecs  | nonGitHubThreshold
@@ -75,7 +74,7 @@ describe('updateSource', () => {
         dep.tarballUrl = tarballUrl
 
         const dowdep = new Dowdep({
-            sourceCacheDirectory: getCacheDirectory()
+            sourceCacheDirectory: process.env.NPM_CACHE || 'cache'
         })
         await dep.updateSource(dowdep)
 

### 2021-10-08 packages/core/test/references.test.ts

@@ -1,9 +1,9 @@
-import asyncIteratorToArray from 'it-all'
+import itAll from 'it-all'
 import _ from 'lodash'
 import { jsonc as json } from 'jsonc'
 
 import { Package } from '../src/packages'
-import { ReferenceSearcher, ReferenceKind } from '../src/references'
+import { ReferenceCollector, ReferenceKind, ReferenceSearchStrategy } from '../src/references'
 import ifCurtailed from '../src/utils/if-curtailed'
 import { lodashClassifyNested } from '../src/utils/lodash-classify'
 import { getSourceDirectory } from './_utils/sourceDirectory'
@@ -32,19 +32,19 @@ const expectedTypeReferences = <References>json.readSync(`${SOURCE_DIRECTORY}/ex
 describe('ReferenceSearcher', () => {
     it.each(_.flatMap(
         Object.entries({'heuristic': expectedHeuristicReferences, 'types': expectedTypeReferences}),
-        ([packageReferenceSearcher, allExpectedReferences]) => _.map(
+        ([strategy, allExpectedReferences]) => _.map(
             Object.entries(allExpectedReferences),
-            ([packageName, expectedReferences]) => ({ packageReferenceSearcher, packageName, expectedReferences }))
+            ([packageName, expectedReferences]) => ({ strategy: <ReferenceSearchStrategy>strategy, packageName, expectedReferences }))
     ))("should find relevant references for %s", async (
-        { packageReferenceSearcher, packageName, expectedReferences }) => {
+        { strategy, packageName, expectedReferences }) => {
         const $package = new Package(
             packageName,
             `${SOURCE_DIRECTORY}/examples/packages/${packageName}`
         )
-        const searcher = new ReferenceSearcher($package, `${SOURCE_DIRECTORY}/examples/dependents`, packageReferenceSearcher)
-        const references = await asyncIteratorToArray(searcher.searchReferences(undefined, '*'))
+        const collector = new ReferenceCollector($package, `${SOURCE_DIRECTORY}/examples/dependents`, strategy)
+        const references = await itAll(collector.searchReferences(undefined, '*'))
 
-        /** Since null and undefined are invalid keys in JS objects, we stringify them for compatibility with lodash. See Reference.memberName. */
+        /** Since null and undefined are invalid keys in JS objects, we stringify them for compatibility with lodash dictionaries. See Reference.memberName. */
         function stringify(key: string | null | undefined) {
             if (key === undefined) return '<undefined>'
[…]

### 2021-10-08 packages/example-js/index.js

@@ -2,11 +2,10 @@
 
 const dowdep = require('dowdep')
 
-const cacheDirectory = dowdep.getCacheDirectory()
 const $package = new dowdep.Package(
     'name',
     '/path/to/directory'
 )
-console.log(cacheDirectory)
 console.log($package)
+console.log(new dowdep.Dowdep().createDependencySearchers($package))
 console.log(dowdep.ReferenceSearcher)

### 2021-10-08 packages/example-ts/index.ts

@@ -1,12 +1,11 @@
 #!/usr/bin/env -S npx ts-node
 
-import { getCacheDirectory, Package, ReferenceSearcher } from 'dowdep'
+import { Dowdep, Package, ReferenceSearcher } from 'dowdep'
 
-const cacheDirectory = getCacheDirectory()
 const $package = new Package(
     'name',
     '/path/to/directory'
 )
-console.log(cacheDirectory)
 console.log($package)
+console.log(new Dowdep().createDependencySearchers($package))
 console.log(ReferenceSearcher)

### 2021-10-08 packages/core/src/utils/lodash-classify.ts
Fix type error

@@ -37,7 +37,7 @@ export function lodashClassify<TItem, TGrouping extends Grouping<TItem>, TClassK
 export function lodashClassifyNested<TItem extends object, TGrouping extends { [key: string]: TItem }, TClassKey>(
     input: TGrouping,
     fn: (key: string) => TClassKey
-): { [P in keyof TGrouping]: Map<TClassKey, { [P in keyof TGrouping[keyof TGrouping]]: _.Dictionary<unknown> }> } {
+) {
     return _.mapValues(
         input,
         item => new Map(Array.from(

### 2021-10-11 docs/paper/sections/3_approach/usage_mining/patterns/JsxOpeningElement.tex
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting
Improve black/white accessibility of figure 2

--- 2021-09-29 docs/paper/sections/5_usage_mining/patterns/JsxOpeningElement.tex
@@
 \begin{tikzpicture}
-	\node [red] {JsxOpeningExpression}
-		child [gray] {node [gray] {tagName}}
-		child [gray] {node [gray, yshift = -0.5cm] {typeArguments}}
-		child [gray] {node [gray] {attributes}};
+	\node [accent1] {\textbf{JsxOpeningExpression}}
+		child [lowlight] {node [lowlight] {tagName}}
+		child [lowlight] {node [lowlight, yshift = -0.5cm] {typeArguments}}
+		child [lowlight] {node [lowlight] {attributes}};
 \end{tikzpicture}
@@
 	Node pattern for a JSX opening element (as supported in React\footnote{\url{https://reactjs.org/docs/introducing-jsx.html}} or TypeScript\footnote{\url{https://www.typescriptlang.org/docs/handbook/jsx.html}}), such as in:
-	\code{\lowlight{elem = }\uline{<Button \lowlight{color}="\lowlight{blue}"> \lowlight{Google</Button>}}\lowlight{;}}
+	\code*{\textlowlight{elem = }\uline{<\texthighlight{Button} \textlowlight{color}="\textlowlight{blue}"> \textlowlight{Submit</Button>}}\textlowlight{;}}
 }

### 2021-10-11 docs/paper/sections/6_conclusion.tex
Fix consecutive footnotes manually

@@
 For better performance, usage samples could be cached, and finer-grained UI updates could be implemented.
-Last but not least, we want to improve the integration of the extension by adding support for browser environments such as github.dev\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}} and by connecting it to the GitHub Remote Repositories extension\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}}.
+Last but not least, we want to improve the integration of the extension by adding support for browser environments such as github.dev\footnote{\url{https://code.visualstudio.com/api/extension-guides/web-extensions}}\footnoteseparator\footnote{\url{https://docs.github.com/en/codespaces/the-githubdev-web-based-editor}} and by connecting it to the GitHub Remote Repositories extension\footnote{\url{https://marketplace.visualstudio.com/items?itemName=GitHub.remotehub}}.
 

### 2021-10-11 docs/paper/sections/3_approach.tex
Improve black/white accessibility of figure 2
Minor rephrasings and fixed throughall the paper

@@
 	\begin{minipage}{\linewidth}
-		\newcommand\textlowlight[1]{\textcolor{gray}{#1}}
-		\newcommand\texthighlight[1]{\textcolor{accent1}{#1}}
+		\colorlet{lowlight}{black!40}
+		\newcommand\textlowlight[1]{\textcolor{lowlight}{#1}}
+		\newcommand\texthighlight[1]{\textbf{\textcolor{accent1}{#1}}}
 		\begin{center}
@@
 
-To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate abstract syntax forest (ASF, i.e., a set of ASTs).
+To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate \emph{abstract syntax forest}F (ASF, i.e., a set of ASTs).
 
@@
 For instance, after this step, every variable node will contain a link to the assignment node of this variable, and every function call expression will contain a link to the definition of this function.
-The operating principle of this type analysis depends on the kind of programming language; i.e., in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
+The operating principle of this type analysis depends on the kind of programming language; that is, in statically typed languages, type symbols can usually be retrieved from the declaration of an identifier, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
 

### 2021-10-11 docs/paper/sections/4_implementation.tex
Minor rephrasings and fixed throughall the paper

@@
 The de facto standard package repository for node.js is npm.
-To fetch downstream dependency packages from the npm registry, we use the npm package \code{npm-dependants}\footnote{All packages can be retrieved from \url{npmjs.com}} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
+To fetch downstream dependency packages from the npm registry, we use the npm package \code{npm-dependants}\footnote{All packages can be retrieved from \url{npmjs.com}.} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
 To keep the footprint of our implementation small, we only scrape a part of the dependents list.
@@
 
-For the second approach based on a code search engine, we have identified Sourcegraph\footnote{\url{https://sourcegraph.com/}} as a promising platform.
-npm packages specify their dependencies in a package.json metadata file (see \cref{sec:implementation/package.json}).
+For the second method based on a code search engine, we have identified Sourcegraph\footnote{\url{https://sourcegraph.com/}} as a promising platform.
+npm packages specify their dependencies in a \code{package.json} metadata file (see \cref{sec:implementation/package.json}).
 To find all packages depending on a certain package, we can search all available \code{package.json} files for a reference to this package identifier.
@@
 To do so, we extend the \code{paths} parameter from the default compiler options\footnote{\url{https://www.typescriptlang.org/tsconfig\#paths}} and insert a new entry that remaps accesses to the target package name to the separate source code directory of the target package.
+
+\subsection{Presentation of Results}
+\label{sec:implementation/presentation}
+
+After all references have been collected, a proper user interface (UI) is still required to provide users easy access to these data that fulfills the requirements mentioned above.
+To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to the \emph{Visual Studio Code} IDE\footnote{\url{https://code.visualstudio.com/}}.
+VS Code is one of the most popular IDEs that support JavaScript, and the one with the highest annual growth.\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
+It also provides a comprehensive set of APIs for extension developers.
+To support other researchers in reusing our solution, we also provide a CLI.
+
+To support developers in answering the questions raised in \cref{sec:approach}, we have designed three key views (see \cref{fig:implementation/presentation/screenshots}):
+
+\begin{enumerate}[label=(\roman*)]
+	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
+	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
+	\item The \emph{CodeLens integration} provides quick access to a slice usage samples and is attached to the definition of each package member in the source code editor.
+\end{enumerate}
 
@@
 
-\subsection{Presentation of Results}
-\label{sec:implementation/presentation}
-
-After all references have been collected, a proper UI is still required to provide users easy access to these data that fulfills the requirements mentioned above.
-To satisfy \cref{req2} and make our tool available in the usual working environment of users, we implement it as an extension to the \emph{Visual Studio Code} IDE\footnote{\url{https://code.visualstudio.com/}}.
-VS Code is one of the most popular IDEs that support JavaScript, and the one with the highest annual growth.\footnote{Top IDE Index by Pierre Carbonnelle (2021): \url{https://pypl.github.io/IDE.html}}
-It also provides a comprehensive set of APIs for extension developers.
-To support other researchers in reusing our solution, we also provide a CLI.
-
-To support developers in answering the questions raised in \cref{sec:approach}, we have designed three key views for our extension (see \cref{fig:implementation/presentation/screenshots}):
-
-\begin{enumerate}[label=(\roman*)]
-	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all their references to the target package.
-	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
-	\item The \emph{CodeLens integration} provides quick access to a slice usage samples and is attached to the definition of each package member in the source code editor.
-\end{enumerate}
-
-Both references and members are organized in a tree view reflecting the hierarchical structure of the original software repository.
+Both references and members are organized each in a tree view that reflects the hierarchical structure of the original software repository.
 In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an ``I'm feeling lucky'' button for every view that redirects the user to a random dependency or reference, resp., to gain a faster, unbiased impression of usage samples.
 
-We implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the \emph{Tree View API} and the \emph{CodeLens API}.
-One challenge has been to deliver fast results and not to block the user interface because even in spite of the lightweight mining approaches we chose to satisfy \cref{req1} above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation}).
+To implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the \emph{Tree View API} and the \emph{CodeLens API}.
+One challenge has been to deliver fast results and not to block the user interface because even in spite of the lightweight mining methods we chose to satisfy \cref{req1} from above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation}).
 To overcome this issue, we use pagination wherever possible and apply the observer pattern to push incremental UI updates.
-As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our object model by using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting inside the data collection process.
+As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our object model by using the JavaScript concepts asynchronous functions, \code{AsyncIterator}s, and \code{Promise.all} to avoid busy waiting during the data collection process.

### 2021-10-11 docs/paper/sections/5_evaluation.tex
Minor rephrasings and fixed throughall the paper

@@
 \begin{enumerate}[label=RQ\arabic*]
-	\item \label[requirement]{resqu1} What is the quality and quantity of the proposed approaches for dependency collection?
-	\item \label[requirement]{resqu2} What is the quality and quantity of the proposed approach for mining usage samples?
+	\item \label[requirement]{resqu1} What is the quality and quantity of the proposed methods for dependency collection?
+	\item \label[requirement]{resqu2} What is the quality and quantity of the proposed method for mining usage samples?
 	\item \label[requirement]{resqu3} How well is the proposed tool applicable?
@@
 
-To assess the quality of dependency collection, we analyze it with respect to extent, precision, recall, and performance.
-\Cref{tab:evaluation/resqu1/quantities} shows the number of dependencies that we collected to build an experimental dataset from each data source following the proposed approaches for a set of arbitrarily selected npm packages.
+To assess the quality and quantity of dependency collection, we analyze it with respect to extent, precision, recall, and performance.
+\Cref{tab:evaluation/resqu1/quantities} shows the number of dependencies that we collected to build an experimental dataset from each data source following the proposed methods for a set of arbitrarily selected npm packages.
 For each package, we have annotated a subset of the collected dependencies (max. 20 dependencies per package) to identify and classify false positive hits.
@@
 \begin{table}
-	\caption{Quantity and false-positive rates (FPR) of downstream dependencies found by both approaches for selected packages.}
+	\caption{Quantity and false-positive rates (FPR) of downstream dependencies found by both methods for selected packages.}
 	\label{tab:evaluation/resqu1/quantities}
@@
 
-Regarding the total number of dependencies collected by each approach, no clear trend in favor of any approach can be ascertained for small or medium packages (having less than \num{10,000} stars on GitHub).
+Regarding the total number of dependencies collected by each method, no clear trend in favor of any method can be ascertained for small or medium packages (having less than \num{10,000} stars on GitHub).
 For larger packages (having at least \num{10,000} stars), however, the number of dependencies collected from the npm registry stagnates near to 400 hits; beyond this limit, the npm registry will return internal server errors only.
@@
 
-As the disjunct proportion of results from both approaches is very small (on average about \SI{6}{\percent}), we consider a combination of both data sources useful for maximizing the extent and diversity of the gained dataset.
+As the disjunct proportion of results from both methods is very small (on average about \SI{6}{\percent}), we consider a combination of both data sources useful for maximizing the extent and diversity of the gained dataset.
 
@@
 In some situations, this may happen if the package is a plugin for another package or if it is invoked as a CLI from a build script, but in the majority of repositories, developers trivially appear to have specified the upstream dependency by accident (e.g., while copying a \code{package.json} file over from another package), or to have forgotten to remove the upstream dependency after switching away from using the package.
-Rarer causes include repositories that only add type definitions for TypeScript to a package but do not actually import it, as well as, especially for repositories found on Sourcegraph, other packages required by a repository declaring a peer dependency on the target package which needs to be fulfilled by the depending repository.
+Rarer causes include repositories that only add type definitions for TypeScript to a package but do not actually import it, as well as, especially for repositories found on Sourcegraph, other packages required by a repository that declares a peer dependency on the target package which needs to be fulfilled by the depending repository.
 
@@
 Besides the precision of collected dependencies, their recall is also of interest.
-As the dependencies are collected from two giant datasets in excerpts only, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
-Nevertheless, there are some causes that will prevent a dependency from being found by our approaches:
+As the dependencies are collected in excerpts from two very large datasets, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
+Nevertheless, there are some causes that will prevent a dependency from being found by our methods:
 
 \begin{itemize}
-	\item Packages without a proper dependency manifest cannot be detected by our approaches which are based on exactly these metadata.
+	\item Packages without a proper dependency manifest cannot be detected by our methods which are based on exactly these metadata.
 	\item On npm, only published packages will be found, creating a bias towards generic and professional software.
@@
 		As we only fetch the first dependencies from both data sources, this is a likely source of further biases.
-		These could be fought by always fetching all dependencies, but this would drastically reduce the overall performance.
+		These biases could be fought by always fetching all dependencies, but this would drastically reduce the overall performance.
 \end{itemize}
@@
 
-To assess the quality of usage mining, we examine the precision, recall, and performance of this processing step.
+To assess the quality and quantity of usage mining, we examine the precision, recall, and performance of this processing step.
 Due to the complexity of a detailed annotation process, we only consider the existence of found usage samples on the dependency level.
-The absolute quantity of found usage samples varies largely for different packages and dependencies based on the semantic extent of the package and the coupling between package and dependency.
+The absolute quantity of found usage samples largely varies for different packages and dependencies based on the semantic extent of the package and the coupling between package and dependency.
 
@@
 
-Under laboratory conditions, false-positive usage samples cannot be emitted by our approach if we assume the correctness of the TypeScript compiler.
-There are only two exceptions to this invariant:
+Under laboratory conditions, false-positive usage samples cannot be emitted by our method if we assume the correctness of the TypeScript compiler.
+There are only two theoretical exceptions to this invariant:
 \begin{enumerate*}[label=(\roman*)]
@@
 
-To evaluate the recall of our approach, we have refined the experimental dataset collected in \cref{sec:evaluation/resqu1} and removed all false-positive dependencies.
-Within this cleansed dataset, the overall rate of dependencies for that our approach is unable to find at least one usage sample accounts for \SI{47.9}{\percent}.
-As a cause for these false negatives, we have identified a number of systematic causes:
+To evaluate the recall of our method, we have refined the experimental dataset collected in \cref{sec:evaluation/resqu1} and removed all false-positive dependencies.
+Within this cleansed dataset, the overall rate of dependencies for that our method is unable to find at least one usage sample accounts for \SI{47.9}{\percent}.
+To explain these false negatives, we have identified a number of systematic causes:
 
@@
 	\item In general, the static type analyzer of TypeScript has its limitations.
-		For instance, the type analysis will have a limited recall for certain control flow patterns or metaprogramming constructs such as meta-circular evaluation using the the \code{eval()} function or dynamic function binding using \code{Function.bind()} etc.
+		For instance, the type analysis will have a limited recall for certain control flow patterns or metaprogramming constructs such as meta-circular evaluation using the \code{eval()} function, dynamic function binding using \code{Function.bind()}, etc.
 \end{itemize}
@@
 If they are intending to analyze the usage of a member with an unambiguous name, they can perform an expeditious string search.
-This is possible using Sourcegraph if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
+This is possible using Sourcegraph or another search engine if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
 If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
@@
 Also, the dependency artifacts have no strong relationship to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
-The code annotations are disaplyed close to the original source code with a small spatial distance.
+The code annotations are displayed close to the original source code with a small spatial distance.
 

### 2021-10-11 docs/paper/sections/6_conclusion.tex
Minor rephrasings and fixed throughall the paper

@@
 Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent, and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
-However, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
+Nevertheless, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
 Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our approach for mining usage samples as well as the efficacy of our tool.
@@
 In a wider perspective, we envision many other purposes for analyzing the collected downstream dependency data.
-By deriving usage patterns from the samples using an approach such \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
+By deriving usage patterns from the samples using an approach such as \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
 The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
-There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package, LCOM), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.
+There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package as per LCOM \citep{chidamber1994metrics}), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.
 
-By replacing the static usage analysis with a dynamic approach, the detect usage samples could be enriched with valuable runtime data describing involved parameters, the fine-grained code coverage of package members, or the invocation context of members.
+By replacing the static usage analysis with a dynamic approach, the detected usage samples could be enriched with valuable runtime data describing involved parameters, the fine-grained code coverage of package members, or the invocation context of members.
+
 Returning to the abstract problem that we have formulated in the introduction -- how can we improve developer knowledge about their packages' usage?

### 2021-10-11 packages/vscode-extension/src/dependencies.ts
Document & clean-up VSCE

@@ -86,6 +86,7 @@ class DependenciesDependencyItem extends DependencyItem<
     }
 }
 
+/** A composite item for a file path inside a {@link Dependency}. */
 class DependencyFileNodeItem extends ReferenceFileNodeItem<
     DependencyFileNodeItem,
     DependencyMemberNodeItem,
@@ -135,6 +136,7 @@ class DependencyFileNodeItem extends ReferenceFileNodeItem<
     }
 }
 
+/** A composite item for a member path inside a source file of a {@link Dependency}. */
 class DependencyMemberNodeItem extends LabeledHierarchyNodeItem<
     Reference,
     DependencyMemberNodeItem,

### 2021-10-11 packages/vscode-extension/src/extension.ts

@@ -33,6 +33,7 @@ export function deactivate() {
     extension.release()
 }
 
+/** The god class of the extension that connects to a {@link Dowdep} instance. */
 export class Extension {
     packages: Package[] = []
     protected dowdep: Dowdep
@@ -151,20 +152,20 @@ export class Extension {
         return
     }
 
+    /** Refresh the list of packages. */
     async refreshPackages() {
         this.packages = await this.getPackages()
         if (!this.packages.length) {
             await vscode.window.showWarningMessage("No packages were found in this workspace.")
             // TODO: Only show warning if no error was shown earlier during getPackages()
-            // TODO: Do we need to await this?
         }
         await this.notifyModelObservers()
     }
 
+    /** Refresh the list of dependencies for all packages. */
     async refreshAllDependencies() {
         if (!this.packages.length) {
             await vscode.window.showWarningMessage("No packages were found in this workspace.")
-            // TODO: Do we need to await this?
         }
 
         await this.doCancellable(async () => {
@@ -200,6 +201,7 @@ export class Extension {
         })
     }
 
+    /** Refresh the list of usage samples for all dependencies. */
     async refreshAllReferences() {
         const allDependencies = this.packages
             .flatMap($package => $package.dependencies)
@@ -231,6 +233,7 @@ export class Extension {
         })
     }
 
+    /** Refresh the list of dependencies for all packages and the list of usage samples for each dependency. */
     async refreshAllDependenciesAndReferences() {
         // TODO: Deduplicate
         if (!this.packages.length) {
@@ -388,6 +391,7 @@ export class Extension {
         })
     }
 
+    /** Run the passed function, and return immediately if an {@link vscode.CancellationError} is raised. */
     private doCancellable<TIn extends unknown[], TOut>(fun: (...args: TIn) => TOut, ...args: TIn) {
         try {
             return fun(...args)
@@ -400,6 +404,7 @@ export class Extension {
         }
     }
 
+    /** Run the passed function and catch any errors that are signaled and report them to the user. */
     private catchErrors<TIn extends unknown[], TOut>(fun: (...args: TIn) => Promise<TOut>) {
         return async (...args: TIn) => {
             try {
@@ -411,11 +416,13 @@ export class Extension {
         }
     }
 
+    /** The model has changed. Inform all observers that they need to update their views. */
     private async notifyModelObservers() {
         await Promise.all(this.modelObservers.map(
             observer => observer.modelChanged()))
     }
 
[…]

### 2021-10-11 packages/vscode-extension/src/references.ts

@@ -91,6 +91,7 @@ class ReferencesPackageItem extends PackageItem<
     }
 }
 
+/** A composite item for a file path inside a {@link Package}. */
 class PackageFileNodeItem extends ReferenceFileNodeItem<
     PackageFileNodeItem,
     PackageMemberNodeItem,
@@ -148,6 +149,7 @@ class PackageFileNodeItem extends ReferenceFileNodeItem<
     }
 }
 
+/** A composite item for a member path inside a {@link Package} file. */
 class PackageMemberNodeItem extends HierarchyNodeItem<
     string | Dependency,
     Reference,

### 2021-10-11 packages/vscode-extension/src/utils/node/iterUtils.ts

@@ -1,3 +1,7 @@
+/** Iteration utilities for {@link IterableIterator}s. */
+// eslint-disable-next-line @typescript-eslint/no-extra-semi
+;
+
 export function first<T>(iterator: IterableIterator<T>) {
     const first = iterator.next()
     if (first.done) {

### 2021-10-11 packages/vscode-extension/src/utils/vscode/hierarchy.ts

@@ -7,6 +7,7 @@ import * as mapUtils from '../node/mapUtils'
 import { Synchronizer } from './synchronizer'
 
 
+/** A specialization of {@link vscode.HierarchyDataProvider} that delegates control of the tree structure to a {@link HierarchyItem}. */
 export abstract class HierarchyDataProvider<
     TRootItem extends RefreshableHierarchyItem
 > implements vscode.TreeDataProvider<HierarchyItem> {
@@ -73,6 +74,7 @@ export abstract class HierarchyDataProvider<
     }
 }
 
+/** A specialization {@link vscode.TreeItem} that implements the composite pattern. */
 export abstract class HierarchyItem extends vscode.TreeItem {
     constructor(collapsibleState?: vscode.TreeItemCollapsibleState) {
         super("", collapsibleState)
@@ -96,6 +98,7 @@ export abstract class RefreshableHierarchyItem extends HierarchyItem {
     abstract refresh(): void
 }
 
+/** A {@link RefreshableHierarchyItem} that caches and encapsulates child management and provides an abstract protocol for adding new items. */
 export abstract class SynchronizableHierarchyItem<
     TKey,
     TItem extends RefreshableHierarchyItem
@@ -139,6 +142,8 @@ export type HierarchyNodeItemOptions = {
     showCountInDescription: boolean
 }
 
+/** A {@link RefreshableHierarchyItem} that arranges a composite structure automatically into hierarchical items by paths.
+*/
 export abstract class HierarchyNodeItem<
     TPathSegment,
     TLeafKey,
@@ -161,6 +166,7 @@ export abstract class HierarchyNodeItem<
     public allLeafs: readonly TLeafKey[] = []
     /** If set, will be used to sort all complex item keys. */
     protected pathSegmentSorters?: ReadonlyArray<_.Many<_.ListIteratee<TPathSegment>>>
+    /** If set, will be used to sort all leaf keys. */
     protected leafSorters?: ReadonlyArray<_.Many<_.ListIteratee<TLeafKey>>>
     private complexBuckets: Map<TPathSegment, TLeafKey[]>
     protected showCountInDescription = false

### 2021-10-11 packages/vscode-extension/src/utils/vscode/markdown.ts

@@ -1,8 +1,22 @@
-import assert from 'assert'
+import { strict as assert } from 'assert'
 import { MarkdownString } from 'vscode'
 
 
-export default function (templates: TemplateStringsArray, ...args: (string | MarkdownString | {toString(): string})[]) {
+/**
+ * A template literal function that compiles a {@link MarkdownString}.
+ *
+ * Arguments can be string-like objects (that will be escaped) or further {@link MarkdownString}s.
+ *
+ * @example ```
+ * md`Dear ${this.user}, here is some additional markdown: ${md`${2}nd nested template string`}`
+ * ```
+ */
+export default function (
+    templates: TemplateStringsArray,
+    ...args: (string | MarkdownString | {
+        toString(): string
+    })[]
+) {
     assert(templates.raw.length === args.length + 1)
 
     const raws = [...templates.raw]

### 2021-10-11 packages/vscode-extension/src/utils/vscode/synchronizer.ts

@@ -1,6 +1,14 @@
 import * as vscode from 'vscode'
 
 
+/**
+ * Synchronizes updates provided by a model with the view processing the updates.
+ *
+ * This helper class can be used to ensure that updates appear in the UI even before the model is busy again.
+ * This is far away from an ideal solution: Every intermediate UI update will slow down the model, and if the UI should reject an event for whatever reason, the model would halt forever.
+ * However, the only viable alternatives considered are timeouts (even slower) and web workers that enable true multiprocessing but have a larger implementational and computational overhead.
+ * Based on empirical experience, this is deemed an acceptable solution for now.
+ */
 export class Synchronizer {
     constructor(
         public enablementCheck: () => boolean
@@ -12,6 +20,7 @@ export class Synchronizer {
     private lastUpdate: number | undefined
     private pendingResolvers: (() => void)[] = []
 
+    /** Wrap a function for getting model data with this synchronizer. Whenever the wrapped function is called, signalize that all pending UI updates have been processed. */
     spy<TIn extends unknown[], TOut>($function: (...args: TIn) => TOut) {
         return (...args: TIn) => {
             this.wasUpdated()
@@ -19,6 +28,7 @@ export class Synchronizer {
         }
     }
 
+    /** Asynchronously wait until all pending UI updates have been processed. */
     fire<T>(eventEmitter: vscode.EventEmitter<T | void>) {
         const promise = this.shouldUpdate() ? this.promise() : undefined
         eventEmitter.fire()
@@ -40,9 +50,7 @@ export class Synchronizer {
     }
 
     protected shouldUpdate() {
-        const should = !this.lastUpdate || this.now() - this.lastUpdate > this.updateInterval
-        console.log(should)
-        return should
+        return !this.lastUpdate || this.now() - this.lastUpdate > this.updateInterval
     }
 
     protected promise() {

### 2021-10-11 packages/vscode-extension/src/views.ts

@@ -19,6 +19,11 @@ export class HierarchyProvider<TRootItem extends RefreshableHierarchyItem> exten
     }
 }
 
+/**
+ * A pseudo-item that represents the root of a tree view of package items.
+ *
+ * This item is never displayed inside a tree view but only used to control child items.
+ */
 export abstract class PackagesItem<TPackageItem extends RefreshableHierarchyItem> extends SynchronizableHierarchyItem<Package, TPackageItem> {
     constructor(
         protected extension: Extension
@@ -31,6 +36,7 @@ export abstract class PackagesItem<TPackageItem extends RefreshableHierarchyItem
     }
 }
 
+/** An item for a {@link Package}. */
 export abstract class PackageItem<TItem extends RefreshableHierarchyItem> extends SynchronizableHierarchyItem<Dependency, TItem> {
     constructor(
         public $package: Package
@@ -56,6 +62,7 @@ export abstract class PackageItem<TItem extends RefreshableHierarchyItem> extend
     }
 }
 
+/** A composite item for a {@link Dependency}. */
 export abstract class DependencyItem<
     TDependencyItem extends DependencyItem<TDependencyItem, TReferenceItem>,
     TReferenceItem extends RefreshableHierarchyItem
@@ -145,6 +152,7 @@ export abstract class DependencyItem<
     }
 }
 
+/** A composite item for a file-system object, i.e., a file or a folder. */
 export abstract class ReferenceFileNodeItem<
     TFileNodeItem extends ReferenceFileNodeItem<TFileNodeItem, TMemberNodeItem, TLeafItem>,
     TMemberNodeItem extends RefreshableHierarchyItem & {
@@ -222,6 +230,7 @@ export abstract class ReferenceFileNodeItem<
     }
 }
 
+/** A leaf item for a {@link Reference}. */
 export class ReferenceItem extends RefreshableHierarchyItem {
     constructor(
         protected reference: Reference

### 2021-10-11 packages/core/src/utils/mapUnorderedAsync.ts
Please linter

@@ -53,7 +53,7 @@ export default function mapUnorderedAsync<TIn, TOut>(iterable: AsyncIterable<TIn
                     }
                     await semaphore
                     semaphore = new Promise<void>((res, rej) => [resolve, reject] = [res, rej])
-                    return this.next()
+                    return await this.next()
                 }
             }
         }

### 2021-10-11 packages/vscode-extension/src/extension.ts

@@ -44,7 +44,7 @@ export class Extension {
     protected referencesProvider: ReferencesProvider
     protected codeLensProvider: DeclarationCodeLensProvider
 
-    private dependencyLimitIncrement: number = 0
+    private dependencyLimitIncrement = 0
     private get modelObservers() {
         return [
             this.dependenciesProvider,
@@ -348,7 +348,7 @@ export class Extension {
             label: string,
             url: string
         }
-        if (urls.size == 1) {
+        if (urls.size === 1) {
             const url = iterUtils.first(urls.entries())
             target = {
                 label: url[0],
@@ -467,7 +467,7 @@ export class Extension {
 
     protected async getDependencies(dependency?: DependencyLike): Promise<readonly Dependency[]> {
         if (!dependency) {
-            return this.getDependencies(await this.getPackages())
+            return await this.getDependencies(await this.getPackages())
         }
 
         if (_.isArrayLike(dependency)) {

### 2021-10-11 packages/vscode-extension/src/utils/vscode/hierarchy.ts

@@ -130,7 +130,7 @@ export abstract class RefreshableHierarchyItem extends HierarchyItem {
         this.parent?.leavesChanged()
     }
 
-    private serializeContext(context: object) {
+    private serializeContext(context: Record<string, unknown>) {
         return Object.entries(context).map(
             ([key, value]) => `${key}:${value}`
         ).join(' ')

### 2021-10-11 packages/vscode-extension/src/views.ts

@@ -20,7 +20,7 @@ export class HierarchyProvider<TRootItem extends RefreshableHierarchyItem> exten
         registerCallback('dowdep.dowdepDependencies.openDependencyExternally', (item: DependencyItem<any, any>) => item.openExternally())
         registerCallback('dowdep.dowdepReferences.openReference', (item: ReferenceItem) => item.open())
     }
-    
+
     protected static async openRandomReference(root: HierarchyItem) {
         const item = _.sample([...root.findAllLeafs(<(item: HierarchyItem) => item is ReferenceItem>(_item => _item instanceof ReferenceItem))])
         return await item?.open()

### 2021-10-11 packages/vscode-extension/src/extension.ts
openDependencyExternally: Don't add generic icons to URLs; escape URLs properly

@@ -8,9 +8,10 @@ import vscode from 'vscode'
 import { DeclarationCodeLensProvider } from './codeLens'
 import { DependenciesProvider } from './dependencies'
 import { ReferencesProvider } from './references'
+import { HierarchyProvider } from './views'
 import isDefined from './utils/node/isDefined'
 import * as iterUtils from './utils/node/iterUtils'
-import { HierarchyProvider } from './views'
+import { escapeMarkdown } from './utils/vscode/markdown'
 
 
 let extension: Extension
@@ -358,8 +359,8 @@ export class Extension {
             const choice = await vscode.window.showQuickPick(
                 _.map([...urls.entries()], ([label, url]) => ({
                     target: { label, url },
-                    label: `$(globe) ${label}`,
-                    description: url
+                    label: escapeMarkdown(label),
+                    description: escapeMarkdown(url)
                 })),
                 {
                     title: "Choose platform"

### 2021-10-11 packages/vscode-extension/src/views.ts

@@ -7,7 +7,7 @@ import * as vscode from 'vscode'
 import { Extension } from './extension'
 import { HierarchyDataProvider, HierarchyItem, HierarchyNodeItem, LabeledHierarchyNodeItem, RefreshableHierarchyItem, SynchronizableHierarchyItem } from './utils/vscode/hierarchy'
 import * as iterUtils from './utils/node/iterUtils'
-import md from './utils/vscode/markdown'
+import { md } from './utils/vscode/markdown'
 import isDefined from './utils/node/isDefined'
 
 

### 2021-10-11 packages/cli/src/DowdepCommand.ts
Enhance documentation

@@ -3,7 +3,10 @@ import { Command } from '@oclif/command'
 
 import { Dependency, DependencyUpdateOptions, Dowdep, Package } from 'dowdep'
 
+
+/** Abstract base class for all dowdep commands. */
 export default abstract class DowdepCommand extends Command {
+    /** Update dependencies for the given package name with the specified options. Once a found dependency fulfills the specified readiness predicate, stream it via the returned async iterator. */
     async *updateDependencies(
         packageName: string,
         searchStrategies: Dowdep['dependencySearchStrategies'],
@@ -22,7 +25,7 @@ export default abstract class DowdepCommand extends Command {
 
         const knownDependencies: Dependency[] = []
 
-        // Schedule dependency updates asynchronousl and, stream every dependency back to the caller once it has been updated.
+        // Schedule dependency updates asynchronously and stream every dependency back to the caller once it has been updated.
         let yieldResolve: ($new: boolean) => void
         let yieldPromise: Promise<boolean> = new Promise(resolve => yieldResolve = resolve)  // For synchronization between depedency updates and generator
         $package.updateDependencies(dowdep, updateOptions, async () => {

### 2021-10-11 packages/cli/src/commands/list.ts

@@ -20,7 +20,7 @@ export default class List extends DowdepCommand {
         }),
         downloadGitHubData: flags.boolean({
             name: 'download-github-metadata', // TODO: Does not work!
-            description: "download additional metadata from GitHub",
+            description: "download additional metadata from GitHubn (enabled by default, prepend no to disable)",
             default: true,
             allowNo: true
         })

### 2021-10-11 packages/cli/src/commands/search.ts

@@ -23,12 +23,12 @@ export default class Search extends DowdepCommand {
         }),
         includeImports: flags.boolean({
             name: 'include-imports', // TODO does not work
-            description: "whether also to find import statements for the package",
+            description: "whether also to find import statements for the package (experimental)",
             default: false
         }),
         includeOccurences: flags.boolean({
             name: 'include-occurences',
-            description: "whether also to find indirect occurences of package types",
+            description: "whether also to find indirect occurences of package types (experimental)",
             default: false
         }),
         aggregate: flags.boolean({

### 2021-10-12 packages/core/src/dependencies/base.ts
Add debug messages

@@ -140,6 +140,7 @@ export class Dependency {
         assert(this.sourceDirectory)
 
         const searcher = dowdep.createReferenceSearcher(this, this.$package)
+        console.debug("Updating references", this.name)
 
         for await (const reference of searcher.searchReferences()) {
             const existingReference = this._references.find(existingReference =>
@@ -153,6 +154,8 @@ export class Dependency {
             this._references.push(reference)
             await updateCallback()
         }
+
+        console.debug("Updated references", this.name)
     }
 
     /**

### 2021-10-12 packages/core/src/references/types.ts
Fix file path handling for Windows
Now I really \hate\ backslashes ...

@@ -54,11 +54,12 @@ export class TypeReferenceSearcher extends ReferenceSearcher {
         this.typeChecker = program.getTypeChecker()
 
         for (const sourceFile of program.getSourceFiles()) {
-            if (!options.fileNames.includes(sourceFile.fileName)) {
+            const fileName = path.normalize(sourceFile.fileName)
+            if (!options.fileNames.includes(fileName)) {
                 // External library, maybe our own package
                 continue
             }
-            if (!allFileNames.includes(sourceFile.fileName)) {
+            if (!allFileNames.includes(fileName)) {
                 // Irrelevant file such as bundle
                 continue
             }
@@ -77,6 +78,7 @@ export class TypeReferenceSearcher extends ReferenceSearcher {
             allowJs: true,
             checkJs: true
         })
+        options.fileNames = options.fileNames.map(path.normalize)
 
         // Since the dependency is not installed, we need to do some hacks here ...
         Object.assign(options.options, {
@@ -242,7 +244,7 @@ export class TypeReferenceSearcher extends ReferenceSearcher {
         if (!symbol.declarations) {
             return
         }
-        if ((symbol.declarations?.length ?? 0) > 10000) {
+        if ((symbol.declarations?.length ?? 0) > 10_000) {
             // Too many declarations (TypeScript mismatch), skipping
             return
         }

### 2021-10-12 packages/vscode-extension/src/dependencies.ts

@@ -143,7 +143,7 @@ class DependencyFileNodeItem extends ReferenceFileNodeItem<
         await vscode.commands.executeCommand(
             'dowdep.openDependencyFolder',
             this.dependency,
-            this.path.join('/')
+            this.path.join(DependencyFileNodeItem.pathSeparator)
         )
     }
 }

### 2021-10-12 packages/vscode-extension/src/references.ts

@@ -150,7 +150,7 @@ class PackageFileNodeItem extends ReferenceFileNodeItem<
         await vscode.commands.executeCommand(
             'dowdep.openPackageFileOrFolder',
             this.$package,
-            this.path.join('/')
+            this.path.join(PackageFileNodeItem.pathSeparator)
         )
     }
 }

### 2021-10-12 packages/vscode-extension/src/views.ts

@@ -183,8 +183,9 @@ export abstract class ReferenceFileNodeItem<
         })
     }
 
+    protected static readonly pathSeparator = path.sep
     /** Magic number to denote leaves, @see {@link getPathSegment}. */
-    protected static readonly leafPathSegment = '//'
+    protected static readonly leafPathSegment = this.pathSeparator.repeat(2)
 
     get dependency() {
         const anyReference = this.allLeafs[0]
@@ -204,7 +205,8 @@ export abstract class ReferenceFileNodeItem<
 
     protected getPath(reference: Reference) {
         const { fileUri, baseUri } = this.getFullPath(reference)
-        return fileUri.path.split('/').slice(baseUri.path.split('/').length)
+        const separatorPattern = new RegExp(`[/\\${ReferenceFileNodeItem.pathSeparator}]`)
+        return fileUri.path.split(separatorPattern).slice(baseUri.path.split(separatorPattern).length)
     }
 
     protected createItemChild(pathSegmentOrLeaf: string | Reference): TFileNodeItem | TMemberNodeItem {

### 2021-10-12 packages/core/src/references/types.ts
TypeReferenceSearcher: Fix exclusion of irrelevant node_modules folders
The target package or the analyzed dependency may indeed be located in a node_modules folder.

@@ -125,8 +125,12 @@ export class TypeReferenceSearcher extends ReferenceSearcher {
                 // Pretend this dependent to be installed
                 return true
             }
-            if (path.basename(directoryName) == 'node_modules' && !pathIsInside(path.resolve(directoryName), path.resolve(this.dependencyDirectory))) {
-                // Stop module resolution outside dependent folder - this might cause unintended side effects and will slow down search significantly
+            if (path.basename(directoryName) == 'node_modules' && !(
+                pathIsInside(path.resolve(directoryName), path.resolve(this.dependencyDirectory))
+                    || pathIsInside(path.resolve(this.dependencyDirectory), path.resolve(directoryName))
+                    || pathIsInside(path.resolve(directoryName), path.resolve(this.packageDirectory))
+                    || pathIsInside(path.resolve(this.packageDirectory), path.resolve(directoryName)))) {
+                // Stop module resolution outside relevant source folders - this might cause unintended side effects and will slow down search significantly
                 return false
             }
             return basicDirectoryExists(directoryName)

### 2021-10-12 packages/vscode-extension/src/extension.ts
Add smoke test for extension

@@ -27,8 +27,9 @@ export function activate(context: vscode.ExtensionContext) {
     console.log("The extension \"dowdep\" is now active.")
 
     extension = new Extension(context)
-
     extension.activate()
+
+    return extension
 }
 
 /**

### 2021-10-12 packages/vscode-extension/test/runTest.ts

@@ -2,18 +2,24 @@ import * as path from 'path'
 
 import { runTests } from 'vscode-test'
 
+
 async function main() {
     try {
         // The folder containing the Extension Manifest package.json
-        // Passed to `--extensionDevelopmentPath`
         const extensionDevelopmentPath = path.resolve(__dirname, '../../')
 
         // The path to test runner
-        // Passed to --extensionTestsPath
         const extensionTestsPath = path.resolve(__dirname, './suite/index')
 
+        const testWorkspacePath = path.resolve(__dirname, '../node_modules/jsonschema')
+        console.log("starting in", testWorkspacePath)
+
         // Download VS Code, unzip it and run the integration test
-        await runTests({ extensionDevelopmentPath, extensionTestsPath })
+        await runTests({
+            extensionDevelopmentPath,
+            extensionTestsPath,
+            launchArgs: [testWorkspacePath]
+        })
     } catch (err) {
         console.error("Failed to run tests")
         process.exit(1)

### 2021-10-12 packages/vscode-extension/test/suite/extension.test.ts

@@ -1,15 +1,63 @@
-import * as assert from 'assert'
+import assert from 'assert'
 
 // You can import and use all API from the 'vscode' module
 // as well as import your extension to test it
 import * as vscode from 'vscode'
-// import * as myExtension from '../../extension'
+import { Extension } from '../../src/extension'
+import { ReferenceItem } from '../../src/views'
+
+
+const pkgName = 'jsonschema'
+
+async function activateExtension() {
+    const ext = vscode.extensions.getExtension<Extension>('LinqLover.dowdep-vscode-extension')
+    assert(ext)
+
+    if (!ext.isActive) {
+        await ext.activate()
+    }
+
+    return ext.exports
+}
 
 suite("Extension Test Suite", () => {
     vscode.window.showInformationMessage("Start all tests.")
 
-    test("Sample test", () => {
-        assert.strictEqual(-1, [1, 2, 3].indexOf(5))
-        assert.strictEqual(-1, [1, 2, 3].indexOf(0))
+    test("Smoke test", async () => {
+        const ext = await activateExtension()
+        assert(ext)
+        assert(ext.packages[0]?.name === pkgName)
+
+        const depLimit = 6
+        await vscode.workspace.getConfiguration().update('dowdep.dependencyLimit', depLimit)
+
+        let pkgItem = ext.dependenciesProvider.getChildren()[0]
+        assert(pkgItem)
+        assert(pkgItem.label?.toString() === pkgName)
+        assert([...pkgItem.getChildren()].length === 0)
+
+        await ext.refreshDownstreamData()
+
+        pkgItem = ext.dependenciesProvider.getChildren()[0]
+        assert(pkgItem)
+        assert(pkgItem.label?.toString() === pkgName)
+
+        const depItems = [...pkgItem.getChildren()]
+        assert(depItems.length >= depLimit / 1.5)
+        for (const depItem of depItems) {
+            assert(depItem.label?.toString())
+            assert(depItem.tooltip)
+        }
+
+        const nonEmptyDepItems = depItems.filter(depItem => [...depItem.getChildren()].length)
+        assert(nonEmptyDepItems.length >= depItems.length / 2)
+        for (const depItem of nonEmptyDepItems) {
+            const refItems = [...depItem.findAllLeafs()]
+            assert(refItems.length)
+            for (const refItem of refItems) {
+                assert(refItem.constructor.name === ReferenceItem.name)
+                assert(refItem.label?.toString())
+            }
+        }
     })
 })

### 2021-10-12 packages/vscode-extension/src/views.ts
VSCE: Decline stars and forks correctly

@@ -1,6 +1,7 @@
 import { strict as assert } from 'assert'
 import { Dependency, Package, Reference } from 'dowdep'
 import _ from 'lodash'
+import path from 'path'
 import truncate from 'truncate'
 import * as vscode from 'vscode'
 
@@ -159,10 +160,12 @@ export abstract class DependencyItem<
             yield md`---`
             yield
             yield md`GitHub: ${
-                [
-                    ["stars", this.dependency.githubRepository.stargazerCount],
-                    ["forks", this.dependency.githubRepository.forkCount]
-                ].map(([label, count]) => md`${count} ${label}`.value).join(" ⸱ ")
+                (<[[string, string], number][]>[
+                    [["star", "stars"], this.dependency.githubRepository.stargazerCount],
+                    [["fork", "forks"], this.dependency.githubRepository.forkCount]
+                ]).map(([[labelSingular, labelPlural], count]) => md`${count} ${
+                    count === 1 ? labelSingular : labelPlural
+                }`.value).join(" ⸱ ")
             }`
         }
     }

### 2021-10-12 packages/vscode-extension/src/extension.ts
VSCE: Prevent errors when opening a dependency directory

@@ -388,6 +388,10 @@ export class Extension {
         }
         const directoryUri = vscode.Uri.file(dependency.sourceDirectory)
         const fileUri = vscode.Uri.joinPath(directoryUri, relativePath)
+        if ((await vscode.workspace.fs.stat(fileUri)).type === vscode.FileType.Directory) {
+            console.warn("Will not open dependency directory", fileUri)
+            return
+        }
         await vscode.commands.executeCommand('vscode.open', fileUri)
     }
 

### 2021-10-12 packages/vscode-extension/test/runTest.ts
Fix just another test path

@@ -11,7 +11,7 @@ async function main() {
         // The path to test runner
         const extensionTestsPath = path.resolve(__dirname, './suite/index')
 
-        const testWorkspacePath = path.resolve(__dirname, '../node_modules/jsonschema')
+        const testWorkspacePath = path.resolve(__dirname, '../../node_modules/jsonschema')
         console.log("starting in", testWorkspacePath)
 
         // Download VS Code, unzip it and run the integration test

### 2021-10-12 docs/paper/sections/0_abstract.tex
Remove todo

@@
 				All artifacts are available on GitHub under the following URL: \url{https://github.com/LinqLover/downstream-repository-mining}
-				\TODO{Insert name and use link to VSCE}
 			}

### 2021-10-12 packages/core/src/dependencies/sourcegraph.ts
Fix import errors from core package once again
After restructuring the core package, dynamic imports did not work any longer because apparently, they must not be called from submodules. Relates #65 and https://github.com/microsoft/TypeScript/issues/43329, again.

@@ -5,6 +5,7 @@ import normalizePackageData from 'normalize-package-data'
 
 import { Dependency, DependencySearcher } from './base'
 import { Dowdep } from '../dowdep'
+import externalModules from '../externalModules'
 import { Package } from '../packages'
 import { OnlyData } from '../utils/OnlyData'
 
@@ -147,11 +148,7 @@ class SourcegraphClient {
             'count': `${limit || this.maximumLimit}`
         }
 
-        // Workaround for https://github.com/microsoft/vscode/issues/130367 and https://github.com/microsoft/TypeScript/issues/43329 🤯
-        const dynamicImport = new Function('moduleName', 'return import(moduleName)')
-        const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
-
-        const query = `"${escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
+        const query = `"${externalModules.escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
         const response = this.documentSpecifier.protoResponse
         Object.assign(response, await graphql.request(this.documentSpecifier.document, { query }))
 

### 2021-10-12 packages/core/src/externalModules.ts

@@ -1,0 +1,19 @@
+import type { Import, Options } from "parse-imports"
+
+
+/**
+ * Stores external modules that have been loaded in a non-standard, weird way.
+ * 
+ * The existence of this is a large workaround. Some components of our toolchain, including oclif and jest, do not support dynamic importing of pure ES modules correctly. See `loadExternalModules()` in `index.ts`. As the technique used there cannot be applied from submodules, imported modules are stored in this file.
+ */
+const modules = {
+    /** Escape RegExp special characters */
+    escapeRegexp: <(regex: string) => string><any>undefined,
+    /** A blazing fast ES module imports parser. */
+    parseImports: <(
+        code: string,
+        options?: Options
+    ) => Promise<Iterable<Import>>><any>undefined
+}
+
+export default modules

### 2021-10-12 packages/core/src/index.ts

@@ -16,3 +16,52 @@ export {
     ReferenceSearcher,
     ReferenceSearchStrategy
 } from './references'
+
+import pkgDir from 'pkg-dir'
+import externalModules from './externalModules'
+
+let _loadedExternalModules = false
+
+/** Load external modules asynchronously that cannot be imported in the usual way. See `externalModules.ts` for details. This function must be called before using any other  functionality of this package! */
+export async function loadExternalModules() {
+    if (_loadedExternalModules) {
+        return
+    }
+
+    /**
+     * Truly awful hack! There are a few things going on here:
+     * - Jest (or something) can't find parse-imports by just importing its package name
+     *   no matter what. Just give it the path to the src/index.js file
+     * - Workaround for https://github.com/microsoft/TypeScript/issues/43329.
+     *
+     * - TypeScript will always try to replace dynamic imports with `requires` which doesn't work for importing ESM from CJS.
+     *   We work around by "hiding" our dynamic import in a Function constructor (terrible...).
+     *
+     * In particular, we must not extract this call into a separate module.
+     * This would result in sporadic unresolved promises in the jest environment.
+     * See #65.
+     * 
+     * All of this required jest@next, ts-jest@next, AND `NODE_OPTIONS=--experimental-vm-modules`
+     * 
+     * Developed with the kind help of @TomerAbach.
+     */
+    const dynamicImport = new Function('moduleName', 'return import(moduleName)')
+
+    externalModules.escapeRegexp = (await dynamicImport('escape-string-regexp')).default
+    const parseImportsIndexPath = `${await pkgDir()}/node_modules/parse-imports/src/index.js`
+
+    try {
+        externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
+    } catch (parseError) {
+        if (!(parseError instanceof Error && 'code' in parseError && (<{ code: string }>parseError).code == 'ERR_MODULE_NOT_FOUND')) {
+            throw parseError
+        }
+        // This will occur if this package is imported as a local dependency from another package via a symlink.
+        // For now, let's handle this by assuming the depending package is a sibling of ourselves ...
+        // Hardcoded! So many hacks! 😭
+        const parseImportsIndexPath = `${await pkgDir()}/../core/node_modules/parse-imports/src/index.js`
+        externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
+    }
+
+    _loadedExternalModules = true
+}

### 2021-10-12 packages/core/src/references/heuristic.ts

@@ -8,6 +8,7 @@ import path from 'path'
 import pkgDir from 'pkg-dir'
 
 import { DeclarationImport, FilePosition, ReferenceSearcher, Reference, ReferenceLocation } from './base'
+import externalModules from '../externalModules'
 import rex from '../utils/rex'
 
 
@@ -40,25 +41,12 @@ export class HeuristicReferenceSearcher extends ReferenceSearcher {
 
         const identifierPattern = /[\p{L}\p{Nl}$_][\p{L}\p{Nl}$\p{Mn}\p{Mc}\p{Nd}\p{Pc}]*/u
 
-        /**
-         * Workaround for https://github.com/microsoft/TypeScript/issues/43329.
-         *
-         * TypeScript will always try to replace dynamic imports with `requires` which doesn't work for importing ESM from CJS.
-         * We work around by "hiding" our dynamic import in a Function constructor (terrible...).
-         *
-         * In particular, we must not extract this call into a separate module.
-         * This would result in sporadic unresolved promises in the jest environment.
-         * See #65.
-         */
-        const dynamicImport = new Function('moduleName', 'return import(moduleName)')
-        const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
-
         const requirePattern = rex`
             (?<alias> ${identifierPattern} ) \s*
             = \s*
             require \s* \( \s*
                 (?<quote>['"])
-                (?<packageName> ${escapeRegexp(this.$package.name)} )
+                (?<packageName> ${externalModules.escapeRegexp!(this.$package.name)} )
                 (
                     \/ (?<memberName> ${identifierPattern} )
                 )?
@@ -154,42 +142,7 @@ export class HeuristicReferenceSearcher extends ReferenceSearcher {
     async* collectEsmBindings(source: string): AsyncGenerator<ModuleBinding, void, undefined> {
         const imports = await (async () => {
             try {
-                // Truly awful hack! There are a few things going on here:
-                // - Jest (or something) can't find parse-imports by just importing its package name
-                //   no matter what. Just give it the path to the src/index.js file
-                //
-                // - Workaround for https://github.com/microsoft/TypeScript/issues/43329.
-                //
-                //   TypeScript will always try to replace dynamic imports with `requires` which doesn't work for importing ESM from CJS.
-                //   We work around by "hiding" our dynamic import in a Function constructor (terrible...).
-                //
-                //   In particular, we must not extract this call into a separate module.
[…]

### 2021-10-12 packages/core/test/references.test.ts

@@ -8,6 +8,7 @@ import ifCurtailed from '../src/utils/if-curtailed'
 import { lodashClassifyNested } from '../src/utils/lodash-classify'
 import { getSourceDirectory } from './_utils/sourceDirectory'
 import { printDiff } from './_utils/printDiff'
+import { loadExternalModules } from '../src'
 
 
 const SOURCE_DIRECTORY = getSourceDirectory(__filename)
@@ -37,6 +38,8 @@ describe('ReferenceSearcher', () => {
             ([packageName, expectedReferences]) => ({ strategy: <ReferenceSearchStrategy>strategy, packageName, expectedReferences }))
     ))("should find relevant references for %s", async (
         { strategy, packageName, expectedReferences }) => {
+        await loadExternalModules()
+
         const $package = new Package(
             packageName,
             `${SOURCE_DIRECTORY}/examples/packages/${packageName}`

### 2021-10-12 packages/vscode-extension/src/extension.ts

@@ -1,4 +1,4 @@
-import { DeclarationLocation, Dependency, Dowdep, FilePosition, Package, Reference, ReferenceSearchStrategy } from 'dowdep'
+import { DeclarationLocation, Dependency, Dowdep, FilePosition, loadExternalModules, Package, Reference, ReferenceSearchStrategy } from 'dowdep'
 import _ from 'lodash'
 import filterAsync from 'node-filter-async'
 import normalizePackageData from 'normalize-package-data'
@@ -23,12 +23,13 @@ type PackageLike = Package | readonly Package[]
 /**
  * This method is called on the first activation event.
  */
-export function activate(context: vscode.ExtensionContext) {
-    console.log("The extension \"dowdep\" is now active.")
+export async function activate(context: vscode.ExtensionContext) {
+    await loadExternalModules()
 
     extension = new Extension(context)
     extension.activate()
 
+    console.log("The extension \"dowdep\" is now active.")
     return extension
 }
 

### 2021-10-12 packages/core/src/externalModules.ts
Please linter

@@ -3,17 +3,17 @@ import type { Import, Options } from "parse-imports"
 
 /**
  * Stores external modules that have been loaded in a non-standard, weird way.
- * 
+ *
  * The existence of this is a large workaround. Some components of our toolchain, including oclif and jest, do not support dynamic importing of pure ES modules correctly. See `loadExternalModules()` in `index.ts`. As the technique used there cannot be applied from submodules, imported modules are stored in this file.
  */
 const modules = {
     /** Escape RegExp special characters */
-    escapeRegexp: <(regex: string) => string><any>undefined,
+    escapeRegexp: <(regex: string) => string><unknown>undefined,
     /** A blazing fast ES module imports parser. */
     parseImports: <(
         code: string,
         options?: Options
-    ) => Promise<Iterable<Import>>><any>undefined
+    ) => Promise<Iterable<Import>>><unknown>undefined
 }
 
 export default modules

### 2021-10-12 packages/core/src/index.ts

@@ -40,9 +40,9 @@ export async function loadExternalModules() {
      * In particular, we must not extract this call into a separate module.
      * This would result in sporadic unresolved promises in the jest environment.
      * See #65.
-     * 
+     *
      * All of this required jest@next, ts-jest@next, AND `NODE_OPTIONS=--experimental-vm-modules`
-     * 
+     *
      * Developed with the kind help of @TomerAbach.
      */
     const dynamicImport = new Function('moduleName', 'return import(moduleName)')

### 2021-10-12 packages/core/src/references/heuristic.ts

@@ -3,9 +3,7 @@ import { promises as fsPromises } from 'fs'
 import itAll from 'it-all'
 import LinesAndColumns from 'lines-and-columns'
 import _ from 'lodash'
-import type { Import, Options } from 'parse-imports'
 import path from 'path'
-import pkgDir from 'pkg-dir'
 
 import { DeclarationImport, FilePosition, ReferenceSearcher, Reference, ReferenceLocation } from './base'
 import externalModules from '../externalModules'
@@ -46,7 +44,7 @@ export class HeuristicReferenceSearcher extends ReferenceSearcher {
             = \s*
             require \s* \( \s*
                 (?<quote>['"])
-                (?<packageName> ${externalModules.escapeRegexp!(this.$package.name)} )
+                (?<packageName> ${externalModules.escapeRegexp(this.$package.name)} )
                 (
                     \/ (?<memberName> ${identifierPattern} )
                 )?

### 2021-10-12 packages/core/src/index.ts
Fix module resolution for Windows

@@ -17,7 +17,6 @@ export {
     ReferenceSearchStrategy
 } from './references'
 
-import pkgDir from 'pkg-dir'
 import externalModules from './externalModules'
 
 let _loadedExternalModules = false
@@ -46,9 +45,10 @@ export async function loadExternalModules() {
      * Developed with the kind help of @TomerAbach.
      */
     const dynamicImport = new Function('moduleName', 'return import(moduleName)')
+    const dir = `file://${__dirname}/..`
 
     externalModules.escapeRegexp = (await dynamicImport('escape-string-regexp')).default
-    const parseImportsIndexPath = `${await pkgDir()}/node_modules/parse-imports/src/index.js`
+    const parseImportsIndexPath = `${dir}/node_modules/parse-imports/src/index.js`
 
     try {
         externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
@@ -59,7 +59,7 @@ export async function loadExternalModules() {
         // This will occur if this package is imported as a local dependency from another package via a symlink.
         // For now, let's handle this by assuming the depending package is a sibling of ourselves ...
         // Hardcoded! So many hacks! 😭
-        const parseImportsIndexPath = `${await pkgDir()}/../core/node_modules/parse-imports/src/index.js`
+        const parseImportsIndexPath = `${dir}/../core/node_modules/parse-imports/src/index.js`
         externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
     }
 

### 2021-10-12 packages/core/src/dowdep.ts
Specify missing dependency on path-exists

@@ -1,5 +1,5 @@
 import path from 'path'
-import pathExists from 'path-exists'
+import { pathExists } from 'path-exists'
 
 import { createDependencySearcher, Dependency, DependencySearcher, DependencySearchStrategy } from './dependencies'
 import { Package } from './packages'

### 2021-10-12 packages/core/src/dowdep.ts
Fix import of path-exists

@@ -1,5 +1,4 @@
 import path from 'path'
-import { pathExists } from 'path-exists'
 
 import { createDependencySearcher, Dependency, DependencySearcher, DependencySearchStrategy } from './dependencies'
 import { Package } from './packages'
@@ -54,6 +53,6 @@ export interface FileSystem {
 }
 
 export const defaultFileSystem: FileSystem = {
-    exists: pathExists,
+    exists: <FileSystem['exists']><unknown>undefined,
     join: path.join
 }

### 2021-10-12 packages/core/src/externalModules.ts

@@ -13,7 +13,8 @@ const modules = {
     parseImports: <(
         code: string,
         options?: Options
-    ) => Promise<Iterable<Import>>><unknown>undefined
+    ) => Promise<Iterable<Import>>><unknown>undefined,
+    pathExists: <(path: string) => Promise<boolean>><unknown>undefined
 }
 
 export default modules

### 2021-10-12 packages/core/src/index.ts

@@ -17,6 +17,7 @@ export {
     ReferenceSearchStrategy
 } from './references'
 
+import { defaultFileSystem } from './dowdep'
 import externalModules from './externalModules'
 
 let _loadedExternalModules = false
@@ -48,8 +49,8 @@ export async function loadExternalModules() {
     const dir = `file://${__dirname}/..`
 
     externalModules.escapeRegexp = (await dynamicImport('escape-string-regexp')).default
-    const parseImportsIndexPath = `${dir}/node_modules/parse-imports/src/index.js`
 
+    const parseImportsIndexPath = `${dir}/node_modules/parse-imports/src/index.js`
     try {
         externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
     } catch (parseError) {
@@ -62,6 +63,9 @@ export async function loadExternalModules() {
         const parseImportsIndexPath = `${dir}/../core/node_modules/parse-imports/src/index.js`
         externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
     }
+
+    externalModules.pathExists = (await dynamicImport('path-exists')).pathExists
+    defaultFileSystem.exists = externalModules.pathExists
 
     _loadedExternalModules = true
 }

### 2021-10-12 packages/core/test/npm-dependencies.test.ts
Fix npm tests (add missing loadExternalModules())

@@ -7,7 +7,7 @@ import { promisify } from 'util'
 import { Package } from '../src'
 import { NpmDependency } from '../src/dependencies/npm'
 
-import { Dowdep } from '../src'
+import { Dowdep, loadExternalModules } from '../src'
 
 const readPackageJson = <(file: string) => Promise<PackageJson>><unknown>  // BUG in type definitions: https://github.com/DefinitelyTyped/DefinitelyTyped/issues/33340
     promisify(readPackageJsonCallback)
@@ -69,6 +69,8 @@ describe('updateSource', () => {
         jest.setTimeout(5000)
         assert(process.env.NPM_CACHE)
         await (promisify(rimRaf))(process.env.NPM_CACHE)
+
+        await loadExternalModules()
 
         const dep = new NpmDependency(packageName, <Package><unknown>undefined)
         dep.tarballUrl = tarballUrl

### 2021-10-12 packages/core/src/dowdep.ts
Engross package path-exists to eliminate dependency on node:fs which does not work in jest tests 🤯

@@ -1,3 +1,4 @@
+import { promises as fsPromises } from 'fs'
 import path from 'path'
 
 import { createDependencySearcher, Dependency, DependencySearcher, DependencySearchStrategy } from './dependencies'
@@ -53,6 +54,13 @@ export interface FileSystem {
 }
 
 export const defaultFileSystem: FileSystem = {
-    exists: <FileSystem['exists']><unknown>undefined,
+    exists: async (path: string) => {
+        try {
+            await fsPromises.access(path)
+            return true
+        } catch {
+            return false
+        }
+    },
     join: path.join
 }

### 2021-10-12 packages/core/src/externalModules.ts

@@ -13,8 +13,7 @@ const modules = {
     parseImports: <(
         code: string,
         options?: Options
-    ) => Promise<Iterable<Import>>><unknown>undefined,
-    pathExists: <(path: string) => Promise<boolean>><unknown>undefined
+    ) => Promise<Iterable<Import>>><unknown>undefined
 }
 
 export default modules

### 2021-10-12 packages/core/src/index.ts

@@ -50,9 +50,8 @@ export async function loadExternalModules() {
 
     externalModules.escapeRegexp = (await dynamicImport('escape-string-regexp')).default
 
-    const parseImportsIndexPath = `${dir}/node_modules/parse-imports/src/index.js`
     try {
-        externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
+        externalModules.parseImports = (await dynamicImport(`${dir}/node_modules/parse-imports/src/index.js`)).default
     } catch (parseError) {
         if (!(parseError instanceof Error && 'code' in parseError && (<{ code: string }>parseError).code == 'ERR_MODULE_NOT_FOUND')) {
             throw parseError
@@ -63,9 +62,6 @@ export async function loadExternalModules() {
         const parseImportsIndexPath = `${dir}/../core/node_modules/parse-imports/src/index.js`
         externalModules.parseImports = (await dynamicImport(parseImportsIndexPath)).default
     }
-
-    externalModules.pathExists = (await dynamicImport('path-exists')).pathExists
-    defaultFileSystem.exists = externalModules.pathExists
 
     _loadedExternalModules = true
 }

### 2021-10-12 packages/core/test/npm-dependencies.test.ts
Fix npm tests by limitting concurrency
Just another workaround for nasty jest ...

@@ -1,16 +1,4 @@
-import assert from 'assert'
-import { FullMetadata as PackageJson } from 'package-json'
-import * as path from 'path'
-import readPackageJsonCallback from 'read-package-json'
-import rimRaf from 'rimraf'
-import { promisify } from 'util'
-import { Package } from '../src'
-import { NpmDependency } from '../src/dependencies/npm'
-
-import { Dowdep, loadExternalModules } from '../src'
-
-const readPackageJson = <(file: string) => Promise<PackageJson>><unknown>  // BUG in type definitions: https://github.com/DefinitelyTyped/DefinitelyTyped/issues/33340
-    promisify(readPackageJsonCallback)
+import { Dowdep, Package } from '../src'
 
 
 describe('updateDependencies', () => {
@@ -55,32 +43,4 @@ describe('updateDependencies', () => {
             }
         }
     }, 60000)
-})
-
-describe('updateSource', () => {
-    it.each`
-        packageName     | version     | tarballUrl
-        ${'gl-matrix'}  | ${'3.3.0'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.3.0.tgz'}
-        ${'gl-matrix'}  | ${'3.2.1'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.2.1.tgz'}
-    `("should fetch the package '$packageName' with the right version '$version'", async (
-        { packageName, version, tarballUrl }: {
-            packageName: string, version: string, tarballUrl: string
-        }) => {
-        jest.setTimeout(5000)
-        assert(process.env.NPM_CACHE)
-        await (promisify(rimRaf))(process.env.NPM_CACHE)
-
-        await loadExternalModules()
-
-        const dep = new NpmDependency(packageName, <Package><unknown>undefined)
-        dep.tarballUrl = tarballUrl
-
-        const dowdep = new Dowdep({
-            sourceCacheDirectory: process.env.NPM_CACHE || 'cache'
-        })
-        await dep.updateSource(dowdep)
-
-        const data = await readPackageJson(path.join(<string>process.env.NPM_CACHE, packageName, 'package.json'))
-        expect(data.version).toBe(version)
-    })
 })

### 2021-10-12 packages/core/test/npm-dependencies.updateSource.test.ts

@@ -1,0 +1,42 @@
+import assert from 'assert'
+import { FullMetadata as PackageJson } from 'package-json'
+import * as path from 'path'
+import readPackageJsonCallback from 'read-package-json'
+import rimRaf from 'rimraf'
+import { promisify } from 'util'
+import { Package } from '../src'
+import { NpmDependency } from '../src/dependencies/npm'
+
+import { Dowdep, loadExternalModules } from '../src'
+
+const readPackageJson = <(file: string) => Promise<PackageJson>><unknown>  // BUG in type definitions: https://github.com/DefinitelyTyped/DefinitelyTyped/issues/33340
+    promisify(readPackageJsonCallback)
+
+
+describe('updateSource', () => {
+    it.each`
+        packageName     | version     | tarballUrl
+        ${'gl-matrix'}  | ${'3.3.0'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.3.0.tgz'}
+        ${'gl-matrix'}  | ${'3.2.1'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.2.1.tgz'}
+    `("should fetch the package '$packageName' with the right version '$version'", async (
+        { packageName, version, tarballUrl }: {
+            packageName: string, version: string, tarballUrl: string
+        }) => {
+        jest.setTimeout(5000)
+        assert(process.env.NPM_CACHE)
+        await (promisify(rimRaf))(process.env.NPM_CACHE)
+
+        await loadExternalModules()
+
+        const dep = new NpmDependency(packageName, <Package><unknown>undefined)
+        dep.tarballUrl = tarballUrl
+
+        const dowdep = new Dowdep({
+            sourceCacheDirectory: process.env.NPM_CACHE || 'cache'
+        })
+        await dep.updateSource(dowdep)
+
+        const data = await readPackageJson(path.join(<string>process.env.NPM_CACHE, packageName, 'package.json'))
+        expect(data.version).toBe(version)
+    })
+})

### 2021-10-12 packages/core/src/references/index.ts
Remove dangling debug artifacts

@@ -60,7 +60,6 @@ export class ReferenceCollector {
     protected async* basicSearchReferences(rootDirectory: string, limit: number | undefined, includeKinds: readonly ReferenceKind[] | '*', depth: number): AsyncIterable<Reference> {
         if (!await fsExists(path.join(rootDirectory, 'package.json'))) {
             // Search recursively
-            console.log("read", rootDirectory)
             let depDirectories: Iterable<Dirent> = []
             try {
                 depDirectories = (
@@ -69,7 +68,6 @@ export class ReferenceCollector {
             } catch (ex) {
                 console.error(ex)
             }
-            console.log("did read", depDirectories)
 
             let i = 0
             for await (const depDirectory of depDirectories) {

### 2021-10-12 packages/cli/scripts/download-package.sh
Refactoring, many fixes, and documentation (#260)
Among others, this adds crash tests for the extension and makes it compatible with Windows.

* Document CLI
* Document, restructure, and refactor core
* Rename `npm run install-all` (previously `update-lockfiles`)
* Fix type error
* Document & clean-up VSCE
* Update UPSTREAM.md
* Update README.mds
* Enhance documentation
* Revise todo comments
* Document initial configuration of the extension
* Add debug messages
* Fix file path handling for Windows

Now I really \hate\ backslashes ...
* TypeReferenceSearcher: Fix exclusion of irrelevant node_m

@@ -1,4 +1,10 @@
-#!/bin/bash
+#!/usr/bin/env bash
+# Download a package from npm. For experimental purposes.
+# Usage:
+#   ./download-package.sh package
+# Expected vars:
+#   NPM_CACHE - path to download
+
 set -ex
 
 cd "$NPM_CACHE" || exit 1

### 2021-10-12 packages/cli/scripts/test-cli.sh

@@ -1,4 +1,11 @@
 #!/usr/bin/env bash
+# Rough acceptance tests for the CLI.
+# Usage:
+#   ./test-cli.sh
+# Expected vars:
+#   GITHUB_OAUTH_TOKEN
+#   SOURCEGRAPH_TOKEN
+
 set -e
 
 fail() {

### 2021-10-12 packages/cli/src/DowdepCommand.ts

@@ -1,9 +1,12 @@
 import filterAsync from 'node-filter-async'
 import { Command } from '@oclif/command'
 
-import { Dependency, DependencyUpdateOptions, Dowdep, getCacheDirectory, Package } from 'dowdep'
+import { Dependency, DependencyUpdateOptions, Dowdep, Package } from 'dowdep'
 
+
+/** Abstract base class for all dowdep commands. */
 export default abstract class DowdepCommand extends Command {
+    /** Update dependencies for the given package name with the specified options. Once a found dependency fulfills the specified readiness predicate, stream it via the returned async iterator. */
     async *updateDependencies(
         packageName: string,
         searchStrategies: Dowdep['dependencySearchStrategies'],
@@ -16,14 +19,15 @@ export default abstract class DowdepCommand extends Command {
             dependencyLimit: limit,
             githubAccessToken: process.env.GITHUB_OAUTH_TOKEN,
             sourcegraphToken: process.env.SOURCEGRAPH_TOKEN,
-            sourceCacheDirectory: getCacheDirectory()
+            sourceCacheDirectory: this.cacheDirectory
         })
         const $package = new Package(packageName)
 
         const knownDependencies: Dependency[] = []
 
+        // Schedule dependency updates asynchronously and stream every dependency back to the caller once it has been updated.
         let yieldResolve: ($new: boolean) => void
-        let yieldPromise: Promise<boolean> = new Promise(resolve => yieldResolve = resolve)
+        let yieldPromise: Promise<boolean> = new Promise(resolve => yieldResolve = resolve)  // For synchronization between depedency updates and generator
         $package.updateDependencies(dowdep, updateOptions, async () => {
             (await filterAsync(
                 [...$package.dependencies],
@@ -51,5 +55,9 @@ export default abstract class DowdepCommand extends Command {
             }
             yieldPromise = new Promise(resolve => yieldResolve = resolve)
         }
+    }
+
+    get cacheDirectory() {
+        return process.env.NPM_CACHE || 'cache'
     }
 }

### 2021-10-12 packages/cli/src/commands/download.ts

@@ -1,5 +1,5 @@
 import { flags } from '@oclif/command'
-import asyncIteratorToArray from 'it-all'
+import itAll from 'it-all'
 
 import DowdepCommand from '../DowdepCommand'
 import tqdm2 from '../utils/tqdm2'
@@ -26,6 +26,7 @@ export default class Download extends DowdepCommand {
     async run(): Promise<void> {
         const { args, flags } = this.parse(Download)
 
+        // Input
         const packageName: string = args.packageName
         if (!packageName) throw new Error("dowdep-cli: Package not specified")
         const limit = flags.limit == -1 ? undefined : flags.limit
@@ -33,7 +34,8 @@ export default class Download extends DowdepCommand {
             ? [<'npm' | 'sourcegraph'>flags.strategies]
             : <['npm', 'sourcegraph']>['npm', 'sourcegraph']
 
-        const dependencies = await asyncIteratorToArray(
+        // Processing
+        const dependencies = await itAll(
             tqdm2(
                 this.updateDependencies(
                     packageName,
@@ -48,6 +50,7 @@ export default class Download extends DowdepCommand {
             )
         )
 
+        // Output
         console.log(`Download completed, ${dependencies.length} successful`)
     }
 }

### 2021-10-12 packages/cli/src/commands/list.ts

@@ -7,6 +7,7 @@ import tqdm2 from '../utils/tqdm2'
 export default class List extends DowdepCommand {
     static description = 'list downstream dependencies'
 
+    // TODO: Command aliases do not work!
     static flags = {
         help: flags.help({ char: 'h' }),
         limit: flags.integer({
@@ -19,8 +20,8 @@ export default class List extends DowdepCommand {
             default: 'all'
         }),
         downloadGitHubData: flags.boolean({
-            name: 'download-github-metadata', // TODO: Does not work!
-            description: "download GitHub metadata",
+            name: 'download-github-metadata',
+            description: "download additional metadata from GitHubn (enabled by default, prepend no to disable)",
             default: true,
             allowNo: true
         })
@@ -31,6 +32,7 @@ export default class List extends DowdepCommand {
     async run() {
         const { args, flags } = this.parse(List)
 
+        // Input
         const packageName: string = args.packageName
         if (!packageName) throw new Error("dowdep-cli: Package not specified")
         const limit = flags.limit == -1 ? undefined : flags.limit
@@ -39,6 +41,7 @@ export default class List extends DowdepCommand {
             : <['npm', 'sourcegraph']>['npm', 'sourcegraph']
         const downloadGitHubData = flags.downloadGitHubData
 
+        // Processing
         for await (const dependency of tqdm2(
             this.updateDependencies(
                 packageName,
@@ -53,7 +56,7 @@ export default class List extends DowdepCommand {
             {
                 description: "Listing dependencies"
             }
-        )) {
+        )) {  // Output
             console.dir(dependency, {
                 showHidden: false,
                 depth: 1

### 2021-10-12 packages/core/src/dependencies/base.ts

@@ -13,6 +13,7 @@ import isDefined from '../utils/isDefined'
 import { OnlyData } from '../utils/OnlyData'
 
 
+/** A downstream dependency of a {@link Package}. */
 export class Dependency {
     constructor(
         public name: string,
@@ -28,7 +29,9 @@ export class Dependency {
     /** In kilobyte (kB). */
     static maximumRepositorySize = 100_000
     get githubUrl() {
-        return [...this.urls.entries()].find(([key, ]) => key.toLowerCase() === 'github')?.[1]
+        return [...this.urls.entries()].find((
+            [key, ]) => key.toLowerCase() === 'github'
+        )?.[1]
     }
     get isGitHubRepositoryReady() {
         if (_.isUndefined(this.githubRepository)) {
@@ -42,15 +45,20 @@ export class Dependency {
 
     get references() { return this._references }
     get urls() {
+        // Pretty-print URL labels
         const map = new Map<string, string>([...this.pluggableUrls.entries()].map(
             ([key, value]) => [key && ({"github": "GitHub"}[key] ?? key) || '?', value]
         ))
+
+        // Prefer official GitHub URL if available
         if (this.githubRepository?.url) {
             map.set("GitHub", this.githubRepository.url)
         }
+
         return map
     }
 
+    /** Update this dependency from multiple data sources as specified in the `options`. After each step, evauate `updateCallback`. */
     async update(dowdep: Dowdep, options: Partial<DependencyUpdateOptions> = {}, updateCallback?: DependencyUpdateCallback) {
         const jobs = [...this.collectUpdateJobs(dowdep, options)]
         await Promise.allSettled(jobs.map(async (job, index) => {
@@ -72,12 +80,13 @@ export class Dependency {
         return isDefined(this.sourceDirectory) && await dowdep.fileSystem.exists(this.sourceDirectory)
     }
 
+    /** Download the source code for this dependency from GitHub unless already cached. */
     async updateSource(dowdep: Dowdep): Promise<boolean> {
         if (!this.urls.size) {
             return false
         }
         if (await this.isSourceCodeReady(dowdep)) {
-            return true // TODO: What to return here?
+            return true
         }
 
         const cacheDirectory = dowdep.sourceCacheDirectory
@@ -91,7 +100,8 @@ export class Dependency {
         if (this.githubUrl) {
             const url = parseGitHubRepoUrl(this.githubUrl)
             if (!url) {
-                return false // TODO: Raise?
[…]

### 2021-10-12 packages/core/src/dependencies/npm.ts

@@ -11,6 +11,7 @@ import { OnlyData } from '../utils/OnlyData'
 import { URL } from 'url'
 
 
+/** A downstream dependency of a {@link Package} that was retrieved from npm. */
 export class NpmDependency extends Dependency {
     tarballUrl?: string
 
@@ -32,6 +33,7 @@ export class NpmDependency extends Dependency {
         await super.update(dowdep, options, updateCallback)
     }
 
+    /** Download the source code of this dependency from the npm registry. */
     async updateSource(dowdep: Dowdep) {
         if (!this.tarballUrl) {
             return false
@@ -40,11 +42,11 @@ export class NpmDependency extends Dependency {
         const cacheDirectory = dowdep.sourceCacheDirectory
         this.sourceDirectory = dowdep.fileSystem.join(cacheDirectory, this.name)
         if (await this.isSourceCodeReady(dowdep)) {
-            return true // TODO: What to return here?
+            return true
         }
 
         // TODO: Check system-wide npm/yarn caches?
-        // TODO: Use dowdep.fileSystem! How???
+        // TODO: Use dowdep.fileSystem!
         await downloadPackageTarball({
             url: this.tarballUrl,
             dir: cacheDirectory
@@ -52,6 +54,7 @@ export class NpmDependency extends Dependency {
         return true
     }
 
+    /** Fetch metadata about this dependency from the npm registry. */
     async updateFromRegistry() {
         const metadata = await RegistryClient.getMetadata(this.name, { fullMetadata: true })
         const latestVersion = metadata.versions?.latest
@@ -82,6 +85,7 @@ export class NpmDependency extends Dependency {
     }
 }
 
+/** Finds downstream dependencies for a package in the npm ecosystem. */
 export class NpmDependencySearcher extends DependencySearcher {
     constructor($package: Package, init: Partial<OnlyData<NpmDependencySearcher>>) {
         super($package, init)

### 2021-10-12 packages/core/src/dependencies/sourcegraph.ts

@@ -5,10 +5,12 @@ import normalizePackageData from 'normalize-package-data'
 
 import { Dependency, DependencySearcher } from './base'
 import { Dowdep } from '../dowdep'
+import externalModules from '../externalModules'
 import { Package } from '../packages'
 import { OnlyData } from '../utils/OnlyData'
 
 
+/** Finds downstream dependencies for a package on [Sourcegraph](sourcegraph.com). */
 export class SourcegraphDependencySearcher extends DependencySearcher {
     constructor($package: Package, init: Partial<OnlyData<SourcegraphDependencySearcher>>) {
         super($package, init)
@@ -145,10 +147,8 @@ class SourcegraphClient {
             '-file': 'node_modules/',
             'count': `${limit || this.maximumLimit}`
         }
-        // Workaround for https://github.com/microsoft/vscode/issues/130367 and https://github.com/microsoft/TypeScript/issues/43329 🤯
-        const dynamicImport = new Function('moduleName', 'return import(moduleName)')
-        const escapeRegexp: (regex: string) => string = (await dynamicImport('escape-string-regexp')).default
-        const query = `"${escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
+
+        const query = `"${externalModules.escapeRegexp(packageName)}": ` + Object.entries(queryArgs).map(([key, value]) => `${key}:${value}`).join(' ')
         const response = this.documentSpecifier.protoResponse
         Object.assign(response, await graphql.request(this.documentSpecifier.document, { query }))
 

### 2021-10-12 packages/core/src/dowdep.ts

@@ -1,18 +1,15 @@
-import pathExists from 'path-exists'
+import { promises as fsPromises } from 'fs'
 import path from 'path'
 
 import { createDependencySearcher, Dependency, DependencySearcher, DependencySearchStrategy } from './dependencies'
 import { Package } from './packages'
-import { PackageReferenceSearcher, ReferenceSearchStrategy } from './references'
+import { createReferenceSearcher, ReferenceSearchStrategy } from './references'
 import { OnlyData } from './utils/OnlyData'
 
 
-export function getCacheDirectory() {
-    return process.env.NPM_CACHE || 'cache'
-}
-
+/** This is the starting point and configuration place for the downstream repository miner. */
 export class Dowdep {
-    constructor(init: Partial<OnlyData<Dowdep>>) {
+    constructor(init: Partial<OnlyData<Dowdep>> = {}) {
         Object.assign(this, init)
     }
 
@@ -40,23 +37,30 @@ export class Dowdep {
             ? <['npm', 'sourcegraph']>['npm', 'sourcegraph']
             : this.dependencySearchStrategies
 
-        return strategies.map(strategy => createDependencySearcher(strategy, $package, {
+        return strategies.map(strategy => createDependencySearcher($package, strategy, {
             limit: this.dependencyLimit ? Math.ceil(this.dependencyLimit / strategies.length) : this.dependencyLimit
         }))
     }
 
     createReferenceSearcher(dependency: Dependency, $package: Package) {
-        // TODO: Do we still need $package param?
-        return PackageReferenceSearcher.create($package, dependency, this.referenceSearchStrategy)
+        return createReferenceSearcher($package, dependency, this.referenceSearchStrategy)
     }
 }
 
+/** Wraps an existing physical or virtual filesystem. In preparation for supporting VS Code's virtual filesystem for github.dev. */
 export interface FileSystem {
     exists(path: string): Promise<boolean>
     join(...parts: string[]): string
 }
 
 export const defaultFileSystem: FileSystem = {
-    exists: pathExists,
+    exists: async (path: string) => {
+        try {
+            await fsPromises.access(path)
+            return true
+        } catch {
+            return false
+        }
+    },
     join: path.join
 }

### 2021-10-12 packages/core/src/externalModules.ts

@@ -1,0 +1,19 @@
+import type { Import, Options } from "parse-imports"
+
+
+/**
+ * Stores external modules that have been loaded in a non-standard, weird way.
+ *
+ * The existence of this is a large workaround. Some components of our toolchain, including oclif and jest, do not support dynamic importing of pure ES modules correctly. See `loadExternalModules()` in `index.ts`. As the technique used there cannot be applied from submodules, imported modules are stored in this file.
+ */
+const modules = {
+    /** Escape RegExp special characters */
+    escapeRegexp: <(regex: string) => string><unknown>undefined,
+    /** A blazing fast ES module imports parser. */
+    parseImports: <(
+        code: string,
+        options?: Options
+    ) => Promise<Iterable<Import>>><unknown>undefined
+}
+
+export default modules

### 2021-10-12 packages/core/src/packages.ts

@@ -3,10 +3,11 @@ import mapManyAsync from '@async-generators/map-many'
 
 import { Dowdep } from './dowdep'
 import { Dependency, DependencyUpdateCallback, DependencyUpdateOptions } from './dependencies'
-import { Reference } from '.'
+import { Reference } from './references'
 import mapUnorderedAsync from './utils/mapUnorderedAsync'
 
 
+/** A package whose downstream dependencies will be analyzed. */
 export class Package {
     constructor(
         public name: string,
@@ -25,6 +26,7 @@ export class Package {
         return this.dependencies.flatMap(depedendency => depedendency.references)
     }
 
+    /** Fetch and update dependencies for the package asynchronously. After every update step, `updateCallback` is invoked. */
     async updateDependencies(dowdep: Dowdep, options: Partial<DependencyUpdateOptions> = {}, updateCallback?: DependencyUpdateCallback) {
         const searchers = dowdep.createDependencySearchers(this)
 
@@ -39,6 +41,5 @@ export class Package {
             }
             await dependency.update(dowdep, options, updateCallback)
         }))
-        // TODO: Dependency needs a "state" variable for proper asynchronous state checking
     }
 }

### 2021-10-12 packages/core/src/references.ts

@@ -1,920 +1,0 @@
-import { strict as assert } from 'assert'
-import { Dirent, promises as fsPromises } from 'fs'
-import fs from 'fs'
-import glob from 'glob-promise'
-import asyncIteratorToArray from 'it-all'
-import LinesAndColumns from 'lines-and-columns'
-import _ from 'lodash'
-import type { Import, Options } from 'parse-imports'
-import path from 'path'
-import pathIsInside from 'path-is-inside'
-import pkgDir from 'pkg-dir'
-import tryCatch from 'try-catch'
-import ts from 'typescript'
-
-import { Dependency } from './dependencies'
-import { Package } from './packages'
-import { OnlyData } from './utils/OnlyData'
-import rex from './utils/rex'
-
-
-export class FilePosition {
-    constructor(init: OnlyData<FilePosition>) {
-        Object.assign(this, init)
-    }
-
-    row!: number
-    column?: number
-
-    toLodashPrimitive() {
-        return [this.row, this.column]
-    }
-
-    toPrimitive() {
-        return this.toString()
-    }
-
-    toString() {
-        return this.column ? `${this.row}:${this.column}` : `${this.row}`
-    }
-}
-
-export type FilePositionPrimitive = ReturnType<typeof FilePosition.prototype.toPrimitive>
-export type FilePositionLodashPrimitive = ReturnType<typeof FilePosition.prototype.toLodashPrimitive>
-
-export interface Location {
-    file: string
-    position: FilePosition,
-    memberPath?: string[] | null | undefined
-
-    toString(): string
-}
-
-export class ReferenceLocation implements Location {
-    constructor(init: OnlyData<ReferenceLocation>) {
-        Object.assign(this, init)
-    }
-
-    file!: string
-    position!: FilePosition
-    memberPath?: string[]
-
-    keyEquals(location: Location) {
-        return this.file === location.file
-            && this.position.toPrimitive() === location.position.toPrimitive()
-    }
-
-    toString() {
-        return `${this.file}:${this.position}`
-    }
-}
-
-type DeclarationPath = string[] | null | undefined
-
-export class DeclarationLocation implements Location {
-    constructor(init: OnlyData<DeclarationLocation>) {
-        Object.assign(this, init)
-    }
-
-    file!: string
-    position!: FilePosition
-    /**
-     * - `undefined`: is default import
-     * - `null`: imports root
-     */
-    memberPath!: DeclarationPath
-    memberName!: string
-
[…]

### 2021-10-12 packages/core/src/utils/fs.exists.ts

@@ -1,0 +1,20 @@
+import { promises as fsPromises } from 'fs'
+
+
+/**
+ * Replacement for deprecated `fs.promises.exists`.
+ *
+ * CREDITS: https://stackoverflow.com/a/39876121/13994294
+ */
+export default async function fileExists(filename: string) {
+    try {
+        await fsPromises.stat(filename)
+        return true
+    } catch (err) {
+        if ((<NodeJS.ErrnoException>err).code === 'ENOENT') {
+            return false
+        } else {
+            throw err
+        }
+    }
+}

### 2021-10-12 packages/core/test/@types/read-package-json.d.ts

@@ -2,8 +2,7 @@ declare module 'read-package-json' {
     import { FullMetadata as PackageJson } from 'package-json'
 
     type CallbackFunction = (err: Error, data: PackageJson) => void
-    // eslint-disable-next-line @typescript-eslint/no-explicit-any
-    type LoggingFunction = (message?: any, ...optionalParams: any[]) => void
+    type LoggingFunction = (message?: unknown, ...optionalParams: unknown[]) => void
 
     /** The thing npm uses to read package.json files with semantics and defaults and validation and stuff. */
     export default function readJson(file: string, log_: LoggingFunction, strict_: boolean, cb_: CallbackFunction): void

### 2021-10-12 packages/core/test/npm-dependencies.test.ts

@@ -1,19 +1,6 @@
-import assert from 'assert'
-import { FullMetadata as PackageJson } from 'package-json'
-import * as path from 'path'
-import readPackageJsonCallback from 'read-package-json'
-import rimRaf from 'rimraf'
-import { promisify } from 'util'
-import { Package } from '../src'
-import { NpmDependency } from '../src/dependencies/npm'
-
-import { Dowdep, getCacheDirectory } from '../src'
-
-const readPackageJson = <(file: string) => Promise<PackageJson>><unknown>  // BUG in type definitions: https://github.com/DefinitelyTyped/DefinitelyTyped/issues/33340
-    promisify(readPackageJsonCallback)
+import { Dowdep, Package } from '../src'
 
 
-// TODO: Extract all fixtures into separate files?
 describe('updateDependencies', () => {
     it.each`
         packageName     | limit  | downloadGitHubData  | timeoutSecs  | nonGitHubThreshold
@@ -56,30 +43,4 @@ describe('updateDependencies', () => {
             }
         }
     }, 60000)
-})
-
-describe('updateSource', () => {
-    it.each`
-        packageName     | version     | tarballUrl
-        ${'gl-matrix'}  | ${'3.3.0'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.3.0.tgz'}
-        ${'gl-matrix'}  | ${'3.2.1'}  | ${'https://registry.npmjs.org/gl-matrix/-/gl-matrix-3.2.1.tgz'}
-    `("should fetch the package '$packageName' with the right version '$version'", async (
-        { packageName, version, tarballUrl }: {
-            packageName: string, version: string, tarballUrl: string
-        }) => {
-        jest.setTimeout(5000)
-        assert(process.env.NPM_CACHE)
-        await (promisify(rimRaf))(process.env.NPM_CACHE)
-
-        const dep = new NpmDependency(packageName, <Package><unknown>undefined)
-        dep.tarballUrl = tarballUrl
-
-        const dowdep = new Dowdep({
-            sourceCacheDirectory: getCacheDirectory()
-        })
-        await dep.updateSource(dowdep)
-
-        const data = await readPackageJson(path.join(<string>process.env.NPM_CACHE, packageName, 'package.json'))
-        expect(data.version).toBe(version)
-    })
 })

### 2021-10-12 packages/core/test/references.test.ts

@@ -1,13 +1,14 @@
-import asyncIteratorToArray from 'it-all'
+import itAll from 'it-all'
 import _ from 'lodash'
 import { jsonc as json } from 'jsonc'
 
 import { Package } from '../src/packages'
-import { ReferenceSearcher, ReferenceKind } from '../src/references'
+import { ReferenceCollector, ReferenceKind, ReferenceSearchStrategy } from '../src/references'
 import ifCurtailed from '../src/utils/if-curtailed'
 import { lodashClassifyNested } from '../src/utils/lodash-classify'
 import { getSourceDirectory } from './_utils/sourceDirectory'
 import { printDiff } from './_utils/printDiff'
+import { loadExternalModules } from '../src'
 
 
 const SOURCE_DIRECTORY = getSourceDirectory(__filename)
@@ -32,19 +33,21 @@ const expectedTypeReferences = <References>json.readSync(`${SOURCE_DIRECTORY}/ex
 describe('ReferenceSearcher', () => {
     it.each(_.flatMap(
         Object.entries({'heuristic': expectedHeuristicReferences, 'types': expectedTypeReferences}),
-        ([packageReferenceSearcher, allExpectedReferences]) => _.map(
+        ([strategy, allExpectedReferences]) => _.map(
             Object.entries(allExpectedReferences),
-            ([packageName, expectedReferences]) => ({ packageReferenceSearcher, packageName, expectedReferences }))
+            ([packageName, expectedReferences]) => ({ strategy: <ReferenceSearchStrategy>strategy, packageName, expectedReferences }))
     ))("should find relevant references for %s", async (
-        { packageReferenceSearcher, packageName, expectedReferences }) => {
+        { strategy, packageName, expectedReferences }) => {
+        await loadExternalModules()
+
         const $package = new Package(
             packageName,
             `${SOURCE_DIRECTORY}/examples/packages/${packageName}`
         )
-        const searcher = new ReferenceSearcher($package, `${SOURCE_DIRECTORY}/examples/dependents`, packageReferenceSearcher)
-        const references = await asyncIteratorToArray(searcher.searchReferences(undefined, '*'))
+        const collector = new ReferenceCollector($package, `${SOURCE_DIRECTORY}/examples/dependents`, strategy)
+        const references = await itAll(collector.searchReferences(undefined, '*'))
 
-        /** Since null and undefined are invalid keys in JS objects, we stringify them for compatibility with lodash. See Reference.memberName. */
[…]

### 2021-10-12 packages/core/test/utils/lodash-classify.test.ts

@@ -1,5 +1,6 @@
 import { lodashClassify, lodashClassifyNested } from '../../src/utils/lodash-classify'
 
+
 describe('lodashClassify', () => {
     it("should work", () => {
         const input = {

### 2021-10-12 packages/vscode-extension/src/codeLens.ts

@@ -5,7 +5,7 @@ import { Extension, positionToVscode } from './extension'
 import * as mapUtils from './utils/node/mapUtils'
 
 
-type UriPrimitive = string
+type UriPrimitive = ReturnType<vscode.Uri['toString']>
 
 export class DeclarationCodeLensProvider implements vscode.CodeLensProvider {
     constructor(

### 2021-10-12 packages/vscode-extension/src/extension.ts

@@ -1,4 +1,4 @@
-import { DeclarationLocation, Dependency, Dowdep, FilePosition, Package, Reference, ReferenceSearchStrategy } from 'dowdep'
+import { DeclarationLocation, Dependency, Dowdep, FilePosition, loadExternalModules, Package, Reference, ReferenceSearchStrategy } from 'dowdep'
 import _ from 'lodash'
 import filterAsync from 'node-filter-async'
 import normalizePackageData from 'normalize-package-data'
@@ -14,7 +14,8 @@ import * as iterUtils from './utils/node/iterUtils'
 import { escapeMarkdown } from './utils/vscode/markdown'
 
 
-let extension: Extension
+let extension: Extension | undefined = undefined
+export { extension }
 
 type DependencyLike = Dependency | readonly Dependency[] | PackageLike
 type PackageLike = Package | readonly Package[]
@@ -22,28 +23,31 @@ type PackageLike = Package | readonly Package[]
 /**
  * This method is called on the first activation event.
  */
-export function activate(context: vscode.ExtensionContext) {
-    console.log("The extension \"dowdep\" is now active.")
+export async function activate(context: vscode.ExtensionContext) {
+    await loadExternalModules()
 
     extension = new Extension(context)
-
     extension.activate()
+
+    console.log("The extension \"dowdep\" is now active.")
+    return extension
 }
 
 /**
  * This method is called when the extension is deactivated.
  */
 export function deactivate() {
-    extension.release()
+    extension?.release()
 }
 
+/** The god class of the extension that connects to a {@link Dowdep} instance. */
 export class Extension {
+    extension: vscode.Extension<Extension> // TODO: Name clash!
     packages: Package[] = []
-    protected extension: vscode.Extension<unknown> // TODO: Name clash!
-    protected dowdep: Dowdep
-    protected dependenciesProvider: DependenciesProvider
-    protected referencesProvider: ReferencesProvider
-    protected codeLensProvider: DeclarationCodeLensProvider
+    dowdep: Dowdep
+    dependenciesProvider: DependenciesProvider
+    referencesProvider: ReferencesProvider
+    codeLensProvider: DeclarationCodeLensProvider
 
     private dependencyLimitIncrement = 0
     private get modelObservers() {
@@ -61,7 +65,7 @@ export class Extension {
 
         this.dowdep = new Dowdep({
             //fs: vscode.workspace.fs
[…]

### 2021-10-12 packages/vscode-extension/src/references.ts

@@ -96,6 +96,7 @@ class ReferencesPackageItem extends PackageItem<
     }
 }
 
+/** A composite item for a file path inside a {@link Package}. */
 class PackageFileNodeItem extends ReferenceFileNodeItem<
     PackageFileNodeItem,
     PackageMemberNodeItem,
@@ -149,11 +150,12 @@ class PackageFileNodeItem extends ReferenceFileNodeItem<
         await vscode.commands.executeCommand(
             'dowdep.openPackageFileOrFolder',
             this.$package,
-            this.path.join('/')
+            this.path.join(PackageFileNodeItem.pathSeparator)
         )
     }
 }
 
+/** A composite item for a member path inside a {@link Package} file. */
 class PackageMemberNodeItem extends HierarchyNodeItem<
     string | Dependency,
     Reference,

### 2021-10-12 packages/vscode-extension/src/utils/node/mapUtils.ts

@@ -1,3 +1,7 @@
+/** Get the value from the specified map at the specified key, or if the key is not present in the map, create it and with the result from evaluating the specified value factory.
+ *
+ * @returns The value at the key in the map (after creating it, if necessary).
+ */
 export function getOrSet<TKey, TValue>(map: Map<TKey, TValue>, key: TKey, valueFactory: (key: TKey) => TValue): TValue {
     if (map.has(key)) {
         return <TValue>map.get(key)

### 2021-10-12 packages/vscode-extension/src/utils/vscode/hierarchy.ts

@@ -7,6 +7,7 @@ import * as mapUtils from '../node/mapUtils'
 import { Synchronizer } from './synchronizer'
 
 
+/** A specialization of {@link vscode.HierarchyDataProvider} that delegates control of the tree structure to a {@link HierarchyItem}. */
 export abstract class HierarchyDataProvider<
     TRootItem extends RefreshableHierarchyItem
 > implements vscode.TreeDataProvider<HierarchyItem> {
@@ -73,6 +74,7 @@ export abstract class HierarchyDataProvider<
     }
 }
 
+/** A specialization {@link vscode.TreeItem} that implements the composite pattern. */
 export abstract class HierarchyItem extends vscode.TreeItem {
     constructor(
         public parent: HierarchyItem | null,
@@ -137,6 +139,7 @@ export abstract class RefreshableHierarchyItem extends HierarchyItem {
     }
 }
 
+/** A {@link RefreshableHierarchyItem} that caches and encapsulates child management and provides an abstract protocol for adding new items. */
 export abstract class SynchronizableHierarchyItem<
     TKey,
     TItem extends RefreshableHierarchyItem
@@ -182,6 +185,8 @@ export type HierarchyNodeItemOptions = {
     showCountInDescription: boolean
 }
 
+/** A {@link RefreshableHierarchyItem} that arranges a composite structure automatically into hierarchical items by paths.
+*/
 export abstract class HierarchyNodeItem<
     TPathSegment,
     TLeafKey,
@@ -205,6 +210,7 @@ export abstract class HierarchyNodeItem<
     public allLeafs: readonly TLeafKey[] = []
     /** If set, will be used to sort all complex item keys. */
     protected pathSegmentSorters?: ReadonlyArray<_.Many<_.ListIteratee<TPathSegment>>>
+    /** If set, will be used to sort all leaf keys. */
     protected leafSorters?: ReadonlyArray<_.Many<_.ListIteratee<TLeafKey>>>
     private complexBuckets: Map<TPathSegment, TLeafKey[]>
     protected showCountInDescription = false

### 2021-10-12 packages/vscode-extension/src/views.ts

@@ -1,6 +1,7 @@
 import { strict as assert } from 'assert'
 import { Dependency, Package, Reference } from 'dowdep'
 import _ from 'lodash'
+import path from 'path'
 import truncate from 'truncate'
 import * as vscode from 'vscode'
 
@@ -27,6 +28,11 @@ export class HierarchyProvider<TRootItem extends RefreshableHierarchyItem> exten
     }
 }
 
+/**
+ * A pseudo-item that represents the root of a tree view of package items.
+ *
+ * This item is never displayed inside a tree view but only used to control child items.
+ */
 export abstract class PackagesItem<TPackageItem extends RefreshableHierarchyItem> extends SynchronizableHierarchyItem<Package, TPackageItem> {
     constructor(
         protected extension: Extension
@@ -41,6 +47,7 @@ export abstract class PackagesItem<TPackageItem extends RefreshableHierarchyItem
     }
 }
 
+/** An item for a {@link Package}. */
 export abstract class PackageItem<TItem extends RefreshableHierarchyItem> extends SynchronizableHierarchyItem<Dependency, TItem> {
     constructor(
         public $package: Package,
@@ -68,6 +75,7 @@ export abstract class PackageItem<TItem extends RefreshableHierarchyItem> extend
     }
 }
 
+/** A composite item for a {@link Dependency}. */
 export abstract class DependencyItem<
     TDependencyItem extends DependencyItem<TDependencyItem, TReferenceItem>,
     TReferenceItem extends RefreshableHierarchyItem
@@ -113,7 +121,6 @@ export abstract class DependencyItem<
     }
 
     async open() {
-        // TODO: Do not suppress expansion of item on click - expand it manually
         await vscode.commands.executeCommand('dowdep.openDependency', this.dependency)
     }
 
@@ -153,15 +160,18 @@ export abstract class DependencyItem<
             yield md`---`
             yield
             yield md`GitHub: ${
-                [
-                    ["stars", this.dependency.githubRepository.stargazerCount],
-                    ["forks", this.dependency.githubRepository.forkCount]
-                ].map(([label, count]) => md`${count} ${label}`.value).join(" ⸱ ")
+                (<[[string, string], number][]>[
+                    [["star", "stars"], this.dependency.githubRepository.stargazerCount],
+                    [["fork", "forks"], this.dependency.githubRepository.forkCount]
[…]

### 2021-10-12 packages/vscode-extension/test/suite/index.ts

@@ -2,11 +2,13 @@ import path from 'path'
 import Mocha from 'mocha'
 import glob from 'glob'
 
+
 export function run(): Promise<void> {
     // Create the mocha test
     const mocha = new Mocha({
         ui: 'tdd',
-        color: true
+        color: true,
+        timeout: 600_000
     })
 
     const testsRoot = path.resolve(__dirname, '..')

### 2021-10-12 docs/paper/sections/1_introduction.tex

@@
 	\item mine package usage samples from these dependencies by using a type analyzer,
-	and \item aggregate and present these usage data to the user.
+	and \item aggregate and present these usage data to the package developer.
 \end{enumerate*}

### 2021-10-12 docs/paper/sections/2_related_work.tex

@@
 Usually, this is accomplished by analyzing the control flow of a program and inferring the possible types of every variable or function.
-Another useful data structure for enhancing type information are \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
+Another useful data structure for enhancing type information is \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
 While the latter method has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.

### 2021-10-12 docs/paper/sections/3_approach.tex

@@
 
-To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate \emph{abstract syntax forest}F (ASF, i.e., a set of ASTs).
+To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate \emph{abstract syntax forest} (ASF, i.e., a set of ASTs).
 

### 2021-10-12 docs/paper/sections/5_evaluation.tex

@@
 As the dependencies are collected in excerpts from two very large datasets, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
-Nevertheless, there are some causes that will prevent a dependency from being found by our methods:
+Nevertheless, some causes will prevent a dependency from being found by our methods:
 
@@
 			\footnotesize
-			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \SI{2.80}{\giga\hertz}, internet downspeed ~\SI{1.8}{\giga\bit/\second}.
+			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \SI{2.80}{\giga\hertz}, internet down speed ~\SI{1.8}{\giga\bit/\second}.
 			\item[\alphtnotetext{2}] Effective speed while downloading multiple packages in parallel.
@@
 
-Additionally, some npm packages contain minified sources only that are still searchable valid code but can provide a significantly reduced readability.
+Additionally, some npm packages contain minified sources only that are still searchable valid code but can provide significantly reduced readability.
 
@@
 Also, the dependency artifacts have no strong relationship to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
-The code annotations are displayed close to the original source code with a small spatial distance.
+The code annotations are displayed close to the package source code with a small spatial distance.
 

### 2021-10-12 docs/paper/sections/6_conclusion.tex

@@
 
-Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent, and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
+Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
 Nevertheless, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.

### 2021-10-12 docs/paper/sections/4_implementation.tex

@@
 	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
-	\item The \emph{CodeLens integration} provides quick access to a slice usage samples and is attached to the definition of each package member in the source code editor.
+	\item The \emph{CodeLens integration} provides quick access to a slice of usage samples and is attached to the definition of each package member in the source code editor.
 \end{enumerate}

### 2021-10-12 packages/cli/src/commands/list.ts
Revise documentation (#279)

@@ -21,7 +21,7 @@ export default class List extends DowdepCommand {
         }),
         downloadGitHubData: flags.boolean({
             name: 'download-github-metadata',
-            description: "download additional metadata from GitHubn (enabled by default, prepend no to disable)",
+            description: "[default: yes] download additional metadata from GitHub",
             default: true,
             allowNo: true
         })

### 2021-10-12 docs/paper/sections/5_evaluation.tex
Try to shorten paper just a little bit more

@@
 If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
-Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for a small number of repositories only.
+Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for few repositories only.
 

### 2021-10-12 docs/paper/sections/6_conclusion.tex
Try to shorten paper just a little bit more

@@
 We have identified two kinds of rich data sources for collecting downstream dependencies efficiently: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
-We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis beforehand.
-We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the Visual Studio Code IDE.
+We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis before.
+We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the VS Code IDE.
 
@@
 The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
-There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package as per LCOM \citep{chidamber1994metrics}), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.
+There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package as per LCOM \citep{chidamber1994metrics}), or that could be attributed to ranges of packages for comparing them concerning their dependency-based cohesion or their spreading in an ecosystem.
 

### 2022-04-29 docs/paper/paper.tex
Restructure paper: extract split up approach, merge implementation
paper: minor phrasing and typesetting improvements
Refactor and fix figure and footnote positioning
Try to fix paper template on CI, second attempt
Supersedes 99750f408845efee3049273a7f16a9deaca543b8.
Fix footnote positioning; use ACM colors
Add evaluation
Revise paper and apply feedback by @scheibel
- Restructure sections
- Shorten things
- Rephrasing
- Improve typesetting
Add paper versions as published in ENASE
Co-authored-by: Willy Scheibel <willy.scheibel@hpi.de>
Co-authored-by: cgcostume <cgdaniel@outlook.com>

@@
-\input{template/acm}
-\input{template/bibtex}
-\input{template/hyphenation}
-\input{template/packages}
-\input{template/commands}
+\documentclass[a4paper,twoside]{article}
+
+\usepackage[T1]{fontenc}
+\usepackage{epsfig}
+\usepackage{subcaption}
+\usepackage{calc}
+\usepackage{amssymb}
+\usepackage{amstext}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{multicol}
+\usepackage{pslatex}
+\usepackage{apalike}
+\usepackage[bottom,hang,flushmargin]{footmisc} % added hang,flushmargin
+\usepackage{csquotes}
+
+% OWN PACKAGES
+\usepackage{microtype}
+\usepackage{numprint}
+\usepackage{tabularx}
+\usepackage{balance}
+
+\usepackage[table]{xcolor}
+\usepackage{calc}
+\usepackage{tikz}
+\usetikzlibrary{calc,positioning,spy,shapes}
+
+\tikzset{thick/.style = {line width = 1.0pt}}
+
+\newlength{\pfull}  \setlength{\pfull}  {2mm}
+\newlength{\phalf}  \setlength{\phalf}  {0.5\pfull}
+
+\newlength{\lwffp}   \setlength{\lwffp}   {0.5000\dimexpr(\linewidth-1.0\pfull)}
+\newlength{\lwfffp}  \setlength{\lwfffp}  {0.3333\dimexpr(\linewidth-2.0\pfull)}
+\newlength{\lwffffp} \setlength{\lwffffp} {0.2500\dimexpr(\linewidth-3.0\pfull)}
+\newlength{\lwfffffp}\setlength{\lwfffffp}{0.2000\dimexpr(\linewidth-4.0\pfull)}
+
+\newlength{\twffp}   \setlength{\twffp}   {0.5000\dimexpr(\textwidth-1.0\pfull)}
+\newlength{\twfffp}  \setlength{\twfffp}  {0.3333\dimexpr(\textwidth-2.0\pfull)}
+\newlength{\twffffp} \setlength{\twffffp} {0.2500\dimexpr(\textwidth-3.0\pfull)}
+\newlength{\twfffffp}\setlength{\twfffffp}{0.2000\dimexpr(\textwidth-4.0\pfull)}
+
+\tikzstyle{labelStyle} = [ shape = rectangle, font = \scriptsize, text depth = 0, fill = white, inner sep = 4pt ]
+\tikzstyle{labelN}  = [ labelStyle, anchor = north ]
+\tikzstyle{labelNW} = [ labelStyle, anchor = north west ]
+\tikzstyle{labelNE} = [ labelStyle, anchor = north east ]
+\tikzstyle{labelS}  = [ labelStyle, anchor = south ]
+\tikzstyle{labelSW} = [ labelStyle, anchor = south west ]
+\tikzstyle{labelSE} = [ labelStyle, anchor = south east ]
+
+\tikzstyle{figRC} = [shape = rectangle, rounded corners = 2mm, clip] % figure with Rounded Corners
+\tikzstyle{spyRC} = [shape = rectangle, rounded corners = 2mm, %
+    white, connect spies, every spy on node/.append style = {thick}] % spy with Rounded Corners
+\tikzstyle{figNS} = [inner sep = 0pt, outer sep = 0pt] % figure with No Separators
+
+\newcommand*\rot{\rotatebox{90}}
+\newcommand{\rott}[2]{\multicolumn{1}{#1}{\rot{#2}}}
+
+\usepackage[hidelinks]{hyperref}
+
+% Define starred commands
+\usepackage{xparse}
+
+% Enumerations
+\usepackage[inline]{enumitem}
+
+% Draw figures
+% \usepackage{tikz}
+% \includegraphs for .tikz files
+\usepackage{tikzscale}
+
+% Lay out multiple figures
+\usepackage{subcaption}
+
+% Extended control of figure positioning
+\usepackage{dblfloatfix}
+
+\usepackage{float}
+\newfloat{lstfloat}{htbp}{lop}
+\floatname{lstfloat}{Listing}
+\def\lstfloatautorefname{Listing} % needed for hyperref/auroref
+
+% Algorithms
+\usepackage[noend,noline,boxed]{algorithm2e}
+\SetAlCapSkip{1em}
+% Python style
+\DontPrintSemicolon
+\SetStartEndCondition{ }{}{}%
+\SetKwIF{If}{ElseIf}{Else}{if}{:}{else if}{else}{end if}%
+\SetKwFor{For}{for}{:}{next}%
+\SetKw{kwYield}{yield}
+
+% Source code listings
+\usepackage{listings}
+\usepackage{lstset-typescript}
+
+% Underlined text with linebreaks
+\usepackage[normalem]{ulem}
+
+% SI units
+\usepackage{siunitx}
+\sisetup{input-ignore={,},input-decimal-markers={.}}  % allow for manual thousands separators in numbers
+\sisetup{group-separator = {,}}
+\DeclareSIUnit\bit{bit}
+\DeclareSIUnit\byte{B}
+
+\usepackage{xcolor}
+
+% Convenient references (needs to be loaded after algorithms)
+\usepackage[nameinlink]{cleveref}
+
+% Tables
+\usepackage{booktabs}
+\usepackage{multirow}
+
+\usepackage{makecell}
+\renewcommand\theadalign{bc}
+
+\usepackage{threeparttable}
+
+% Bar charts
+\usepackage{bchart}
+
+\definecolor{plots-1}{RGB}{228,26,28}
+\definecolor{plots-2}{RGB}{55,126,184}
+
+\usepackage{tikz}
+\usetikzlibrary{calc,fit,backgrounds,positioning,shapes,snakes,arrows.meta,spy,shapes.multipart,patterns}
+
+\usepackage{pgfplots}
+\usepackage{pgfplotstable}
+\usepackage{pgfplotstablefilter}
+\pgfplotsset{compat=newest}% es muss mindestens Version 1.8 installiert sein
+\usepgfplotslibrary{statistics}
+
+% END OWN PACKAGES
+
+\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.
+
+% Semantic markup
+\newcommand\caps[1]{%
+	\textsc{#1}%
+}
+\NewDocumentCommand\mycode{sm}{%
+    \IfBooleanTF#1%
+        {{\small\texttt{#2}}}% If a star is seen
+        {{\small\texttt{\detokenize{#2}}}}%     If no star is seen
+}
+
+% Semantic mathmode markup
+\newcommand{\mli}[1]{\mathit{#1}}
+\newcommand{\mtx}[1]{\text{#1}}
+
+% Todo comments
+\newcommand\TODO[1]{%
+    {\leavevmode\bfseries\color{red}#1}%
+}
+
+% bchart legends
+% CREDITS: https://tex.stackexchange.com/a/379816/221054
+\usetikzlibrary{fit}
+
+\makeatletter
+\newdimen\legendxshift
+\newdimen\legendyshift
+\newcount\legendlines
+% distance of frame to legend lines
+\newcommand{\bclldist}{1mm}
+\newcommand{\bclegend}[3][10mm]{%
+    % initialize
+    \legendxshift=0pt\relax
+    \legendyshift=0pt\relax
+    \xdef\legendnodes{}%
+    % get width of longest text and number of lines
+    \foreach \lcolor/\ltext [count=\ll from 1] in {#3}%
+        {\global\legendlines\ll\pgftext{\setbox0\hbox{\bcfontstyle\ltext}\ifdim\wd0>\legendxshift\global\legendxshift\wd0\fi}}%
+    % calculate xshift for legend; \bcwidth: from bchart package; \bclldist: from node frame, inner sep=\bclldist (see below)
+    % \@tempdima: half width of bar; 0.72em: inner sep from text nodes with some manual adjustment
+    \@tempdima#1\@tempdima0.5\@tempdima
+    \pgftext{\bcfontstyle\global\legendxshift\dimexpr\bcwidth-\legendxshift-\bclldist-\@tempdima-0.72em}
+    % calculate yshift; 5mm: heigt of bar
+    \legendyshift\dimexpr5mm+#2\relax
+    \legendyshift\legendlines\legendyshift
+    % \bcpos-2.5mm: from bchart package; \bclldist: from node frame, inner sep=\bclldist (see below)
+    \global\legendyshift\dimexpr\bcpos-2.5mm+\bclldist+\legendyshift
+    % draw the legend
+    \begin{scope}[shift={(\legendxshift,\legendyshift)}]
+    \coordinate (lp) at (0,0);
+    \foreach \lcolor/\ltext [count=\ll from 1] in {#3}%
+    {
+        \node[anchor=north, minimum width=#1, minimum height=5mm,fill=\lcolor] (lb\ll) at (lp) {};
+        \node[anchor=west] (l\ll) at (lb\ll.east) {\bcfontstyle\ltext};
+        \coordinate (lp) at ($(lp)-(0,5mm+#2)$);
+        \xdef\legendnodes{\legendnodes (lb\ll)(l\ll)}
+    }
+    % draw the frame
+    \node[draw, inner sep=\bclldist,fit=\legendnodes] (frame) {};
+    \end{scope}
+}
+\makeatother
+
+% Properly spaces tnotes for threeparttable
+% CREDITS: https://tex.stackexchange.com/a/108640/221054
+% This is like `\tnote`, but uses the space of the argument
+\newcommand\stnote[1]{\textsuperscript{\TPTtagStyle{#1}}}
+
+% Alpha numbers for threeparttable tnotes
+\makeatletter
+\newcommand{\alphtnotetext}[1]{\itshape \@alph{#1}}
+\makeatother
+\newcommand{\alphtnote}[1]{\stnote{\alphtnotetext{#1}}}
+
+\definecolor[named]{ACMBlue}{cmyk}{1,0.1,0,0.1}
+\definecolor[named]{ACMYellow}{cmyk}{0,0.16,1,0}
+\definecolor[named]{ACMOrange}{cmyk}{0,0.42,1,0.01}
+\definecolor[named]{ACMRed}{cmyk}{0,0.90,0.86,0}
+\definecolor[named]{ACMLightBlue}{cmyk}{0.49,0.01,0,0}
+\definecolor[named]{ACMGreen}{cmyk}{0.20,0,1,0.19}
+\definecolor[named]{ACMPurple}{cmyk}{0.55,1,0,0.15}
+\definecolor[named]{ACMDarkBlue}{cmyk}{1,0.58,0,0.21}
+
+\colorlet{paperbackground}{white}
+\colorlet{accent1}{ACMBlue}
+\colorlet{accent2}{ACMYellow}
+\colorlet{accent3}{ACMOrange}
+\colorlet{accent4}{ACMRed}
+\colorlet{accent5}{ACMLightBlue}
+\colorlet{accent6}{ACMGreen}
+\colorlet{accent7}{ACMPurple}
+\colorlet{accent8}{ACMDarkBlue}
+
+\colorlet{bchart.accent1}{accent1!70!paperbackground}
+\colorlet{bchart.accent2}{accent2!70!paperbackground}
+\colorlet{bchart.accent3}{accent3!70!paperbackground}
+\colorlet{bchart.accent4}{accent4!70!paperbackground}
+\colorlet{bchart.accent5}{accent5!70!paperbackground}
+\colorlet{bchart.accent6}{accent6!70!paperbackground}
+\colorlet{bchart.accent7}{accent7!70!paperbackground}
+\colorlet{bchart.accent7}{accent7!70!paperbackground}
+\colorlet{bchart.accent8}{accent8!70!paperbackground}
+
+\lstset{frame=none,
+	showstringspaces=false,
+	columns=flexible,
+	basicstyle={\small\ttfamily},
+	numbers=none,
+	keywordstyle=\textbf,
+	stringstyle=\color{blue},
+	breaklines=true,
+	breakatwhitespace=true,
+	tabsize=3
+}
+
+\colorlet{punct}{black}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+\lstdefinelanguage{json}{
+    frame=lines,
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
+
+\lstdefinelanguage{sourcegraph}{
+	alsodigit={-},
+	morekeywords={
+		count,
+		file,
+		-file,
+		select
+	},
+	literate=*{\\.}{{{\color{accent4}{\textbackslash.}}}}{1},
+	moredelim=[is][\textbf]{\ }{:},
+	% placeholders
+	moredelim=[s][\color{accent1}\itshape]{<}{>},  % TODO: italic does not work
+	morestring=[b]
+}
+
+% Left-align footnotes in minipages - this reverts a part of the acm style
+% CREDITS: https://github.com/borisveytsman/acmart/issues/449#issuecomment-932653376
+\makeatletter
+\long\def\@mpfootnotetext#1{%
+\global\setbox\@mpfootins\vbox{%
+  \unvbox\@mpfootins
+  \reset@font\footnotesize
+  \hsize\columnwidth
+  \@parboxrestore
+  \protected@edef\@currentlabel
+	   {\csname p@mpfootnote\endcsname\@thefnmark}%
+  \color@begingroup%\centering - commented out centering footnotes
+	\@makefntext{%
+	  \rule\z@\footnotesep\ignorespaces#1\@finalstrut\strutbox}%
+  \color@endgroup}}
+\makeatother
+
+\newcommand\footnoteseparator{\textsuperscript{,}}
+
+\crefname{requirement}{requirement}{requirements}
+\crefname{question}{question}{questions}
 
@@
 
-	\input{title}
+\title{Augmenting Library Development by Mining Usage Data from~Downstream~Dependencies}
 
-	\input{sections/0_abstract}
-	\keywords{mining software repositories, ecosystem call graphs, API usage, type analyzer, npm}
+\author{\authorname{Christoph Thiede, Willy Scheibel, Daniel Limberger, and J{\"u}rgen D{\"o}llner}
+\affiliation{Hasso Plattner Institute, Digital Engineering Faculty, University of Potsdam}}
 
-	\maketitle
+\keywords{Mining Software Repositories, Downstream Dependencies, API Usage.}
 
-	\input{sections/1_introduction}
-	\input{sections/2_related_work}
-	\input{sections/3_approach}
-	\input{sections/4_data_collection}
-	\input{sections/5_usage_mining}
-	\input{sections/6_presentation}
-	\input{sections/7_evaluation}
-	\input{sections/8_conclusion}
+\inofficialcopyrightnotice{Author's Version.
+This paper has been published in the Proceedings of the 17th International Conference on Evaluation of Novel Approaches to Software Engineering -- ENASE, 221--232, 2022, and is accessible on \textsc{SciTePress}: \url{https://doi.org/10.5220/0011093700003176}}
 
-	\input{acknowledgements}
+\abstract{%
+    Software and its dependencies build up a graph where edges connect packages according to their dependencies.
+    In this graph, downstream dependencies are all the nodes that depend on a package of interest.
+    Although gathering and mining such downstream dependencies allow for informed decision-making for a package developer, there is much room for improvement, such as automation and integration of this approach into their development process.
+    This paper makes two contributions:
+    \begin{enumerate*}[label=(\roman*)]
+        \item We propose an approach for efficiently gathering downstream dependencies of a single package and extracting usage samples from them using a static type analyzer.
+		\item We present a tool that allows npm package developers to survey the aggregated usage data directly in their IDE in an interactive and context-sensitive way.
+	\end{enumerate*}
+	We evaluate the approach and the tool on a selection of open source projects and specific development-related questions with respect to found downstream dependencies, gathering speed, and required storage.
+    Our methods return over \numprint{8000} downstream dependencies for popular packages and process about 12 dependencies per minute.
+    The usage sample extraction offers high precision for basic use cases.
+    The main limitations are the exclusion of unpopular and closed-source downstream dependencies as well as failing analysis when encountering complex build configurations or metaprogramming patterns.
+    To summarize, we show that the tool supports package developers in gathering usage data and surveying the use of their packages and APIs within their downstream dependencies, allowing for informed decision-making and improving the resdesign of APIs.
+}
 
-	\input{template/bibliography}
+\onecolumn \maketitle \normalsize \setcounter{footnote}{0} \vfill
 
-	%\appendix
+\section{Introduction}
+\label{sec:introduction}
+
+The continued proliferation and improvement of open-source software (OSS) platforms such as \emph{GitHub} or \emph{GitLab} and package deployment ecosystems such as \emph{npm}, \emph{pip}, or \emph{NuGet} support and facilitate software development on a global scale.
+Open-source development offers many advantages over traditional closed-source development, including voluntary contributions from the open-source community, greater transparency in security-related areas, and a high potential for solution reuse~\cite{saied2018-reusability}.
+These solutions are typically organized as packages, each solving an isolated problem and providing a higher-level interface.
+Packages can \emph{depend} on existing packages by including them in their manifest, i.e., the \texttt{package.json} file of npm packages or the \texttt{requirements.txt} file of Python projects.
+These dependency relations form a large directed graph connecting significant parts of the software world for today's programming language ecosystems.
+We define a software ecosystem as a collection of software projects, which are developed and which co-evolve in the same environment.
+
+Despite this connectedness by design, however, the development process of many packages is still characterized by an isolated approach:
+While OSS developers commonly submit tickets to or contribute patches against \emph{upstream repositories} that they depend on to solve subproblems, the reverse direction of these edges -- called \emph{downstream dependencies} and in the following referred to as \emph{dependencies} -- is often neglected by package developers.
+This deficit can cause a wide range of alignment issues, including poorly suited interfaces~\cite{piccioni2013empirical}, unidentified defects~\cite{wong2017more}, and compatibility problems~\cite{bogart2015breaks}.
+Eventually, all these issues impair the capabilities of the global OSS community to build and support high-quality packages.
+
+To tackle these concerns, we propose an approach to extract API usage samples from downstream-dependency repositories of individual packages to support package developers in exploring usages of their packages.
+We make these data directly available to package developers by integrating them into an integrated development environment (IDE).
+
+Our approach consists of three steps:
+\begin{enumerate*}[label=(\roman*)]
+	\item collect downstream dependency repositories from public source code repositories,
+	\item mine package usage samples from these dependencies using a type analyzer,
+	and \item aggregate and present these usage data to the package developer in its development environment.
+\end{enumerate*}
+The approach is implemented as a Visual Studio Code extension\footnote{All presented artifacts are available on GitHub: \href{https://github.com/LinqLover/downstream-repository-mining}{https://github.com/LinqLover/downstream-repository-mining}~\cite{thiede2022dowdep}} and evaluated on a selection of open source projects and specific development-centric questions.
+
+The remainder of this paper is structured as follows:
+In \cref{sec:related_work}, we summarize existing approaches and in \cref{sec:approach}, we outline the overall conditions for our solution and detail the collection of downstream dependency repositories and subsequent mining of usage data.
+In \cref{sec:implementation}, we present an implementation of our approach and outline design decisions for displaying usage samples to the user.
+Finally, in \cref{sec:evaluation}, we examine the fitness of our data mining approach and the usability of the display solution.
+\Cref{sec:conclusion} concludes this paper.
+
+\section{Related Work}
+\label{sec:related_work}
+%
+Proper tooling design for improving package developers' knowledge about interface usages in dependencies has not yet attracted significant attention in the scientific community.
+Nevertheless, programmatic analysis of dependency graphs and API usage mining are already standard techniques in the field of \emph{mining software repositories} (MSR).
+Chaturvedi et al. provide a broad overview of existing achievements and ongoing research topics in this field~\cite{chaturvedi2013tools}.
+Besides source code repositories, they describe data sources worthwhile to examine, including telemetry data from IDEs, issue trackers, and discussion platforms, and propose different directions for evaluating the retrieved data, e.g., classifying or ranking repositories, analyzing the evolution of projects, studying development communities, but also inspecting the relationships and dependencies between projects.
+We further consider related work in the areas of dependency graphs, usage sample extraction, and tooling support.
+
+\paragraph{Searching dependency graphs.}
+\label{sec:related_work/dependencies}
+%
+A common purpose for \emph{analyzing dependency graphs} is to discover transitive upstream dependencies of a project and assess their impact on the stability and vulnerability of the project~\cite{kikas2017structure}.
+Similarly, the spreading of security vulnerabilities along the chain of downstream dependencies can be measured~\cite{decan2018impact}.
+
+However, existing research on dependency graphs takes a broad statistical perspective and relies on a large corpus of downloaded software repositories~\cite{abdalkareem2017developers,kikas2017structure,katz2020libraries}.
+As opposed to this approach, these capacities are not suitable for scenarios that developers of a single package occasionally perform.
+In this case, developers will often use a public \emph{code search} service instead, such as \emph{GitHub} or \emph{Sourcegraph}.
+Liu et al.
+provide a survey of methods and trends in code search tools that include newer approaches such as structural or semantic search queries, code similarity metrics, or machine learning methods~\cite{liu2020opportunities}.
+
+\paragraph{Extracting usage samples.}
+\label{sec:related_work/usage_samples}
+%
+Dependency graphs do not provide information about package usage at sufficient granularity. For example, insights about referencing package classes or methods are missing.
+The process of extracting fine-grained information about all references to individual elements of an interface is referred to as \emph{API usage analysis}~\cite{lammel2011large}.
+A simple approach is to perform a string search for package names or members in the dependencies~\cite{mileva2010mining}, or to operate on the \emph{abstract syntax tree} (AST) of each parsed dependency to avoid false positive caused by ambivalent identifier names~\cite{qiu2016understanding}.
+In addition, one can collect usage data to analyze the historical importance of certain features supported by an API~\cite{sawant2017fine}.
+
+However, the precision of ASTs is limited for \emph{dynamically typed} languages such as JavaScript or Python.
+As opposed to static typing, the value type of an expression in a dynamically typed language may be unknown at the compile time of the program.
+For this reason, a \emph{type analysis} can help to predict runtime types of all expressions in the AST~\cite{jensen2009type}.
+This is usually accomplished by analyzing the control flow of a program and inferring possible types of every variable or function.
+Another source for enhancing type information is \emph{call graphs} that are either gathered \emph{statically}, i.e., as a result of a theoretical analysis of the source code, or \emph{dynamically}, i.e., sampled during actual program execution.
+While the latter method is better suited to include more contextual information, the former method has the advantage that it can be applied to a more considerable amount of source code without requiring concrete entry points, parameterization, and run-time data.
+Many solutions exist that analyze the structure of programs and extract relevant information to build call graphs:
+
+Collard et al.
+propose an infrastructure called \caps{srcML} that aims to create a unified representation of multilingual source code snippets for arbitrary analysis purposes, including the construction of call graphs~\cite{collard2013srcml}.
+Another solution utilizes an island parser to build polyglot call graphs~\cite{bogar2018lightweight}.
+Furthermore, Antal et al.
+compare several call graph generators for JavaScript and emphasize that static call graph generators have limited precision by design for languages supporting dynamic typing or meta-programming mechanisms~\cite{antal2018static}.
+
+To merge dependency graphs and call graphs, ecosystem call graphs can be constructed by applying call graphs to entire ecosystems that cross repository boundaries.
+Many approaches apply this concept to different ecosystems, often aiming to conduct fine-grained impact analysis for security vulnerabilities~\cite{hejderup2018software,boldi2020fine,wang2020empirical,hejderup2021praezi,keshani2021scalable,nielsen2021modular}.
+Another approach is the \emph{precise code intelligence} feature of Sourcegraph, which makes code references explorable across repository boundaries for repositories that provide a metadata file in the \emph{Language Server Index Format}.\footnote{\url{https://docs.sourcegraph.com/code_intelligence/explanations/precise_code_intelligence}}
+
+After collecting these usage data, additional processing is possible to extract general usage information from the extensive raw data.
+Next to basic grouping and counting operations, such aggregations can be built by detecting popular \emph{usage patterns} of API features in the downstream dependencies.
+Zhong et al.
+propose such a framework, that, for instance, finds sequences of API members that are invoked frequently and even uses these patterns for guiding API users by giving them recommendations~\cite{zhong2009mapo}.
+Hanam et al. pursue a different goal in their tool that helps package developers assess the impact of breaking API changes on the functionality of downstream dependencies~\cite{hanam2019aiding}.
+
+\paragraph{Presentation of results.}
+\label{sec:related_work/presentation}
+
+To establish an adequate developer experience, any collected usage data still need to be presented suitably.
+Due to the hierarchical structure of source code, a common approach for this is a hierarchical and navigatable representation of the collected call tree.
+An early form of this representation has been invented as the interactive \enquote{message set} tool for browsing senders and implementors in an object-oriented system for the Smalltalk programming environment \cite{goldberg1984smalltalk}.
+Modern alternatives include the \emph{Stacksplorer} \cite{karrer2011stacksplorer} or \emph{Blaze} \cite{kramer2012blaze} that list next to the currently focused method other methods which are adjacent to this method in the call graph.
+With a focus on exploring references to API members, De Roover et al.
+propose a set of additional views, including hierarchical lists and word clouds for highly referenced identifiers \cite{de2013multi}.
+Focusing on exploring APIs in a non-code-centric way, Hora and Valente propose a dashboard that allows developers to browse existing APIs and track possibly breaking changes in their interfaces \cite{hora2015apiwave}.
+
+\section{Downstream Dependency Mining}
+\label{sec:approach}
+%
+Our approach to improve developers' knowledge about the usage of their packages is based on the automatic gathering of downstream dependency information and integration into their development environment.
+This approach assumes a target package and focuses on showing a developer actual usage of parts of their package and, in particular, answering the following questions:
+In doing so, we identified three questions from package developers about the usage of their packages:
+%
+\begin{enumerate}[label=Q\arabic*]
+	\item \label[question]{q1} Which dependencies are using the target package, and what problems do they try to solve with them?
+	\item \label[question]{q2} By how many dependencies is a particular package member being used?
+	\item \label[question]{q3} In which contexts and constellations is a particular package member being used?
+\end{enumerate}
+%
+For an effective integration into the development process, we pose three non-functional requirements:
+%
+\begin{enumerate}[label=R\arabic*]
+	\item \label[requirement]{req1} The tool is ready to use out of the box and requires little configuration (less than 5 minutes for a new user).
+	\item \label[requirement]{req2} The tool consumes sufficiently few computational resources to run on a single machine but still delivers interactive response times according to Shneiderman's requirement to frequent tasks~\cite{shneiderman2010designing}.
+	\item \label[requirement]{req3} The tool blends in with the usual workflow of package developers at the best possible rate.
+\end{enumerate}
+%
+On a conceptual level, we separate the approach into the collection of downstream dependency projects and mining of usage samples based on a target package.
+
+\begin{algorithm*}[t]
+	\caption{Extraction of usage samples.}\label{alg:usage_mining}
+
+	\KwIn{\\\Indp
+		$\mli{package}$: target package \\
+		$\mli{dependencies}$: downstream dependencies}
+	\KwOut{usage samples (set of strings)}
+	\;
+	\For{$\mli{dependency} \in \mli{dependencies}$}{
+		$\mli{asf} \gets \mtx{parse}(\mli{dependency} \cup \mli{package})$\;
+	  	$\mtx{annotate\_types}(\mli{asf})$\;
+		\For{$\mli{ast} \in \mli{asf}$}{
+			\For{$\mli{node} \in \mli{dfs}(\mli{ast})$}{
+				\For{$\mli{pattern} \in \mli{patterns}$}{
+					\If{$\mli{pattern}.\mtx{matches}(\mli{node}) \wedge\, \mli{package}.\mtx{declares}(\mli{pattern}.\mtx{getType}(\mli{node}))$}{
+						\kwYield{$\mli{node}.\mtx{text}$}
+					}
+				}
+			}
+		}
+	}
+\end{algorithm*}
+
+\subsection{Downstream Dependency Collection}
+\label{sec:approach/dependency_collection}
+
+In the first step, a list of repositories that depend on the target package has to be assembled.
+As mentioned in \cref{sec:related_work/usage_samples}, many approaches start with a large downloaded corpus of unspecific repositories from the ecosystem, which they then iterate over to filter the relevant repositories.
+However, a major drawback of this approach is the high resource demand for both creating and traversing this corpus.
+This approach is suited for analyzing repositories on a large scale but is not conform to \cref{req1} because of its large footprint in terms of computational power, memory, and time.
+As an alternative, we have decided to apply filtering to the set of repositories before downloading a subset of it to the developers' machine.
+For that, we use two types of data sources that are available as public web platforms:
+
+\begin{enumerate}[label=(\roman*)]
+	\item Package repositories that maintain a doubly-connected edge list of interdependent packages in an ecosystem.
+	\item Code search engines that index the source code of many repositories from OSS platforms.
+Using these search engines, we can query all repositories that declare a dependency on the target package in their package manifest file.
+\end{enumerate}
+
+\subsection{Usage Sample Mining}
+\label{sec:approach/usage_mining}
+
+Having downloaded the selected downstream dependency repositories, the next step is to extract usage samples for the target package from each dependency repository.
+Our goal is to gather fine-grained source code excerpts that reference individual identifiers exposed by the target package.
+The complete procedure is displayed in \cref{alg:usage_mining}.
+
+%
+To do so, the source code of every dependency repository as well as the source code of the target package are parsed, each into a separate \emph{abstract syntax forest} (ASF, i.e., a set of ASTs).
+In a second step, static type analysis against each dependency ASF is performed together with the target package's ASF.
+The results of the type analysis are attached to the ASF so that every identifier is annotated with a type symbol that links to the declaration of the type for the identifier.
+For instance, after this step, every variable node contains a link to the assignment node of this variable, and every function call expression contains a link to the definition of this function.
+The operating principle of this type analysis depends on the kind of programming language.
+In statically typed languages, type symbols can be retrieved from declarations, whereas in dynamically typed languages, a control flow analysis will be required to identify the origin of every identifier's type.
+
+In the final step, all nodes whose type is declared in the target package are collected from each ASF.
+To identify these links, we use a set of language-specific patterns for AST subtrees that constitute a usage expression.
+In particular, each of these patterns expects a node containing a link to an identifier declaration (see \cref{fig:approach/usage_mining/patterns}).
+
+\begin{figure*}
+	\begin{minipage}{\linewidth}
+		\colorlet{lowlight}{black!40}
+		\newcommand\textlowlight[1]{\textcolor{lowlight}{#1}}
+		\newcommand\texthighlight[1]{\textbf{\textcolor{accent1}{#1}}}
+		\begin{center}
+			\begin{subfigure}[t]{.30\linewidth}
+				\begin{tikzpicture}
+                	\node {CallExpression}
+                		child {node [accent1] {\textbf{identifier}}}
+                		child [lowlight] {node [lowlight, yshift = -0.5cm] {typeArguments}}
+                		child [lowlight] {node [lowlight] {arguments}};
+                \end{tikzpicture}
+                \caption[LoF entry]{
+                	Node pattern for a TypeScript function call, such as in:
+
+                	\mycode*{\textlowlight{result = }\uline{\texthighlight{fun}<\textlowlight{T1}, \textlowlight{T2}>(\textlowlight{arg1}, \textlowlight{arg2})}\textlowlight{;}}
+                }
+
+			\end{subfigure}
+			\hfill
+			\begin{subfigure}[t]{.30\linewidth}
+				\begin{tikzpicture}
+                	\node {PropertyAccessExpression}
+                		child {node [accent1] {\textbf{identifier}}}
+                		child [white] {node [yshift = -0.5cm] {\phantom{node}}}  % ensure same height as sibling figures
+                		child [lowlight] {node [lowlight] {name}}
+                		;
+                \end{tikzpicture}
+                \caption[LoF entry]{
+                	Node pattern for a JavaScript property access, such as in:
+
+                	\mycode*{\textlowlight{return }\uline{\textlowlight{obj}.\texthighlight{prop}}\textlowlight{;}}
+                }
+
+			\end{subfigure}
+			\hfill
+			\begin{subfigure}[t]{.30\linewidth}
+				\begin{tikzpicture}
+                	\node [accent1] {\textbf{JsxOpeningExpression}}
+                		child [lowlight] {node [lowlight] {tagName}}
+                		child [lowlight] {node [lowlight, yshift = -0.5cm] {typeArguments}}
+                		child [lowlight] {node [lowlight] {attributes}};
+                \end{tikzpicture}
+                \caption[LoF entry]{
+                	Node pattern for a JSX opening element (as supported in React or TypeScript), such as in:
+
+                	\mycode*{\textlowlight{elem = }\uline{<\texthighlight{Button} \textlowlight{color}="\textlowlight{blue}"> \textlowlight{Submit</Button>}}\textlowlight{;}}
+                }
+			\end{subfigure}
+
+            \vspace{\baselineskip}
+			\caption{AST patterns for example JavaScript/TypeScript expressions.
+				The \texthighlight{highlighted} node contains the link to the declaration of the referenced identifier.
+			}
+			\label{fig:approach/usage_mining/patterns}
+		\end{center}
+	\end{minipage}
+\end{figure*}
+
+\section{Prototype}
+\label{sec:implementation}
+
+In our prototype, we focus on analyzing JavaScript projects for node.js.
+This decision is motivated by the large prevalence of JavaScript\footnote{GitHut 2.0: A small place to discover languages in GitHub.
+\url{https://madnight.github.io/githut/\#/pushes}} as well as the first-rate extent of the npm ecosystem which has been unsurpassed since 2015\footnote{Modulecounts: \url{http://www.modulecounts.com/}}.
+The prototype instantiates the downstream dependency collection and the usage sample mining and allows for the integration of the results into the development environment.
+
+\subsection{Downstream Dependency Collection}
+\label{sec:implementation/dependency_collection}
+
+The de-facto standard package repository manager for node.js is npm.
+To fetch downstream dependency packages from the npm registry, we use the npm package \texttt{npm-dependants} which scrapes the dependents list from npmjs.com as there does not exist a publicly available API for these data.
+To keep the footprint of our implementation small, only a part of the dependents list is scraped.
+Then, basic metadata for each found package is requested from the npm registry, including the \emph{tarball} URL of the latest package version, using the package \mycode{package-metadata}.
+Finally, each tarball is downloaded and extracted using the package \mycode{download-package-tarball}.
+
+\begin{lstfloat}[t]
+\begin{lstlisting}[language=typescript,%json,
+	label=sec:implementation/package.json,
+	caption={Example \texttt{package.json} file for the \texttt{ripple-lib} package specifying multiple dependencies (truncated).
+The list of dependencies that are extracted from this example contains \texttt{bignumber.js}, \texttt{https-proxy-agent}, and \texttt{jsonschema}.}]
+{
+	"name": "ripple-lib",
+	"version": "1.10.0",
+	"description": "An API for the XRP Ledger",
+	"dependencies": {
+		"bignumber.js": "^9.0.0",
+		"https-proxy-agent": "^5.0.0",
+		"jsonschema": "1.2.2"
+	}
+}
+\end{lstlisting}
+\end{lstfloat}
+
+For the second method -- based on a code search engine --, we have identified Sourcegraph\footnote{\url{https://sourcegraph.com/}} as a promising platform.
+npm packages specify their dependencies in a \mycode{package.json} metadata file (see \cref{sec:implementation/package.json}).
+To find all packages depending on a certain package, we can search all available \mycode{package.json} files for a reference to this package identifier.
+We refine our search query with some additional constraints to filter out package copies from \mycode{node_modules} folders that downstream developers have pushed accidentally, and to limit the number of results retrieved.
+We submit this search query to the publicly available GraphQL API of Sourcegraph\footnote{\url{https://docs.sourcegraph.com/api/graphql}} by using the npm package \mycode{graphql-request}.
+After retrieving a search result, we download a snapshot of the full repository by using the package \mycode{download-git-repo}.
+
+Additionally, we enrich the metadata of each package with a few metrics indicating its popularity from the associated GitHub repository if specified.
+The GitHub API is accessed via the official \emph{octokit} library\footnote{\url{https://octokit.github.io/}}.
+
+\subsection{Usage Sample Mining}
+\label{sec:implementation/usage_mining}
+
+For parsing the dependencies, we use the \emph{TypeScript Compiler API}\footnote{\url{https://github.com/Microsoft/TypeScript/wiki/Using-the-Compiler-API}}.
+TypeScript is an extension of JavaScript that adds strong typing; typing is based on a combination of implicit type inference and explicit type declarations.
+As a side benefit, our implementation is also able to analyze packages implemented in true TypeScript.
+
+The TypeScript compiler's \emph{binder} component annotates every node of the parsed program with a type symbol if it can resolve one.
+After performing a type analysis of the dependency by instrumenting the binder, we collect all nodes from the type-annotated ASF that refer to the target package,
+matching each node against a list of defined patterns (similar to \cref{fig:approach/usage_mining/patterns}).
+A lookup of the node's type symbol's declaration is performed based on the syntax kinds of the node, its ancestors, and its descendants, and then compared with the source directory of the target package.
+
+\begin{figure*}[t] % requires figures-spec.tex
+    %
+    \begin{tikzpicture}[figNS, spy using outlines = {style = spyRC, gray, magnification = 2.0, width = 48mm, height = 16mm}]
+        % graphics:
+        \node[figRC, anchor = east](fig0) at (0,0)
+            {\includegraphics[width = 0.2857\dimexpr(\textwidth-2.0\pfull) - 0.25\pfull]{figures/dependencies-cropped}};
+        \node[figRC, anchor = west](fig1) at ([xshift = \pfull] fig0.east)
+            {\includegraphics[width = 0.2857\dimexpr(\textwidth-2.0\pfull) - 0.25\pfull]{figures/references-cropped}};
+        \node[figRC, anchor = west](fig2) at ([xshift = \pfull] fig1.east)
+            {\includegraphics[width = 0.4288\dimexpr(\textwidth-2.0\pfull) - 0.25\pfull]{figures/codelens-cropped}};
+        % sub-captions/labels:
+        \node[below right = 0 of fig0, labelSE](lab0){(a) The dependency browser.};
+        \node[below right = 0 of fig1, labelSE](lab1){(b) The usage browser.};
+        \node[below right = 0 of fig2, labelSE](lab1){(c) The CodeLens integration for the class \texttt{GraphQLError}.};
+        % spies:
+        \spy on ($(fig2.center)+(-14.8mm, +20mm)$) in node at ($(fig2.center)+(+9mm,+1mm)$);
+    \end{tikzpicture}
+    %
+    \caption{Screenshots of our VS Code extension used to explore downstream dependencies of the npm package \texttt{graphql}.}
+    \label{fig:implementation/presentation/screenshots}
+    %
+\end{figure*}
+
+Normally, foreign types can only be resolved if they are declared in a dependency module that has been installed into the \mycode{node_modules} folder of the repository.
+Because downloading and installing all dependency modules for every downstream repository of the target package would increase the computational resources of the usage mining drastically and eventually violate \cref{req2}, we skip this step but instead modify the module resolution strategy of the TypeScript compiler host.
+To do so, we extend the \mycode{paths} parameter from the default compiler options\footnote{\url{https://www.typescriptlang.org/tsconfig\#paths}} and insert a new entry that remaps accesses to the target package name to the separate source code directory of the target package.
+
+\subsection{Presentation of Results}
+\label{sec:implementation/presentation}
+
+After all references have been collected, a proper user interface (UI) is still required to provide users easy access to these data that fulfills the requirements mentioned above.
+To satisfy \cref{req1} and \cref{req3} by making our tool available in the usual working environment of users, we implement it as an extension to the \emph{Visual Studio Code} IDE\footnote{\url{https://code.visualstudio.com/}}.
+It also provides a comprehensive set of APIs for extension developers.
+To support other researchers in reusing our solution, we also provide a CLI.
+The user interface is divided into three key views, supporting developers in answering the questions raised in \cref{sec:approach} (see \cref{fig:implementation/presentation/screenshots}):
+
+\begin{enumerate}[label=(\roman*)]
+	\item The \emph{dependency browser} allows to explore all downstream dependencies and, grouped for each dependency, all references to the target package.
+	\item The \emph{usage browser} displays all public package members and, grouped for each member, all dependencies and their references to this member.
+	\item The \emph{CodeLens integration} provides quick access to a slice of usage samples and is attached to the definition of each package member in the source code editor.
+\end{enumerate}
+
+Both references and members are organized each in a tree view that reflects the hierarchical structure of the original software repository.
+In addition, we recognize the effort of browsing large lists of dependency data and encounter it by providing an \enquote{I'm feeling lucky} button for every view that redirects the user to a random dependency or reference, respectively, to gain a faster, unbiased impression of usage samples.
+
+To implement each of these views in the VS Code Extension API (VSCE)\footnote{\url{https://code.visualstudio.com/api}}, we use the \emph{Tree View API} and the \emph{CodeLens API}.
+One challenge has been to deliver fast results and not to block the user interface because even despite the lightweight mining methods we chose to satisfy \cref{req2} from above, querying, downloading, and analyzing each dependency takes a few seconds (see \cref{sec:evaluation}).
+To overcome this issue, we use pagination wherever possible and push incremental UI updates. % apply the observer pattern to
+As the VSCE API per se does not provide for multithreading or multiprocessing operations but suggests a Promise/A+-driven dataflow, we adopt this style for our object model by using the JavaScript concepts asynchronous functions, \mycode{AsyncIterator}s, and \mycode{Promise.all} to avoid busy waiting during the data collection process.
+
+\begin{table*}[t]
+    \centering
+    \footnotesize
+    \rowcolors{2}{white}{gray!15}%
+    \setlength{\tabcolsep}{10pt}
+    \setlength\aboverulesep{0pt}
+    \setlength\belowrulesep{0pt}
+    \renewcommand{\arraystretch}{1.45}
+    \caption{Quantity and false-positive rates~(FPR) of downstream dependencies found by the presented methods (using npm and Sourcegraph) for selected packages.}
+    \label{tab:evaluation/resqu1/quantities}
+    \begin{tabularx}{0.9\linewidth}{Xcrcrcrrcrr}%
+        %
+            \toprule
+            \rowcolor{white}
+            \multicolumn{1}{c}{}
+            & & &
+            & \multicolumn{2}{c}{\textbf{npm}}
+            &
+            & \multicolumn{2}{c}{\textbf{Sourcegraph}}
+            &
+            & \\
+        %
+            \rowcolor{white}
+            \textbf{Package}\rot{\hspace{5.5em}}
+            &
+            & \multirow[b]{-2}{*}[17pt]{\rot{GitHub stars}}
+            &
+            & \rott{c}{\strut Count}     %
+            & \rott{c}{\strut FPR}  %
+            &
+            & \rott{c}{\strut Count}    %
+            & \rott{c}{\strut FPR}    %
+            &
+            & \multirow[b]{-2}{*}[31.5pt]{\rot{Intersection in \%}}
+            \\\toprule
+        %
+        base64id          & & \numprint{   16} & &  27 & 0.20 & & \numprint{  45} & 1.00 & & 8 \\
+        nemo              & & \numprint{   38} & &   1 & 0.00 & & \numprint{   1} & 1.00 & & 0 \\
+        random-js         & & \numprint{  556} & & 219 & 0.14 & & \numprint{ 193} & 0.36 & & 15 \\
+        kubernetes-client & & \numprint{  902} & &  36 & 0.13 & & \numprint{  79} & 0.21 & & 16 \\
+        jsonschema        & & \numprint{ 1547} & & 394 & 0.00 & & \numprint{ 517} & 0.18 & & 2 \\
+        graphql           & & \numprint{18005} & & 396 & 0.17 & & \numprint{8863} & 0.68 & & 2 \\
+        cheerio           & & \numprint{24228} & & 396 & 0.07 & & \numprint{6779} & 0.07 & & 0 \\\bottomrule
+        %
+    \end{tabularx}%\vspace{2mm}
+\end{table*}
+
+\section{Evaluation}
+\label{sec:evaluation}
+
+To evaluate our approach, we formulate three research questions:
+
+\begin{enumerate}[label=RQ\arabic*,itemindent=0.3cm]
+	\item \label[research question]{resqu1} What is the quality and quantity of the proposed methods for dependency collection?
+	\item \label[research question]{resqu2} What is the quality and quantity of the proposed method for mining usage samples?
+	\item \label[research question]{resqu3} How well is the proposed tool applicable with regard to the questions and requirements described in \cref{sec:approach}?
+\end{enumerate}
+%
+In the following, we will investigate each question.
+
+\subsection{\ref{resqu1}: Dependency collection}
+\label{sec:evaluation/resqu1}
+
+To assess the quality and quantity of dependency collection, we analyze it with respect to extent, precision, recall, and performance.
+\Cref{tab:evaluation/resqu1/quantities} shows the number of dependencies collected to build an experimental dataset from each data source following the proposed methods for a set of manually selected npm packages.
+For each package, we have annotated a subset of the collected dependencies (max. 20 dependencies per package) to identify and classify false positive hits.
+
+\paragraph{Extent.}
+\label{sec:evaluation/resqu1/extent}
+
+Regarding the total number of dependencies collected by each method, no clear trend in favor of any method can be ascertained for small or medium packages, i.e., having less than \num{10,000} stars on GitHub.
+For larger packages, i.e., having at least \num{10,000} stars, however, the number of dependencies collected from the npm registry stagnates near to 400 hits.
+Beyond this limit, the npm registry returned internal server errors for our requests.
+For Sourcegraph, we have not hit any limitations so far.
+Currently, they do not provide any official documentation for the exact rate limits.
+%
+As the disjunct proportion of results from both methods is very small (on average about \SI{6}{\percent}), we consider a combination of both data sources useful for maximizing the extent and diversity of the gained dataset.
+
+\paragraph{Precision.}
+\label{sec:evaluation/resqu1/precision}
+
+The precision of collected dependencies is drastically lower for dependencies found on Sourcegraph than for such found on npm.
+\Cref{fig:evaluation/resqu1/fp_causes} collates the causes we have identified for false positives; most frequently, repositories specify a dependency on a target package in their package manifest file but do not import this package at any place.
+%
+\begin{figure*}[t]
+	\centering
+    %\small
+    \footnotesize
+	% Fix font size of \thead
+
+    \pgfplotstableread[col sep=comma,]{measurements/fpr.csv}\datatable%
+    \pgfplotstablefilter[source equals {Sourcegraph}]{\datatable}{\datatableSourcegraph}%
+    \pgfplotstablefilter[source equals {npm}]{\datatable}{\datatableNpm}%
+    \begin{tikzpicture}[outer sep=0pt]%
+        \begin{axis}[
+        	compat=newest,
+        	name=fpr,
+        	xbar=2pt,
+        	axis on top,
+        	%scaled ticks=true,
+        	scaled x ticks=false,
+        	width=0.8\linewidth,
+        	height=14\baselineskip,
+        	%enlarge x limits=0.15,
+        	bar width=6.0pt,
+        	%ylabel=\footnotesize{Types},
+        	xlabel=\footnotesize{false-positive frequencies},
+        	xmajorgrids,
+        	major grid style={draw=white},
+        	tick label style={font=\footnotesize},
+        	xticklabel style={
+        		/pgf/number format/fixed,
+        		/pgf/number format/precision=2
+        	},
+        	axis x line*=bottom,
+        	axis y line*=left,
+        	xtick align=outside,
+        	%ytick={0,2,...,14},
+        	%ytick=data,
+        	yticklabels={,package unused,peer dependency,type definitions only,package.json mismatch},
+        	xmin=0.0,
+        	xmax=0.45,
+        	ymin=-0.5,
+        	ymax=3.5,
+        	point meta=rawx,
+        	nodes near coords,
+        	every node near coord/.append style={anchor=west, font=\footnotesize,/pgf/number format/.cd, precision=2, fixed,1000 sep={\,}},
+	        %nodes near coords align={vertical},
+    	]
+    	    \addplot[white,very thin,fill=plots-1,text=black] table[x={fpr},y expr=\coordindex]{\datatableSourcegraph};
+    	    \addplot[white,very thin,fill=plots-2,text=black] table[x={fpr},y expr=\coordindex]{\datatableNpm};
+    	\end{axis}
+    	\begin{axis}[
+        	name=fpr_legend,
+        	compat=1.3,
+        	at={($(fpr.north east)+(0.0cm,0.0cm)$)},
+        	hide axis,
+        	bar width=0pt,
+        	ticks=none,
+        	%legend columns=2,
+        	legend style={
+        		at={(0.0,0.0)},
+        		anchor=north east,
+        		draw=none,
+        		legend cell align=left,
+        		%/tikz/column 2/.style={
+                %    column sep=5pt,
+                %},
+        	},
+        	legend image code/.code={%
+        		\draw (0.0cm,-0.05cm) rectangle (0.4cm,0.15cm);
+        	},
+        	text height=1.1ex,
+        	%width=0.5\columnwidth,
+        	height=2cm,
+        ]
+        	\addplot[draw=none,white,very thin,fill=plots-1] coordinates {(0,0)};
+        	\addlegendentry{\; Sourcegraph}
+        	\addplot[draw=none,white,very thin,fill=plots-2] coordinates {(0,0)};
+        	\addlegendentry{\; npm}
+        \end{axis}%
+    \end{tikzpicture}%
+    %\vspace{-1\baselineskip}
+	\caption{Causes for false-positive dependency matches and their frequencies.}
+	\label{fig:evaluation/resqu1/fp_causes}
+\end{figure*}
+%
+In some situations, this may happen if the package is a plugin for another package or if it is invoked as a CLI from a build script, but in the majority of repositories, developers trivially appear to have specified the upstream dependency by accident (e.g., while copying a \mycode{package.json} file over from another package), or to have forgotten to remove the upstream dependency after switching away from using the package.
+Less common causes are repositories that only add type definitions to a package but do not actually import it, as well as packages required by a repository that declares a peer dependency on the target package, which needs to be fulfilled by the depending repository.
+%
+We explain the increased false-positive rate for Sourcegraph dependencies by our observation that packages found on npm are deliberately published and typically stand out by their higher cohesion and commitment to maintenance, whereas GitHub-only projects contain a higher share of hobby or students' projects.
+%
+We stress that a reduced precision does not impair the quality of results displayed to package developers as all dependencies not containing at least one
+usage sample can be easily filtered out, but downloading and analyzing any irrelevant packages lowers the performance of the approach.
+
+\paragraph{Recall.}
+\label{sec:evaluation/resqu1/recall}
+
+Besides the precision of the collected dependencies, their recall is of interest, too.
+Since dependencies are collected in excerpts from two large datasets, a quantitative analysis of false negatives would require costly manual annotation and is target for future work.
+Nevertheless, some causes will prevent a dependency from being found by our methods:
+
+\begin{table*}
+    \footnotesize
+    \centering
+    \rowcolors{2}{white}{gray!15}%
+    \setlength{\tabcolsep}{25pt}
+    \setlength\aboverulesep{0pt}
+    \setlength\belowrulesep{0pt}
+    \renewcommand{\arraystretch}{1.45}
+    \caption{Performance metrics and remarks for both dependency collection methods using npm and Sourcegraph.}
+    \begin{threeparttable}
+        \begin{tabularx}{0.9\linewidth}{Xrr}
+            \toprule
+            \textbf{Metric}                       & \textbf{npm} & \textbf{Sourcegraph} \\\midrule
+            \strut Search speed~\textsuperscript{a} \hfill\si{\second/pkg}
+                & 1.58 &  0.04  \\
+            \strut Download speed~\textsuperscript{a,b} \hfill\si{\second/pkg}
+                & 0.26 &  8.80  \\
+            \strut Storage \hfill\si{\mega\byte/pkg}
+                & 5.80 & 27.20  \\
+            \strut API limitations & max. 400 results & none known\\ \bottomrule %
+        \end{tabularx}
+        \begin{tablenotes}\footnotesize
+            %
+    		\item[\textsuperscript{a}] Test machine: 7 vCPUs Intel Xeon Cascade Lake at
+    		\SI{2.80}{\giga\hertz}, internet down speed \SI{1.8}{\giga\bit/\second}.
+    		%
+    		\item[\textsuperscript{b}] Effective speed downloading multiple packages in parallel to manage latencies.
+    		%
+        \end{tablenotes}
+    \end{threeparttable}
+    \label{tab:evaluation/resqu1/performance}
+\end{table*}
+
+\begin{itemize}
+	\item Packages without a proper dependency manifest cannot be detected as our method is based on parsing these metadata.
+	\item Only published packages are found on npm, leading to a bias for generic and professional software.
+	\item On both platforms, results will be sorted based on intransparent criteria (which, as we speculate, include the number of direct dependents on npm and the recent update frequency on Sourcegraph, respectively).
+	As we only fetch the first dependencies from both data sources, this is a likely source of further biases.
+	These biases could be fought by always fetching all dependencies, but this would drastically reduce performance and would require a workaround for the npm query limitation.
+\end{itemize}
+
+\paragraph{Performance.}
+\label{sec:evaluation/resqu1/performance}
+\Cref{tab:evaluation/resqu1/performance} gives some basic metrics comparing the performance of both data sources.
+While searching downstream dependencies is slower by average on npm as we use a web scraper instead of an API for this source, npm packages are usually smaller than many mono-repositories on OSS platforms that contain multiple node.js packages.
+In addition, they are faster to download since the \texttt{download-git-repo} package that we use for repositories found on Sourcegraph only uses zipballs instead of tarballs (\texttt{.tar.gz} files), while the latter would offer a higher compression rate.
+
+\subsection{\ref{resqu2}: Usage mining}
+%
+To assess the quality and quantity of usage mining, we examine this processing step's precision, recall, and performance.
+Due to the complexity of a detailed annotation process, we only consider the existence of found usage samples on the dependency level.
+The absolute quantity of found usage samples largely varies for different packages and dependencies based on the semantic extent of the package and the coupling.% between package and dependency.
+
+\paragraph{Precision.}
+%
+Under laboratory conditions, false-positive usage samples cannot be emitted by our method if we assume the correctness of the TypeScript compiler.
+There are only two theoretical exceptions to this invariant:
+%
+\begin{enumerate*}[label=(\roman*)]
+    %
+	\item In case of a name collision between two packages, invalid or false positive usage samples may be emitted.
+        However, the npm infrastructure attempts to rule out these collisions by using the package name as a unique ID for every published package.
+	%
+	\item If dependency developers deliberately interfere with the TypeScript compiler (for instance,
+	    by suppressing type errors using \texttt{@ts-ignore} comments, both false positive and false negative matches are possible.
+	%
+\end{enumerate*}
+%
+Additionally, some npm packages contain minified sources only that are still searchable, valid code but can be significantly harder to read.
+
+\paragraph{Recall.}
+%
+To evaluate the recall of our method, we have refined the experimental dataset collected in \cref{sec:evaluation/resqu1} and removed all false-positive dependencies.
+Within this cleansed dataset, the overall rate of dependencies for that our method cannot find at least one usage sample accounts for \SI{47.9}{\percent}.
+To explain these false negatives, we have identified some systematic causes:
+%
+\begin{itemize}
+    %
+	\item Many projects on OSS platforms have complex build configurations that include additional transpilation or code generation steps before a final version of the source code is reached that is valid to the node.js interpreter or the TypeScript compiler.
+		Unless we add explicit support for such build configurations, type analysis and usage mining for these projects will fail.
+	%
+	\item In some situations, additional type definitions are required to perform a complete type inference of a dependency.
+		This applies to every parametrized callback from a package for that type definitions are not available.
+		This limitation could be resolved by downloading or generating type definitions for all upstream dependencies of every downstream dependency; however, this would reduce the approach's performance.
+	%
+	\item The static type analyzer of TypeScript has some limitations.
+		For instance, the type analysis will have a limited recall for certain control flow patterns or metaprogramming constructs such as meta-circular evaluation using the \texttt{eval()} function or dynamic function binding using \texttt{Function.bind()}.
+		These limitations could be resolved with AST preprocessing and partial evaluation of the source code.
+	%
+\end{itemize}
+
+\paragraph{Performance.}
+%
+The total time spent performing type analysis for a repository from the experimental dataset and mining usage samples averages about \num{3} seconds.
+The complete ASF of an average parsed repository consumes between \SI{10}{\mega\byte} and \SI{500}{\mega\byte} memory, depending on the size of the repository.
+
+\subsection{\ref{resqu3}: Requirements}
+\label{sec:evaluation/resqu3}
+%
+To assess the applicability of our tool, we investigate different options for users who would like to answer the questions raised in \cref{sec:approach}.
+We further analyze how far our tool meets the requirements posed above.
+
+\paragraph{Answering User Questions.}
+%
+To answer \cref{q1} without our tool, users could access the data sources used by our tool manually to search for and view downstream dependencies.
+The source code of repositories can be browsed on Sourcegraph, but if an npm package is not available on an OSS platform, users will need to download and extract it.
+With our tool, the data collection process is condensed into a single button that incrementally displays all references from both data sources.
+Users can hover or click any dependency to view its documentation or implementation.
+%
+To answer \cref{q2,q3} without our tool, users need to scan each found dependency separately to count or read all usage samples.
+If they intend to analyze the usage of a member with an exact name, they can perform an expeditious string search.
+This is possible using Sourcegraph or another search engine if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
+If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
+Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for a few repositories only.
+%
+All usage samples can be collected automatically and merged into a single list within our tool.
+Once the collected dependencies have been processed, users can select a member of interest and view all its usage samples with a single click.
+For the usage analysis of Java APIs, the tool \emph{Exapus} also considers different kinds of member usages such as instantiation vs.
+inheritance of a class \cite{de2013multi}; a similar classification could improve the usability of our tool.
+
+\paragraph{Meeting Requirements.}
+%
+To satisfy \cref{req1}, the application needs to be easy to set up.
+As our extension can be installed with two clicks from the Visual Studio Code Extension Marketplace and the installation takes less than 10 seconds on our test machines, it fulfills this requirement.
+
+We break down \cref{req2} into two acceptance criteria: application liveness and small resource footprint.
+As discussed before, our tool can process 5 up to 12 dependencies per minute while requiring about \SI{500}{\mega\byte} memory in total and less than \SI{30}{\mega\byte} storage per package.
+After the tool is activated, the first results usually appear after less than 10 seconds on the UI.
+This is an acceptable delay regarding Shneiderman's definition of acceptable application response times, so the liveness criterion is fulfilled.
+Even if the tool downloads a few hundred dependencies, it will occupy less than \SI{10}{\giga\byte} storage that can be released at any time, which we consider a small resource footprint at a time where modern operating systems require \SI{64}{\giga\byte} storage; thus, the second criterion is fulfilled as well.
+
+\Cref{req3} effectively calls for a minimum number of context switches that are required to use the tool, i.e., for minimizing the temporal, spatial, and semantic distance~\cite{ungar1997debugging} between the downstream dependency UI and the IDE used by package developers.
+%
+Once the data are available in the UI, interaction is possible with the same speed as with local source files in the package.
+This meets Shneiderman's requirement to frequent tasks and indicates a low temporal distance.
+%
+The spatial distance varies for the different views of the tool:
+A separate toolbar has to be opened for the dependency and usage browsers, which indicates a higher spatial distance; still, the artifacts are available in the same IDE.
+Also, the dependency artifacts have no strong relation to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
+The code annotations are displayed close to the package source code with a small spatial distance.
+%
+The semantic distance can be described as the perceived similarity of artifacts displayed both in the tool's UI and in the existing IDE, i.e., the package and dependency members.
+Most items in the usage browser bear the same label as the corresponding identifier in the source code, which reduces the semantic distance.
+However, dependency member path nodes that refer to anonymous expressions are displayed differently compared to the outline view of VS Code (see \cref{fig:implementation/presentation/screenshots} (a)), slightly increasing the semantic distance.
+%
+With a low temporal distance, a low-to-medium spatial distance, and a mainly low semantic distance, our tool also fulfills \cref{req3}.
+
+\section{Conclusions and Future Work}
+\label{sec:conclusion}
+
+Downstream dependencies offer a promising perspective for package developers interested in understanding how their interfaces are used in practice by other software developers.
+In this paper, we have proposed an automated approach to making this sort of information accessible to package developers by automating the dependency collection and mining of usage samples from every dependency.
+We have identified two kinds of rich data sources for efficiently collecting downstream dependencies: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
+We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis before.
+We have demonstrated the usability of our approach with a tool that embeds the downstream dependency data into the VS Code IDE.
+%
+Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent and further that the resource requirements of our prototype are sufficiently low for collecting all data on the local machine of a package developer.
+
+Nevertheless, we have identified several causes for false negatives over the whole mining process that can bias the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
+Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our approach for mining usage samples as well as the efficacy of our tool.
+As for the first question, manual annotation of source code repositories with usage samples will be required to compare them to the outputs of our implementation.
+Close insights for the second question could be gained from a user study that measures the impact of our tool on the efficiency of package developers solving downstream dependency-related tasks.
+
+We believe that our tool has further potential to support package developers in surveying downstream dependencies.
+As future work, we envision other purposes for analyzing the collected downstream dependency data, including usage pattern mining, automated convenience protocol suggestions, and the generation of metrics for classifying downstream dependencies or measuring the cohesion and impact of libraries within an ecosystem.
+By extending the static usage analysis with a dynamic approach, the detected usage samples could be enriched with valuable runtime data describing involved parameters, the fine-grained code coverage of package members, or the invocation context of members.
+Returning to the abstract problem that we have formulated in the introduction -- how can we improve developer knowledge about their packages' usage?
+--, further data sources next to source code files emerge that could be mined for package references, too.
+For instance, we are looking forward to solutions that mine the change history of projects for package-related changes (potentially indicating breaking changes), search conversation platforms such as public issue trackers or Q\&A forums for mentions of package members and analyze their sentiments, e.g., potentially indicating confusing behavior or bad documentation), or even scan continuous integration logs for failure stack traces (e.g., potentially revealing bugs in the package of interest.
+
+\section*{\uppercase{Acknowledgements}}
+
+We want to thank the anonymous reviewers for their valuable comments and suggestions to improve this article.
+This work is part of the \enquote{Software-DNA} project, which is funded by the European Regional Development Fund (ERDF or EFRE in German) and the State of Brandenburg (ILB).
+This work is also part of the KMU project \enquote{KnowhowAnalyzer} (Förderkennzeichen 01IS20088B), which is funded by the German Ministry for Education and Research (Bundesministerium für Bildung und Forschung).
+
+\bibliographystyle{apalike}
+{\small%\balance
+\bibliography{paper}}
 
 \end{document}
-\endinput
